### 2015-04-15 Paper2015.tex
Initial commit.
Files from Qian to Simon on 15 April.

% Paper 2015

\documentclass[12pt,journal]{IEEEtran}

% *** MISC UTILITY PACKAGES ***
%
\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
   % pdf code
 %\else
   % dvi code
% \fi

% *** CITATION PACKAGES ***
%
\usepackage{cite}

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
   \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
   \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
   \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
   \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
   \DeclareGraphicsExtensions{.eps}
\fi

% *** MATH PACKAGES ***
%
\usepackage[cmex10]{amsmath}

% *** SPECIALIZED LIST PACKAGES ***
%
\usepackage{algorithmic}

% *** ALIGNMENT PACKAGES ***
%
\usepackage{array}

% *** SUBFIGURE PACKAGES ***
\ifCLASSOPTIONcompsoc
  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\else
  \usepackage[caption=false,font=footnotesize]{subfig}
\fi

% *** FLOAT PACKAGES ***
%
\usepackage{fixltx2e}

\usepackage{stfloats}

\ifCLASSOPTIONcaptionsoff
  \usepackage[nomarkers]{endfloat}
 \let\MYoriglatexcaption\caption
\renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
\fi

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
\usepackage{url}

\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{subfig}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------
\title{\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Monte Carlo calculation to characterize neutron and gamma fields for ANITA neutron facility at TSL}} 	% Article title

\author{Q. Hong, 
S. P. Platt,~\IEEEmembership{Member,~IEEE}
Alexander V. Prokofiev,~\IEEEmembership{Member,~IEEE}
\thanks{further information}\\[2mm] 	% Your name
%\normalsize University of Central Lancashire \\ 							% Your institution
%\normalsize \href{qhong@uclan.ac.uk} 								% Your email address
\vspace{-5mm}
}

%----------------------------------------------------------------------------------------

\maketitle % Insert title

%----------------------------------------------------------------------------------------
%	ABSTRACT
%----------------------------------------------------------------------------------------

\begin{abstract}
Monte Carlo simulation of spallation neutron source of ANITA at TSL was used to analyze radiation fields at the Close User Position (CUP) and Standard User Position(SUP) for single-event effect testing. ...
\end{abstract}

%----------------------------------------------------------------------------------------
%	KEYWORDS
%----------------------------------------------------------------------------------------
\begin{IEEEkeywords}
ANITA,Geant4, neutron,gamma, TSL.
\end{IEEEkeywords}

%----------------------------------------------------------------------------------------
%	ARTICLE CONTENTS
%----------------------------------------------------------------------------------------

\IEEEpeerreviewmaketitle

\section{Introduction}

\IEEEPARstart{M}{onte} Carlo simulations of naked spallation neutron sources at Los Alamos Neutron Science Center (LANSCE) Weapons Neutron Research (WNR) Target 4\cite{Wender87} and the ANITA beam at the University of Uppsala The Svedberg Laboratory (TSL) have been completed using Geant4 and proved that Binary intranuclear cascade (INC) model gave a good representation of neutron spectra than Bertini INC model did\cite{Platt13}. Simulation result of neutron spectra using Geant4 with Binary INC model is below measurement data from ANITA neutron facility. It is likely to be influenced by our omission of collimator, shielding, and bending magnet component. This work is to verify this hypothesis is correct. In addition, we are intested in the gamma field at CUP and SUP in spallation neutron source at the ANITA neutron facility at TSL for SEE testing. 
%------------------------------------------------

\section{Modelling}

In simulation work, more components such as bending magnet, shielding, target surroundings, collimator, and detector system were constructed compare with preliminary model of neutron source at the ANITA neutron facility at TSL, see Fig.~\ref{fig:ANITAoverview}. 
The detector system includes five size simulated-detectors which are placed at different positions, see Table~\ref{table:DetectorSystem}.

\begin{figure}[!t]
	\centering
	\includegraphics[width=3in]{overview.png}
	\caption{Simulated ANITA facility overview seen from above (yellow: bending magnet; red: shielding components; blue: target cooling jacket (enclosing the target); grey: collimator; blue: detector system)}
	\label{fig:ANITAoverview}
\end{figure}

\begin{table}[!tbp]
	\caption{Detector system}
	\label{table:DetectorSystem}
	\centering
	\begin{tabular}{lllr}
	\toprule
	Detector name & Size   & Location from Target & Ref \\
		  	   & $cm$ & $cm$			& 	\\
	\midrule
	CUP		& $60\times60\times0.1$  & $75.0$    & \cite{Prokofiev14}\\
	CUPTOF	& $60\times60\times0.1$  & $84.0$    & \cite{Prokofiev14}\\
	FF 		& $120\times240\times0.1$  & $86.6$    & \\
	TE 		& aperture size  & $186.7$  & \\
	SUP  		& $120\times120\times0.1$  & $250.0$  & \cite{Prokofiev2009}\\
	\bottomrule
	\end{tabular}
\end{table}

\begin{table}[!tbp]
\caption{Neutron yield under the umbra region at the standard user position}	%title of the table
	\label{table:NYieldRadiusEffectAtSUP}
	\centering
	\begin{tabular}{l c c c}
            \toprule
            {collimator}   &{$< \SI{1}{\MeV}$}	&{$\geq 1 \& <\SI{10}{\MeV}$}	&{$\geq \SI{10}{\MeV}$}\\
            \cmidrule(r){2-4}
            {\si{\centi\metre}}     &	&{\SI{1e-6}{ncm^{-2}p^{-1}}}	&\\
             \midrule
		3 		& 0.833 	& 0.975	& 0.525\\
		10.2 		& 1.394 	& 1.248	& 0.525\\ 
		30 		& 1.962 	& 1.555	& 0.650\\
            \bottomrule
	\end{tabular}
\end{table}

%------------------------------------------------
\section{Results}

\subsection{Subsection One}
\begin{figure*}[!t] 
	\centering    
	\subfloat[Geant4 modelling]{\includegraphics[width=3in]{TOFLethargylinearspace.eps}
	\label{fig:TOFLethargylinearspace}}
	\hfil
	\subfloat[TSL MCNPX modelling~\cite{Prokofiev14}]{\includegraphics[width=3in]{StandardLetNYieldAtCUPTOF.eps}
	\label{fig:StandardLethargylinearspace}}
	\caption{Simulated spectral fluence at the CUP-TOF position for \SI{3}{\cm}, \SI{10.2}{\cm}, \SI{30}{\cm} and no collimator. The dashed line, solid line, and dotted line represent the neutron yield of collimator with diameter 3, 10.2, and \SI{30}{\cm}. The dash-dotted line represents modelling with no collimator attached.}
	\label{fig_LethargylinearspaceFor4collimators}
\end{figure*}

Fig.~\ref{fig_LethargylinearspaceFor4collimators} shows

\begin{figure}[!t] 
	\centering    
	\includegraphics[width=3in]{SUPcomparedlinearspace.eps}
	\caption{Simulated spectral yield at the SUP for \SI{3}{\cm}, \SI{10.2}{\cm}, and \SI{30}{\cm} collimators}
	\label{fig:SUPcomparedlinearspace}
\end{figure}

\subsection{Subsection Two}
\begin{figure*}[!t] 
	\centering    
	\subfloat[Differential]{\includegraphics[width=3in]{DiffYieldComparedSUPCUP10.eps}
	\label{fig:DiffYieldComparedSUPCUP10}}
	\hfil
	\subfloat[Integral]{\includegraphics[width=3in]{IntYieldComparedSUPCUP10.eps}
	\label{fig:IntYieldComparedSUPCUP10}}
	\caption{Comparison of Geant4 simulated spectral fluence with analytical model at the SUP and the CUP with \SI{10.2}{\cm} collimator~\cite{Prokofiev2009,Prokofiev14}}
	\label{fig:NYieldComparedSUPCUP10}
\end{figure*}

\subsection{Subsection Three}
\begin{figure}[!t] 
	\centering  
	\includegraphics[width=3in]{TOF3Componentslinear.eps}
	\caption{Simulated neutron yield with \SI{3}{\cm} collimator at the CUP-TOF position and three components. The dashed line, dotted line, dash-dotted line represent neutrons directly from the target, frontal wall component, and surroundings component, respectively. The solid line represents the sum of the DC, FWC, and SC components, which is the neutron yield with \SI{3}{\cm} collimator at the CUP-TOF position, in the lethargy scale.}
	\label{fig:TOF3Componentslinear}
\end{figure}

\subsection{Subsection Four, time of flight spectrum}

\begin{figure}[!t] 
	\centering 
	\subfloat[Time of flight spectrum at the CUP-TOF position, with \SI{3}{\cm} collimator]{\includegraphics[width=3in]{TOF3frameoverlap.eps}
	\label{fig:TOFFrameOverlapspectrum}}
	\vfil
	\subfloat[Time of flight spectrum at the SUP, with \SI{10.2}{\cm} collimator]{\includegraphics[width=3in]{SUP10frameoverlap.eps}
	\label{fig:SUP10FrameOverlapspectrum}}
\end{figure}

\subsection{Subsection Five, beam profile folding with $^{238}U(n,f)$ cross-section}

\begin{figure}[!t]
	\centering
	\subfloat[\SI{3}{\cm} collimator]{\includegraphics[width=2.5in]{CUPTOF3beampro.png}
	\label{fig:CUPTOF3beampro}}
	\hfil
	\subfloat[\SI{10.2}{\cm} collimator]{\includegraphics[width=2.5in]{CUPTOF10beampro.png}
	\label{fig:CUPTOF10beampro}}
	\hfil
	\subfloat[\SI{30}{\cm} collimator]{\includegraphics[width=2.5in]{CUPTOF30beampro.png}
	\label{fig:CUPTOF30beampro}}
	\caption{Neutron beam profiles folding with $^{238}U(n,f)$ cross-section at the CUP-TOF position with \SI{3}{\cm}, \SI{10.2}{\cm}, and \SI{30}{\cm} collimator} 
	\label{fig:CUPTOFbeamprofileFolding}
\end{figure}

\begin{figure}[!t] 
	\centering    
	\subfloat[\SI{3}{\cm} collimator]{\includegraphics[width=2.5in]{SUP3beamproFolding.png}
	\label{fig:SUP3beamproFolding}}
	\hfill
	\subfloat[\SI{10.2}{\cm} collimator]{\includegraphics[width=2.5in]{SUP10beamproFolding.png}
	\label{fig:SUP10beamproFolding}}
	\hfill
	\subfloat[\SI{30}{\cm} collimator]{\includegraphics[width=2.5in]{SUP30beamproFolding.png}
	\label{fig:SUP30beamproFolding}}
	\caption{Neutron beam profile folding with $^{238}U(n,f)$ cross-section at the SUP with \SI{3}{\cm}, \SI{10.2}{\cm}, and \SI{30}{\cm} collimator} 
	\label{fig:SUPbeamprofileFolding}
\end{figure}

Fig.~\ref{fig:CUPTOFbeamprofileFolding} shows

%\begin{equation}
%\label{eq:emc}
%e = mc^2
%\end{equation}

\subsection{Gamma, subsection one : Spatial distribution}

\begin{figure}[!t] 
	\centering    
	\subfloat[\SI{3}{\cm} collimator]{\includegraphics[width=3in]{CUP3ColSpatialDistributionAllG}
	\label{fig:CUP3SpatialDistributionAllG}}
	\hfil
	\subfloat[\SI{10.2}{\cm} collimator]{\includegraphics[width=3in]{CUP10ColSpatialDistributionAllG}
	\label{fig:CUP10SpatialDistributionAllG}}
	\caption{Gamma spatial distribution at the CUP with \SI{3}{\cm}, and \SI{10.2}{\cm} collimator~\cite{Prokofiev2009,Prokofiev14}}
	\label{fig:gCUPSpatialDistribution}
\end{figure}

\begin{table}[!tbp]
\caption[{$\gamma$ yield for each collimator in a radius of \SI{5}{\cm} at the CUP}]{$\gamma$ yield for each collimator at the CUP}	%title of the table
\centering
\label{table:GYieldCUP}
\begin{tabular}{l	c	c}
\hline% insert double-line
Collimator size   & above \SI{1}{\MeV}   &  above \SI{0.1}{\MeV}  \\ 
\cmidrule(r){2-3}
\SI{}{\cm}       & \SI{}{10^{-6}.\gamma.cm^{-2}.p^{-1}} &  \SI{}{10^{-6}.\gamma.cm^{-2}.p^{-1}}\\
\hline % insert single-line
3 & 4.93 & 15.73\\

10.2 & 4.86  &  15.27\\

30 & 4.44  &  13.80\\
\hline
\end{tabular}
\end{table}

\begin{table}[!tbp]
\caption[$\gamma$ yield for each collimator in umbra region at the SUP]{$\gamma$ yield for each collimator in umbra region at the SUP}	%title of the table
\centering
\label{table:GYieldSUP}
\begin{tabular}{l	c	c}
\hline% insert double-line
Collimator size   & above \SI{1}{\MeV}   &  above \SI{0.1}{\MeV}   \\ 
\cmidrule(r){2-3}
\SI{}{\cm}       & \SI{}{10^{-7}.\gamma.cm^{-2}.p^{-1}} &  \SI{}{10^{-7}.\gamma.cm^{-2}.p^{-1}}\\
\hline % insert single-line
3 & 2.3 & 6.7\\

10.2 & 2.8  &  8.3\\

30 & 3.2  &  9.4\\
\hline
\end{tabular}
\end{table}

\subsection{Gamma, subsection two : Photon spectra at the CUP and SUP }

\begin{figure}[!t] 
	\centering    
	\subfloat[CUP]{\includegraphics[width=3in]{gCUPDYieldcompared}
	\label{fig:gCUPDYieldcompared}}
	\vfil
	\subfloat[SUP]{\includegraphics[width=3in]{gSUPDYieldcompared}
	\label{fig:gSUPDYieldcompared}}
	\caption{Comparison of differential photon yield at the CUP and SUP}
	\label{fig:gDYieldspectra}
\end{figure}

\begin{figure}[!t] 
	\centering    
	\subfloat[CUP]{\includegraphics[width=3in]{gCUPIYieldcompared}
	\label{fig:gCUPIYieldcompared}}
	\vfil
	\subfloat[SUP]{\includegraphics[width=3in]{gSUPIYieldcompared}
	\label{fig:gSUPIYieldcompared}}
	\caption{Comparison of integral photon yield at the CUP and SUP}
	\label{fig:gIYieldspectra}
\end{figure}
Figure~\ref{fig:gIYieldspectra} displayed integral photon spectra at the CUP and SUP. The photon spectra at the SUP with \SI{3}{\cm} collimator, it is dominated by energy within about \SI{7}{\MeV} at the SUP, see Figure~\ref{fig:gSUPIYieldcompared}.

\begin{table}
\caption{$\gamma$ dose rate for each collimator at the CUP and SUP}	%title of the table
\centering
\label{Table:DoseRate}
        \begin{tabular}{l c c}
            \toprule
            {collimator diameter}   &{CUP}         &{SUP}\\
            {\si{\centi\metre}}    &{\si{mSvh^{-1}}}   &{\si{mSvh^{-1}}}\\
            \midrule
            3                       & 378.0                	& 17.32\\
            10.2                  & 369.4               	& 20.90\\
            30                     & 336.4          		& 23.65\\
            \bottomrule
\end{tabular}
\end{table}

\begin{figure}[!t] 
	\centering    
	\subfloat[CUP]{\includegraphics[width=2.5in]{DoseVSenergyCUP.eps}
	\label{fig:DoseVSenergyCUP}}
	\hfil
	\subfloat[SUP]{\includegraphics[width=2.5in]{DoseVSenergySUP.eps}
	\label{fig:DoseVSenergySUP}}
	\caption{Dose versus energy at the CUP and SUP with \SI{3}{\cm}, \SI{10.2}{\cm}, and \SI{30}{\cm} collimators}
	\label{fig:DoseVSenergy}
\end{figure}

%------------------------------------------------
\section{Discussion}

\subsection{Subsection One}

Neutron .....

\subsection{Subsection Two}

Gamma .....

%----------------------------------------------------------------------------------------
%	REFERENCE LIST
%----------------------------------------------------------------------------------------

\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

\begin{thebibliography}{99} % Bibliography - this is intentionally simple in this template

\bibitem{Wender87}
S.A. Wender and P.W. Lisowski,
\newblock A white neutron source from 1 to 400 MeV,								% title	
\newblock {\em Nucl. Instr. Meth. Phys. Res. B}, vol. 24-25, pp. 897-900.					% vol:page, 2011

\bibitem{Platt13}
Platt, S.P. and Hong, Q. and Mein, S.J. and Zhang, L.H.,
\newblock Neutron and gamma fields at neutron spallation sources for single-event-effects testing,		% title	
\newblock {\em in Proc. 14th European Conf. Radiat. Effects Compon. Syst. 2013,} pp 1-4			% vol:page, 2011

\bibitem{Prokofiev14}
Prokofiev, A.V. and Blomgren, J. and Majerle, M. and Nolte, R. and Rottger, S. and Platt, S.P. and Cai Xiao Xiao and Smirnov, A.N.,
\newblock Characterization of the ANITA Neutron Source for Accelerated SEE Testing at the Svedberg Laboratory,		% title	
\newblock {\em in Proc. IEEE Radiation Effects Data Workshop. 2009,} pp 166-173 							% vol:page, 2011

\bibitem{Prokofiev2009}
Prokofiev, A.V. and Passoth, E. and Hjalmarsson, A. and Majerle, M.,
\newblock CUP-A New High-Flux Irradiation Position at the ANITA Neutron Facility at TSL,		% title	
\newblock {\em in Proc. IEEE Trans. Nucl. Sci. 2014}, pp 1929-1936 					% vol:page, 2011

\end{thebibliography}

%----------------------------------------------------------------------------------------

\end{document}

### 2015-04-15 Paper2015.tex
Work in progress.

@@
 % Paper 2015
-
 \documentclass[12pt,journal]{IEEEtran}
@@
 \usepackage{siunitx}
+\DeclareSIUnit\photon{\ensuremath{\gamma}}
+\DeclareSIUnit\proton{p}
+\DeclareSIUnit\neutron{n}
 \usepackage{booktabs}
@@
 
+\usepackage{todo}
 % correct bad hyphenation here
@@
 %----------------------------------------------------------------------------------------
-\title{\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Monte Carlo calculation to characterize neutron and gamma fields for ANITA neutron facility at TSL}} 	% Article title
+\title{Monte Carlo calculation to characterize neutron and gamma fields for ANITA neutron facility at TSL}
 
@@
 
-In simulation work, more components such as bending magnet, shielding, target surroundings, collimator, and detector system were constructed compare with preliminary model of neutron source at the ANITA neutron facility at TSL, see Fig.~\ref{fig:ANITAoverview}.
-The detector system includes five size simulated-detectors which are placed at different positions, see Table~\ref{table:DetectorSystem}.
+A detailed model of the ANITA geometry was implemented in Geant4.
+This is illustrated in overview in Fig.~\ref{fig:ANITAoverview}
+Description of the geometry is given in \cite{Prokofiev2009,Prokofiev14}; a summary only is given here.
+The spallation target is a tungsten cylinder of diameter \SI{0}{\cm} and length \SI{0}{\cm}.
+The target is cooled by water and surrounded by a stainless-steel cooling jacket.
+The target assembly with its cooling jacket appears as a small blue rectangle in Fig.~\ref{fig:ANITAoverview}.
+Lead shielding blocks in the target region are also modelled, and shown in red Fig.~\ref{fig:ANITAoverview}.
+A large electromagnet surrounding the target is modelled and shown in Fig.~\ref{fig:ANITAoverview} in grey (iron) and yellow (copper).
+An iron collimator with variable apertures is modelled  and shown downstream of the target (grey).
 
@@
 
-\begin{table}[!tbp]
-	\caption{Detector system}
-	\label{table:DetectorSystem}
-	\centering
-	\begin{tabular}{lllr}
-	\toprule
-	Detector name & Size   & Location from Target & Ref \\
-		  	   & $cm$ & $cm$			& 	\\
-	\midrule
-	CUP		& $60\times60\times0.1$  & $75.0$    & \cite{Prokofiev14}\\
-	CUPTOF	& $60\times60\times0.1$  & $84.0$    & \cite{Prokofiev14}\\
-	FF 		& $120\times240\times0.1$  & $86.6$    & \\
-	TE 		& aperture size  & $186.7$  & \\
-	SUP  		& $120\times120\times0.1$  & $250.0$  & \cite{Prokofiev2009}\\
-	\bottomrule
-	\end{tabular}
-\end{table}
+Simulations were conducted using Geant4 version~TBD.
+The TBD intranuclear cascade model was selected in accordance with the results of earlier work~\cite{Platt13}, in which it performed well in simulations of neutron spallation in the region from \SIrange{0}{0}{\MeV}.
+In the simulation protons were incident axially at an energy of \SI{180}{\MeV}.
+Resulting gamma and neutron fields were evaluated at several locations.
+In this paper results are presented for three of these: The Standard User Position (SUP), \SI{2.5}{\m} downstream of the target centre (check centre)~\cite{Prokofiev2009}, the Close User Position (CUP), \SI{0}{\m} downstream of the target, and the CUP-TOF, \SI{0}{m} downstream of the target.
+The SUP, CUP and CUP-TOF positions are visible in blue in Fig.~\ref{fig:ANITAoverview}.
+The SUP and CUP positions are of interest as they are positions used for SEE tests; the CUP-TOF position is the location of thin-film breakdown counter (TFBC) detectors used for beam monitoring and characterisation using time-of-flight (TOF) techniques.
+Model validation will be demonstrated against CUP-TOF data (section~\ref{tbd}).
 
@@
           \cmidrule(r){2-4}
-            {\si{\centi\metre}}     &	&{\SI{1e-6}{ncm^{-2}p^{-1}}}	&\\
+          {\si{\centi\metre}}	&						&{\SI{1e-6}{\neutron\per\cm\squared\per\proton}}	&\\
           \midrule
@@
 \section{Results}
+
+In previous work Platt et al.~\cite{Platt13} reported simulations of a naked ANITA target, demonstrating good qualitative agreement with independent calculations and measurements of the fast neutron field at ANITA SUP~\cite{Prokofiev2009}.
+Part of the motivation for this work was to investigate whether improvements in the fidelity of the Geant4 model would lead to increased quantitative agreement.
+Fig.~\ref{fig:SUPCollimator}
+
+\begin{figure}
+    \todo{}
+    \caption{Neutron field at the Standard User Position downstream of the \SI{10.2}{\cm} collimator}
+    \label{fig:SUPCollimator}
+\end{figure}
+
+\begin{figure}
+    \todo{}
+    \caption{Neutron profile at the Standard User Position downstream of the \SI{10.2}{\cm} collimator}
+    \label{fig:SUPProfile}
+\end{figure}
+
+Fig.~\ref{fig:FirstComparison}\ldots
+
+\begin{figure}
+	\todo{Here we need figures showing the integral spectra on log-log plots and equilethargic spectra normalised to unit area above \SI{10}{\MeV}}
+	\caption{Neuton spectrum at the SUP, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from a naked Geant4 model~\cite{Platt13} and this work.}
+	\label{fig:FirstComparison}
+\end{figure}
 
@@
 \label{table:GYieldCUP}
-\begin{tabular}{l	c	c}
+\begin{tabular}{lcc}
 	\hline% insert double-line
@@
 	\cmidrule(r){2-3}
-\SI{}{\cm}       & \SI{}{10^{-6}.\gamma.cm^{-2}.p^{-1}} &  \SI{}{10^{-6}.\gamma.cm^{-2}.p^{-1}}\\
+/\si{\cm}       & /\SI{e-6}{\photon\per\cm\squared\per\proton} & /\SI{e-6}{\photon\per\cm\squared\per\proton} \\
 \hline % insert single-line
@@
 \cmidrule(r){2-3}
-\SI{}{\cm}       & \SI{}{10^{-7}.\gamma.cm^{-2}.p^{-1}} &  \SI{}{10^{-7}.\gamma.cm^{-2}.p^{-1}}\\
+/\si{\cm}       & \/\SI{e-6}{\photon\per\cm\squared\per\proton} &  /\SI{e-6}{\photon\per\cm\squared\per\proton} \\
 \hline % insert single-line
@@
 
+\todos
+
 \end{document}

### 2015-04-16 Paper2015.tex
Modified text of paper.
Introduced macro for U238.

In introduction, explained that we'll only present results for the 10.2cm collimator in the summary - other collimators in the final paper.

Added and tidied up todos.

Removed table about neutron yield - information to go in main text.

Completed text for the first part of the results section: neutron contour plot, neutron profile, neutron spectrum (with comparison to earlier results)

@@
 \DeclareSIUnit\neutron{n}
+
 \usepackage{booktabs}
@@
 \usepackage{todo}
+
+\usepackage{bpchem}
+\def\U238{\BPChem{\^{238}U}}
+
 % correct bad hyphenation here
@@
 An iron collimator with variable apertures is modelled  and shown downstream of the target (grey).
+For brevity in this summary we only present results for the standard collimator size (\SI{10.2}{\cm} diameter); in the final paper we will present results for cylindrical collimators in the range from \SIrange{3}{30}{\cm} diameter.
 
@@
 Simulations were conducted using Geant4 version~TBD.
-The TBD intranuclear cascade model was selected in accordance with the results of earlier work~\cite{Platt13}, in which it performed well in simulations of neutron spallation in the region from \SIrange{0}{0}{\MeV}.
+The TBD intranuclear cascade model was selected in accordance with the results of earlier work~\cite{Platt13}, in which it performed well in simulations of neutron spallation in the region from \SIrange{0}{0}{\MeV}.\todo{Enter neutron energy range}
 In the simulation protons were incident axially at an energy of \SI{180}{\MeV}.
 Resulting gamma and neutron fields were evaluated at several locations.
-In this paper results are presented for three of these: The Standard User Position (SUP), \SI{2.5}{\m} downstream of the target centre (check centre)~\cite{Prokofiev2009}, the Close User Position (CUP), \SI{0}{\m} downstream of the target, and the CUP-TOF, \SI{0}{m} downstream of the target.
+In this paper results are presented for three of these: The Standard User Position (SUP), \SI{2.5}{\m} downstream of the target centre\todo{check centre}~\cite{Prokofiev2009}, the Close User Position (CUP), \SI{0}{\m} downstream of the target, and the CUP-TOF, \SI{0}{m} downstream of the target.\todo{Enter CUP \& CUP-TOF ranges}
 The SUP, CUP and CUP-TOF positions are visible in blue in Fig.~\ref{fig:ANITAoverview}.
@@
 Model validation will be demonstrated against CUP-TOF data (section~\ref{tbd}).
-
-\begin{table}[!tbp]
-\caption{Neutron yield under the umbra region at the standard user position}	%title of the table
-	\label{table:NYieldRadiusEffectAtSUP}
-	\centering
-	\begin{tabular}{l c c c}
-		\toprule
-          {collimator}   		&{$< \SI{1}{\MeV}$}	&{$\geq 1 \& <\SI{10}{\MeV}$}	&{$\geq \SI{10}{\MeV}$}\\
-          \cmidrule(r){2-4}
-          {\si{\centi\metre}}	&						&{\SI{1e-6}{\neutron\per\cm\squared\per\proton}}	&\\
-          \midrule
-		3 		& 0.833 	& 0.975	& 0.525\\
-		10.2 	& 1.394 	& 1.248	& 0.525\\
-		30 		& 1.962 	& 1.555	& 0.650\\
-           \bottomrule
-	\end{tabular}
-\end{table}
 
@@
 In previous work Platt et al.~\cite{Platt13} reported simulations of a naked ANITA target, demonstrating good qualitative agreement with independent calculations and measurements of the fast neutron field at ANITA SUP~\cite{Prokofiev2009}.
-Part of the motivation for this work was to investigate whether improvements in the fidelity of the Geant4 model would lead to increased quantitative agreement.
-Fig.~\ref{fig:SUPCollimator}
+Part of the motivation for this work was to investigate whether improvements in the fidelity of the geometry used in the Geant4 model would lead to increased quantitative agreement.
+Fig.~\ref{fig:SUPCollimator} shows neutron fluence rate contours at the SUP position.
+The collimation effect is clearly visible.
+Fig.~\ref{fig:SUPProfile} compares simulated and measured neutron fluence profile at the SUP.
+Measurements were taken with a TFBC in which \U238\ is the target material~\cite{Prokofiev2009}; accordingly, simulated results were folded in energy with the neutron fission cross section for \U238~\cite{tbd}.
+The results show~\todo{Explain SUP profile results.}
+The predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{0}{\neutron\per\cm\squared\per\second}, compared to \SI{0}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt13} and \SI{0}{\neutron\per\cm\squared\per\second} from the parameterisation~\cite{Prokofiev2009}.
+The current calculations therefore underpredict the parameterisation by tbd\%.\todo{Quantify integral yield}
 
-\begin{figure}
-    \todo{}
-    \caption{Neutron field at the Standard User Position downstream of the \SI{10.2}{\cm} collimator}
+\begin{figure}[t]
+    \todo{Show neutrons above \SI{10}{\MeV}}
+    \caption{Neutron yield above \SI{10}{\MeV} at the Standard User Position.}
     \label{fig:SUPCollimator}
@@
 
-\begin{figure}
-    \todo{}
-    \caption{Neutron profile at the Standard User Position downstream of the \SI{10.2}{\cm} collimator}
+\begin{figure}[t]
+    \todo{Show SUP profile, compared to measurements}
+    \caption{Neutron profile at the Standard User Position}
     \label{fig:SUPProfile}
@@
 
-Fig.~\ref{fig:FirstComparison}\ldots
+Fig.~\ref{fig:FirstComparison} compares calculated neutron yield versus energy in the umbra at the SUP with that predicted by the naked-target simulation~\cite{Platt13} and with the standard parameterisation of the ANITA sup spectrum~\cite{Prokofiev2009}.
+The results show\ldots\todo{Discuss the results. Compare current with earlier calculations. Compare calculations with parameterisation.}
 
-\begin{figure}
-	\todo{Here we need figures showing the integral spectra on log-log plots and equilethargic spectra normalised to unit area above \SI{10}{\MeV}}
+\begin{figure}[t]
+	\subfloat[Integral fluence rate]{\hspace{\columnwidth}\todo{Integral spectra on log-log axes}}\\
+	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\hspace{\columnwidth}\todo{Normalised spectra on lethargy axes}}
 	\caption{Neuton spectrum at the SUP, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from a naked Geant4 model~\cite{Platt13} and this work.}

### 2015-04-16 Paper2015.tex
Revised results section to have three parts, and completed first draft of first part.
Three parts are on neutron spatial distribution and spectrum, neutron TOF, and gamma.

Added and updated some todos.

@@
 Monte Carlo simulation of spallation neutron source of ANITA at TSL was used to analyze radiation fields at the Close User Position (CUP) and Standard User Position(SUP) for single-event effect testing.
-...
+...\todo{Revise abstract}
 \end{abstract}
@@
 \section{Introduction}
-
+\todo{Review introduction}
 \IEEEPARstart{M}{onte} Carlo simulations of naked spallation neutron sources at Los Alamos Neutron Science Center (LANSCE) Weapons Neutron Research (WNR) Target 4\cite{Wender87} and the ANITA beam at the University of Uppsala The Svedberg Laboratory (TSL) have been completed using Geant4 and proved that Binary intranuclear cascade (INC) model gave a good representation of neutron spectra than Bertini INC model did\cite{Platt13}.
@@
 In previous work Platt et al.~\cite{Platt13} reported simulations of a naked ANITA target, demonstrating good qualitative agreement with independent calculations and measurements of the fast neutron field at ANITA SUP~\cite{Prokofiev2009}.
-Part of the motivation for this work was to investigate whether improvements in the fidelity of the geometry used in the Geant4 model would lead to increased quantitative agreement.
-Fig.~\ref{fig:SUPCollimator} shows neutron fluence rate contours at the SUP position.
+Part of the motivation for this work was to investigate whether improvements in the fidelity of the geometry used in the Geant4 model would lead to increased quantitative agreement.\todo{Review frst part of Results section -- move to introduction?}
+
+\subsection{Neutron fluence rate, spatial distribution and spectrum}
+
+Fig.~\ref{fig:SUPDensity} shows neutron spatial distribution at the SUP.
 The collimation effect is clearly visible.
@@
 Measurements were taken with a TFBC in which \U238\ is the target material~\cite{Prokofiev2009}; accordingly, simulated results were folded in energy with the neutron fission cross section for \U238~\cite{tbd}.
-The results show~\todo{Explain SUP profile results.}
+The results show~\todo{Explain SUP profile results. Include explanation of ``umbra'' and ``penumbra''}
 The predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{0}{\neutron\per\cm\squared\per\second}, compared to \SI{0}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt13} and \SI{0}{\neutron\per\cm\squared\per\second} from the parameterisation~\cite{Prokofiev2009}.
-The current calculations therefore underpredict the parameterisation by tbd\%.\todo{Quantify integral yield}
+The parameterisation therefore exceeds the current calculations by tbd\%.\todo{Quantify integral yield}
 
 \begin{figure}[t]
-    \todo{Show neutrons above \SI{10}{\MeV}}
-    \caption{Neutron yield above \SI{10}{\MeV} at the Standard User Position.}
-    \label{fig:SUPCollimator}
+    \vspace{2in}
+    \todo{Show density of neutrons above \SI{10}{\MeV} at SUP}
+    \caption{Neutron fluence rate above \SI{10}{\MeV} at the Standard User Position.}
+    \label{fig:SUPDensity}
 \end{figure}
@@
 \begin{figure}[t]
+    \vspace{2in}
     \todo{Show SUP profile, compared to measurements}
@@
 
-Fig.~\ref{fig:FirstComparison} compares calculated neutron yield versus energy in the umbra at the SUP with that predicted by the naked-target simulation~\cite{Platt13} and with the standard parameterisation of the ANITA sup spectrum~\cite{Prokofiev2009}.
+Fig.~\ref{fig:SUPSpectraComparison} compares calculated neutron yield versus energy in the umbra at the SUP with that predicted by the naked-target simulation~\cite{Platt13} and with the standard ANITA SUP parameterisation~\cite{Prokofiev2009}.
 The results show\ldots\todo{Discuss the results. Compare current with earlier calculations. Compare calculations with parameterisation.}
@@
 \begin{figure}[t]
+    \vspace{2in}
 	\subfloat[Integral fluence rate]{\hspace{\columnwidth}\todo{Integral spectra on log-log axes}}\\
+    \vspace{2in}
 	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\hspace{\columnwidth}\todo{Normalised spectra on lethargy axes}}
 	\caption{Neuton spectrum at the SUP, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from a naked Geant4 model~\cite{Platt13} and this work.}
-	\label{fig:FirstComparison}
+	\label{fig:SUPSpectraComparison}
 \end{figure}
+
+Fig.~\ref{fig:CUPDensity} and Fig.~\ref{fig:CUPProfile} show neutron spatial distribution (for neutrons above \SI{10}{\MeV}) and profile (folded in energy with the \U238\ fission cross-section) at the CUP.
+The results show\ldots\todo{Describe the results: contours and profile at CUP}
+
+\begin{figure}[t]
+    \vspace{2in}
+    \todo{Show density of neutrons above \SI{10}{\MeV} at CUP}
+    \caption{Neutron fluence rate above \SI{10}{\MeV} at the Close User Position.}
+    \label{fig:CUPDensity}
+\end{figure}
+
+\begin{figure}[t]
+    \vspace{2in}
+    \todo{Show CUP profile, compared to measurements}
+    \caption{Neutron profile at the Close User Position}
+    \label{fig:CUPProfile}
+\end{figure}
+
+Fig.~\ref{fig:CUPSpectraCOmparison} compares the spectrum calculated at the CUP with that from the standard parameterisation~\cite{Prokofiev14}.
+The latter curve is derived from MCNPX calculations supported by TOF measurements with TFBCs.
+The results show\ldots\todo{Explain what the results show: CUP measurement comparison.}
+Fig.~\ref{fig:MCComparison} provides a direct comparison between the two Monte Carlo calculations.
+The results show\ldots\todo{Explain what the results show (comparison between independent MC calculations).}
+
+\begin{figure}[t]
+    \vspace{2in}
+	\subfloat[Integral fluence rate]{\hspace{\columnwidth}\todo{Integral spectra on log-log axes: CUP}}\\
+    \vspace{2in}
+	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\hspace{\columnwidth}\todo{Normalised spectra on lethargy axes: CUP}}
+	\caption{Neuton spectrum at the Close User Position, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from this work.}
+	\label{fig:CUPSpectraComparison}
+\end{figure}
+
+\begin{figure}[t]
+    \vspace{2in}
+    \todo{Show Comparison between Geant4 and MCNPX calculations}
+    \caption{Calculated neutron spectra at the CUP-TOF position, compared to independent MCPX calculations~\cite{Prokofiev14}}
+    \label{fig:MCComparison}
+\end{figure}
+
+Fig.~\ref{fig:DifferentialSpectra} summarise neutron yield results by comparing differential flux as calculated in this work with facility parameterisations~\cite{Prokofiev2009,Prokofiev14}.
+The SUP calculations and parameterisations agree very closely below \SI{20}{\MeV}; the parameterisation exceeds the calculations somewhat above that energy.
+At CUP the parameterisation exceeds the Geant4 calculations by about TBD\% below \SI{20}{\MeV} and slightly more above that energy.\todo{Improve precision of the summary description of differential spectra.}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=3in]{DiffYieldComparedSUPCUP10.eps}
+    \caption{Differential neutron spectra at CUP and SUP, comparing results of this work to facility parameterisations~\cite{Prokofiev2009,Prokofiev14}}
+    \label{fig:DifferentialSpectra}
+\end{figure}
+
+\subsection{Neutron time of flight}
+
+\subsection{Gamma fluence rate, spatial distribution and dose rate}
 

### 2015-04-16 Paper2015.tex
Completed first draft of second results subsection, on neutron TOF.

@@
 
+Neutron beam monitoring and characterisation at TSL uses time-of flight measurements with \U238\ TFBCs.
+Our Geant4 model permits these measurements to be simulated.
+Neutron time of flight data from the simulation (time measured from the time of arrival of primary photons at the target to the time of arrival of secondary neutrons at the point of interest) were folded in energy with the \U238\ fission cross-section, convolved with a \SI{5}{\ns} rectangle function approximating the primary proton micropulse shape, and overlapped at \SI{45}{\ns}, representing the timing ambiguity due to the micropulse period.
+Results are for SUP and CUP-TOF positions and compared with measurements~\cite{Prokofiev2009,Prokofiev14} in Fig.~\ref{fig:TOFSpectra}.
+The simulated CUP-TOF results were calculated for the \SI{3}{\cm} collimator, to match the available measured data.
+The results show\ldots\todo{Explain what the results show.}
+
+\begin{figure}[!t]
+	\centering
+	\subfloat[At the CUP-TOF position, with \SI{3}{\cm} collimator]{\includegraphics[width=3in]{TOF3frameoverlap.eps}\todo{Add experimental data to TOF figure (CUP)}
+	\label{fig:TOFFrameOverlapspectrum}}\\
+	\subfloat[At the SUP, with \SI{10.2}{\cm} collimator]{\includegraphics[width=3in]{SUP10frameoverlap.eps}\todo{Add experimental data to TOF figure (SUP)}
+	\label{fig:SUP10FrameOverlapspectrum}}
+    \caption{Simulated neutron time of flight spectra compared to measurements}
+    \label{fig:TOFSpectra}
+\end{figure}
+
+Prokofiev et at.~\cite{Prokofiev14} explain the TOF spectrum upstream of the collimator as being the resultant of three components: directly from the target, scattered from the target surroundings, and backscattered from the collimator front face.
+The complex flight paths and energy losses in the scattered components break the one-to-one relationship between neutron energy and neutron time of flight from target to detector.
+We are able to reproduce this situation in our simulation, as shown by Fig.~\ref{fig:TOF3Componentslinear}, which shows good agreement with\ldots\todo{Complete description of the three components.}
+
+\begin{figure}[!t]
+	\centering
+	\includegraphics[width=3in]{TOF3Componentslinear.eps}
+	\caption{
+    Simulated neutron yield with \SI{3}{\cm} collimator at the CUP-TOF position.
+    The three components are directly from the target, scattered forward from the target surroundings, and scattered back from the collimator front wall.}
+	\label{fig:TOF3Componentslinear}
+\end{figure}
+
 \subsection{Gamma fluence rate, spatial distribution and dose rate}
@@
 \subsection{Subsection Three}
-\begin{figure}[!t]
-	\centering
-	\includegraphics[width=3in]{TOF3Componentslinear.eps}
-	\caption{Simulated neutron yield with \SI{3}{\cm} collimator at the CUP-TOF position and three components.
-The dashed line, dotted line, dash-dotted line represent neutrons directly from the target, frontal wall component, and surroundings component, respectively.
-The solid line represents the sum of the DC, FWC, and SC components, which is the neutron yield with \SI{3}{\cm} collimator at the CUP-TOF position, in the lethargy scale.}
-	\label{fig:TOF3Componentslinear}
-\end{figure}
 

### 2015-04-16 Paper2015.tex
Completed first draft of the gamma results subsection.

@@
 
+Fig.~\ref{fig:GammaSpatialDistribution} shows the calculated spatial distribution of gamma photons at SUP and CUP.
+Fig.~\ref{fig:DifferentialGammaSpectra} shows the calculated differential gamma spectra within the central region of the spatial distribution.
+The results show\ldots\todo{Describe the gamma results}
+
+\begin{figure}
+    \centering
+    \vspace{2in}
+    \subfloat[SUP]{
+        \hspace{\columnwidth}\todo{Add gamma spatial distribution at SUP, \SI{10.2}{\cm} collimator}
+        \label{fig:GammaSpatialDistributionSUP}
+    }\\
+    \subfloat[CUP]{
+        \hspace{\columnwidth}\todo{Add gamma spatial distribution at CUP, \SI{10.2}{\cm} collimator}
+        \label{fig:GammaSpatialDistributionCUP}
+    }
+    \caption{Gamma spatial distribution}
+    \todo{It would be better if gamma spatial distribution were expressed as dose, rather than number of photons. Not in time for the abstract submission, however!}
+    \label{fig:GammaSpatialDistribution}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \vspace{2in}
+    \hspace{\columnwidth}
+    \caption{Calculated differential gamma spectra at CUP and SUP}
+    \label{fig:DifferentialGammaSpectra}
+\end{figure}
+
+Fig.~\ref{fig:GammaDoseEnergy} shows the calculated distribution of gamma dose, obtained by folding the gamma spectra (Fig~\ref{fig:GammaDoseEnergy}) with dose conversion data from \cite{tbd}.
+The results show\ldots\todo{Describe the gamma dose versus energy graphs.}
+The calculated dose rate at \SI{200}{\nA} primary proton current is \SI{21}{\milli\gray\per\hour} at SUP and \SI{370}{\milli\gray\per\hour} at CUP.\todo{Discuss calculated dose rates}
+
+\begin{figure}
+    \centering
+    \vspace{2in}
+    \subfloat[SUP]{
+        \hspace{\columnwidth}\todo{Add gamma dose versus energy at SUP, \SI{10.2}{\cm} collimator}
+        \label{fig:GammaDoseEnergySUP}
+    }\\
+    \subfloat[CUP]{
+        \hspace{\columnwidth}\todo{Add gamma dose versus energy at CUP, \SI{10.2}{\cm} collimator}
+        \label{fig:GammaDoseEnergyCUP}
+    }
+    \caption{Gamma dose spectra}
+    \label{fig:GammaDoseEnergy}
+\end{figure}
+
 \subsection{Subsection One}

### 2015-04-16 Paper2015.tex
Completed first draft text for results section.
Removed some unneeded sections (figures, tables etc.).
Added some todos.

@@
 \maketitle % Insert title
-
+\todo{Check title, affiliations etc.}
 %----------------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------------
-\begin{IEEEkeywords}
-ANITA,Geant4, neutron,gamma, TSL.
-\end{IEEEkeywords}
 
@@
 In previous work Platt et al.~\cite{Platt13} reported simulations of a naked ANITA target, demonstrating good qualitative agreement with independent calculations and measurements of the fast neutron field at ANITA SUP~\cite{Prokofiev2009}.
-Part of the motivation for this work was to investigate whether improvements in the fidelity of the geometry used in the Geant4 model would lead to increased quantitative agreement.\todo{Review frst part of Results section -- move to introduction?}
+Part of the motivation for this work was to investigate whether improvements in the fidelity of the geometry used in the Geant4 model would lead to increased quantitative agreement.\todo{Review first part of Results section -- move to introduction?}
 
@@
     \vspace{2in}
-	\subfloat[Integral fluence rate]{\hspace{\columnwidth}\todo{Integral spectra on log-log axes}}\\
+	\subfloat[Integral fluence rate]{\todo{Integral spectra on log-log axes}\hspace{\columnwidth}}\\
     \vspace{2in}
-	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\hspace{\columnwidth}\todo{Normalised spectra on lethargy axes}}
+	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\todo{Normalised spectra on lethargy axes}\hspace{\columnwidth}}
 	\caption{Neuton spectrum at the SUP, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from a naked Geant4 model~\cite{Platt13} and this work.}
@@
     \vspace{2in}
-	\subfloat[Integral fluence rate]{\hspace{\columnwidth}\todo{Integral spectra on log-log axes: CUP}}\\
+	\subfloat[Integral fluence rate]{\todo{Integral spectra on log-log axes: CUP}\hspace{\columnwidth}}\\
     \vspace{2in}
-	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\hspace{\columnwidth}\todo{Normalised spectra on lethargy axes: CUP}}
+	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\todo{Normalised spectra on lethargy axes: CUP}\hspace{\columnwidth}}
 	\caption{Neuton spectrum at the Close User Position, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from this work.}
@@
 	\centering
-	\subfloat[At the CUP-TOF position, with \SI{3}{\cm} collimator]{\includegraphics[width=3in]{TOF3frameoverlap.eps}\todo{Add experimental data to TOF figure (CUP)}
+	\subfloat[At the CUP-TOF position, with \SI{3}{\cm} collimator]{\todo{Add experimental data to TOF figure (CUP)\includegraphics[width=3in]{TOF3frameoverlap.eps}}
 	\label{fig:TOFFrameOverlapspectrum}}\\
-	\subfloat[At the SUP, with \SI{10.2}{\cm} collimator]{\includegraphics[width=3in]{SUP10frameoverlap.eps}\todo{Add experimental data to TOF figure (SUP)}
+	\subfloat[At the SUP, with \SI{10.2}{\cm} collimator]{\todo{Add experimental data to TOF figure (SUP)}\includegraphics[width=3in]{SUP10frameoverlap.eps}
 	\label{fig:SUP10FrameOverlapspectrum}}
@@
     \subfloat[SUP]{
-        \hspace{\columnwidth}\todo{Add gamma spatial distribution at SUP, \SI{10.2}{\cm} collimator}
+        \todo{Add gamma spatial distribution at SUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
         \label{fig:GammaSpatialDistributionSUP}
@@
     \subfloat[CUP]{
-        \hspace{\columnwidth}\todo{Add gamma spatial distribution at CUP, \SI{10.2}{\cm} collimator}
+        \todo{Add gamma spatial distribution at CUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
         \label{fig:GammaSpatialDistributionCUP}
@@
     \subfloat[SUP]{
-        \hspace{\columnwidth}\todo{Add gamma dose versus energy at SUP, \SI{10.2}{\cm} collimator}
+        \todo{Add gamma dose versus energy at SUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
         \label{fig:GammaDoseEnergySUP}
@@
     \subfloat[CUP]{
-        \hspace{\columnwidth}\todo{Add gamma dose versus energy at CUP, \SI{10.2}{\cm} collimator}
+        \todo{Add gamma dose versus energy at CUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
         \label{fig:GammaDoseEnergyCUP}
@@
 
-\subsection{Subsection One}
-\begin{figure*}[!t]
-	\centering
-	\subfloat[Geant4 modelling]{\includegraphics[width=3in]{TOFLethargylinearspace.eps}
-	\label{fig:TOFLethargylinearspace}}
-	\hfil
-	\subfloat[TSL MCNPX modelling~\cite{Prokofiev14}]{\includegraphics[width=3in]{StandardLetNYieldAtCUPTOF.eps}
-	\label{fig:StandardLethargylinearspace}}
-	\caption{Simulated spectral fluence at the CUP-TOF position for \SI{3}{\cm}, \SI{10.2}{\cm}, \SI{30}{\cm} and no collimator.
-The dashed line, solid line, and dotted line represent the neutron yield of collimator with diameter 3, 10.2, and \SI{30}{\cm}.
-The dash-dotted line represents modelling with no collimator attached.}
-	\label{fig_LethargylinearspaceFor4collimators}
-\end{figure*}
-
-Fig.~\ref{fig_LethargylinearspaceFor4collimators} shows
-
-\begin{figure}[!t]
-	\centering
-	\includegraphics[width=3in]{SUPcomparedlinearspace.eps}
-	\caption{Simulated spectral yield at the SUP for \SI{3}{\cm}, \SI{10.2}{\cm}, and \SI{30}{\cm} collimators}
-	\label{fig:SUPcomparedlinearspace}
-\end{figure}
-
-\subsection{Subsection Two}
-\begin{figure*}[!t]
-	\centering
-	\subfloat[Differential]{\includegraphics[width=3in]{DiffYieldComparedSUPCUP10.eps}
-	\label{fig:DiffYieldComparedSUPCUP10}}
-	\hfil
-	\subfloat[Integral]{\includegraphics[width=3in]{IntYieldComparedSUPCUP10.eps}
-	\label{fig:IntYieldComparedSUPCUP10}}
-	\caption{Comparison of Geant4 simulated spectral fluence with analytical model at the SUP and the CUP with \SI{10.2}{\cm} collimator~\cite{Prokofiev2009,Prokofiev14}}
-	\label{fig:NYieldComparedSUPCUP10}
-\end{figure*}
-
-\subsection{Subsection Three}
-
-\subsection{Subsection Four, time of flight spectrum}
-
-\begin{figure}[!t]
-	\centering
-	\subfloat[Time of flight spectrum at the CUP-TOF position, with \SI{3}{\cm} collimator]{\includegraphics[width=3in]{TOF3frameoverlap.eps}
-	\label{fig:TOFFrameOverlapspectrum}}
-	\vfil
-	\subfloat[Time of flight spectrum at the SUP, with \SI{10.2}{\cm} collimator]{\includegraphics[width=3in]{SUP10frameoverlap.eps}
-	\label{fig:SUP10FrameOverlapspectrum}}
-\end{figure}
-
-\subsection{Subsection Five, beam profile folding with $^{238}U(n,f)$ cross-section}
-
-\begin{figure}[!t]
-	\centering
-	\subfloat[\SI{3}{\cm} collimator]{\includegraphics[width=2.5in]{CUPTOF3beampro.png}
-	\label{fig:CUPTOF3beampro}}
-	\hfil
-	\subfloat[\SI{10.2}{\cm} collimator]{\includegraphics[width=2.5in]{CUPTOF10beampro.png}
-	\label{fig:CUPTOF10beampro}}
-	\hfil
-	\subfloat[\SI{30}{\cm} collimator]{\includegraphics[width=2.5in]{CUPTOF30beampro.png}
-	\label{fig:CUPTOF30beampro}}
-	\caption{Neutron beam profiles folding with $^{238}U(n,f)$ cross-section at the CUP-TOF position with \SI{3}{\cm}, \SI{10.2}{\cm}, and \SI{30}{\cm} collimator}
-	\label{fig:CUPTOFbeamprofileFolding}
-\end{figure}
-
-\begin{figure}[!t]
-	\centering
-	\subfloat[\SI{3}{\cm} collimator]{\includegraphics[width=2.5in]{SUP3beamproFolding.png}
-	\label{fig:SUP3beamproFolding}}
-	\hfill
-	\subfloat[\SI{10.2}{\cm} collimator]{\includegraphics[width=2.5in]{SUP10beamproFolding.png}
-	\label{fig:SUP10beamproFolding}}
-	\hfill
-	\subfloat[\SI{30}{\cm} collimator]{\includegraphics[width=2.5in]{SUP30beamproFolding.png}
-	\label{fig:SUP30beamproFolding}}
-	\caption{Neutron beam profile folding with $^{238}U(n,f)$ cross-section at the SUP with \SI{3}{\cm}, \SI{10.2}{\cm}, and \SI{30}{\cm} collimator}
-	\label{fig:SUPbeamprofileFolding}
-\end{figure}
-
-Fig.~\ref{fig:CUPTOFbeamprofileFolding} shows
-
-%\begin{equation}
-%\label{eq:emc}
-%e = mc^2
-%\end{equation}
-
-\subsection{Gamma, subsection one : Spatial distribution}
-
-\begin{figure}[!t]
-	\centering
-	\subfloat[\SI{3}{\cm} collimator]{\includegraphics[width=3in]{CUP3ColSpatialDistributionAllG}
-	\label{fig:CUP3SpatialDistributionAllG}}
-	\hfil
-	\subfloat[\SI{10.2}{\cm} collimator]{\includegraphics[width=3in]{CUP10ColSpatialDistributionAllG}
-	\label{fig:CUP10SpatialDistributionAllG}}
-	\caption{Gamma spatial distribution at the CUP with \SI{3}{\cm}, and \SI{10.2}{\cm} collimator~\cite{Prokofiev2009,Prokofiev14}}
-	\label{fig:gCUPSpatialDistribution}
-\end{figure}
-
-\begin{table}[!tbp]
-\caption[{$\gamma$ yield for each collimator in a radius of \SI{5}{\cm} at the CUP}]{$\gamma$ yield for each collimator at the CUP}	%title of the table
-\centering
-\label{table:GYieldCUP}
-\begin{tabular}{lcc}
-	\hline% insert double-line
-	Collimator size   & above \SI{1}{\MeV}   &  above \SI{0.1}{\MeV}  \\
-	\cmidrule(r){2-3}
-/\si{\cm}       & /\SI{e-6}{\photon\per\cm\squared\per\proton} & /\SI{e-6}{\photon\per\cm\squared\per\proton} \\
-\hline % insert single-line
-3 & 4.93 & 15.73\\
-
-10.2 & 4.86  &  15.27\\
-
-30 & 4.44  &  13.80\\
-\hline
-\end{tabular}
-\end{table}
-
-\begin{table}[!tbp]
-\caption[$\gamma$ yield for each collimator in umbra region at the SUP]{$\gamma$ yield for each collimator in umbra region at the SUP}	%title of the table
-\centering
-\label{table:GYieldSUP}
-\begin{tabular}{l	c	c}
-\hline% insert double-line
-Collimator size   & above \SI{1}{\MeV}   &  above \SI{0.1}{\MeV}   \\
-\cmidrule(r){2-3}
-/\si{\cm}       & \/\SI{e-6}{\photon\per\cm\squared\per\proton} &  /\SI{e-6}{\photon\per\cm\squared\per\proton} \\
-\hline % insert single-line
-3 & 2.3 & 6.7\\
-
-10.2 & 2.8  &  8.3\\
-
-30 & 3.2  &  9.4\\
-\hline
-\end{tabular}
-\end{table}
-
-\subsection{Gamma, subsection two : Photon spectra at the CUP and SUP }
-
-\begin{figure}[!t]
-	\centering
-	\subfloat[CUP]{\includegraphics[width=3in]{gCUPDYieldcompared}
-	\label{fig:gCUPDYieldcompared}}
-	\vfil
-	\subfloat[SUP]{\includegraphics[width=3in]{gSUPDYieldcompared}
-	\label{fig:gSUPDYieldcompared}}
-	\caption{Comparison of differential photon yield at the CUP and SUP}
-	\label{fig:gDYieldspectra}
-\end{figure}
-
-\begin{figure}[!t]
-	\centering
-	\subfloat[CUP]{\includegraphics[width=3in]{gCUPIYieldcompared}
-	\label{fig:gCUPIYieldcompared}}
-	\vfil
-	\subfloat[SUP]{\includegraphics[width=3in]{gSUPIYieldcompared}
-	\label{fig:gSUPIYieldcompared}}
-	\caption{Comparison of integral photon yield at the CUP and SUP}
-	\label{fig:gIYieldspectra}
-\end{figure}
-Figure~\ref{fig:gIYieldspectra} displayed integral photon spectra at the CUP and SUP.
-The photon spectra at the SUP with \SI{3}{\cm} collimator, it is dominated by energy within about \SI{7}{\MeV} at the SUP, see Figure~\ref{fig:gSUPIYieldcompared}.
-
-\begin{table}
-\caption{$\gamma$ dose rate for each collimator at the CUP and SUP}	%title of the table
-\centering
-\label{Table:DoseRate}
-        \begin{tabular}{l c c}
-            \toprule
-            {collimator diameter}   &{CUP}         &{SUP}\\
-            {\si{\centi\metre}}    &{\si{mSvh^{-1}}}   &{\si{mSvh^{-1}}}\\
-            \midrule
-            3                       & 378.0                	& 17.32\\
-            10.2                  & 369.4               	& 20.90\\
-            30                     & 336.4          		& 23.65\\
-            \bottomrule
-\end{tabular}
-\end{table}
-
-\begin{figure}[!t]
-	\centering
-	\subfloat[CUP]{\includegraphics[width=2.5in]{DoseVSenergyCUP.eps}
-	\label{fig:DoseVSenergyCUP}}
-	\hfil
-	\subfloat[SUP]{\includegraphics[width=2.5in]{DoseVSenergySUP.eps}
-	\label{fig:DoseVSenergySUP}}
-	\caption{Dose versus energy at the CUP and SUP with \SI{3}{\cm}, \SI{10.2}{\cm}, and \SI{30}{\cm} collimators}
-	\label{fig:DoseVSenergy}
-\end{figure}
-
-%------------------------------------------------
 \section{Discussion}
-
-\subsection{Subsection One}
-
-Neutron .....
-
-\subsection{Subsection Two}
-
-Gamma .....
-
-%----------------------------------------------------------------------------------------
-%	REFERENCE LIST
-%----------------------------------------------------------------------------------------
+\todo{Discussion}
 
@@
 \fi
+
+\todo{Complete citations}
 

### 2015-04-16 Paper2015.tex
Using 11pt instead of 12pt.
working progress

@@
 % Paper 2015
-\documentclass[12pt,journal]{IEEEtran}
+\documentclass[11pt,a4paper]{IEEEtran}
 
@@
 Description of the geometry is given in \cite{Prokofiev2009,Prokofiev14}; a summary only is given here.
-The spallation target is a tungsten cylinder of diameter \SI{0}{\cm} and length \SI{0}{\cm}.
+The spallation target is a tungsten cylinder of diameter \SI{5}{\cm} and length \SI{2.4}{\cm}.
 The target is cooled by water and surrounded by a stainless-steel cooling jacket.
@@
 
-Simulations were conducted using Geant4 version~TBD.
-The TBD intranuclear cascade model was selected in accordance with the results of earlier work~\cite{Platt13}, in which it performed well in simulations of neutron spallation in the region from \SIrange{0}{0}{\MeV}.\todo{Enter neutron energy range}
+Simulations were conducted using Geant4 version 10.0.
+The binary intranuclear cascade model was selected in accordance with the results of earlier work~\cite{Platt13}, in which it performed well in simulations of neutron spallation in the region from \SIrange{0}{0}{\MeV}.\todo{Enter neutron energy range}
 In the simulation protons were incident axially at an energy of \SI{180}{\MeV}.
 Resulting gamma and neutron fields were evaluated at several locations.
-In this paper results are presented for three of these: The Standard User Position (SUP), \SI{2.5}{\m} downstream of the target centre\todo{check centre}~\cite{Prokofiev2009}, the Close User Position (CUP), \SI{0}{\m} downstream of the target, and the CUP-TOF, \SI{0}{m} downstream of the target.\todo{Enter CUP \& CUP-TOF ranges}
+In this paper results are presented for three of these: The Standard User Position (SUP), \SI{2.5}{\m} downstream of the target centre\todo{check centre}~\cite{Prokofiev2009}, the Close User Position (CUP), \SI{0.75}{\m} downstream of the target, and the CUP-TOF, \SI{0.84}{m} downstream of the target.\todo{Enter CUP \& CUP-TOF ranges}
 The SUP, CUP and CUP-TOF positions are visible in blue in Fig.~\ref{fig:ANITAoverview}.
@@
     \vspace{2in}
-    \todo{Show density of neutrons above \SI{10}{\MeV} at SUP}
+    \includegraphics[width=3in]{SUP10ColSpatialDistribution10MeVRADECS.png}
+% \todo{Show density of neutrons above \SI{10}{\MeV} at SUP}
     \caption{Neutron fluence rate above \SI{10}{\MeV} at the Standard User Position.}
@@
     \vspace{2in}
-    \todo{Show SUP profile, compared to measurements}
+    \includegraphics[width=3in]{SUP10beamproFoldingRADECS.png}
+% \todo{Show SUP profile, compared to measurements}
     \caption{Neutron profile at the Standard User Position}
@@
     \vspace{2in}
-	\subfloat[Integral fluence rate]{\todo{Integral spectra on log-log axes}\hspace{\columnwidth}}\\
+%	\subfloat[Integral fluence rate]{\todo{Integral spectra on log-log axes}\hspace{\columnwidth}}\\
+	\subfloat[Integral fluence rate]{\includegraphics[width=3in]{ANITAIntYieldRADECS.eps}\hspace{\columnwidth}}\\
     \vspace{2in}
-	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\todo{Normalised spectra on lethargy axes}\hspace{\columnwidth}}
+%	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\todo{Normalised spectra on lethargy axes}\hspace{\columnwidth}}
+	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\includegraphics[width=3in]{ANITALetYieldnormalisedRADECS.eps}\hspace{\columnwidth}}
 	\caption{Neuton spectrum at the SUP, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from a naked Geant4 model~\cite{Platt13} and this work.}
@@
     \vspace{2in}
-    \todo{Show density of neutrons above \SI{10}{\MeV} at CUP}
+    \includegraphics[width=3in]{CUP10ColSpatialDistribution10MeV.png}
+% \todo{Show density of neutrons above \SI{10}{\MeV} at CUP}
     \caption{Neutron fluence rate above \SI{10}{\MeV} at the Close User Position.}
@@
     \vspace{2in}
-    \todo{Show CUP profile, compared to measurements}
+    \includegraphics[width=3in]{CUPTOF10beamproRADECS.png}
+% \todo{Show CUP profile, compared to measurements}
     \caption{Neutron profile at the Close User Position}
@@
     \subfloat[SUP]{
+%	SUP10ColSpatialDistributionAllG
         \todo{Add gamma spatial distribution at SUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
@@
     \subfloat[CUP]{
+%    CUP10ColSpatialDistributionAllG
         \todo{Add gamma spatial distribution at CUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
@@
     \hspace{\columnwidth}
+    \includegraphics[width=3in]{gDYieldcomparedRADECS.eps}
     \caption{Calculated differential gamma spectra at CUP and SUP}

### 2015-04-16 Paper2015.tex
Add eps and png files
Updated authors to include Elke.
working process

@@
 \author{Q. Hong,
-S. P. Platt,~\IEEEmembership{Member,~IEEE}
-Alexander V. Prokofiev,~\IEEEmembership{Member,~IEEE}
+S. P. Platt,
+A. V. Prokofiev,
+E. Passoth
 \thanks{further information}\\[2mm] 	% Your name
@@
 %	\subfloat[Integral fluence rate]{\todo{Integral spectra on log-log axes}\hspace{\columnwidth}}\\
-	\subfloat[Integral fluence rate]{\includegraphics[width=3in]{ANITAIntYieldRADECS.eps}\hspace{\columnwidth}}\\
+	\subfloat[Integral fluence rate]{\includegraphics[width=3in]{SUPcomparedIFluxRADECS.eps}\hspace{\columnwidth}}\\
     \vspace{2in}
 %	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\todo{Normalised spectra on lethargy axes}\hspace{\columnwidth}}
-	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\includegraphics[width=3in]{ANITALetYieldnormalisedRADECS.eps}\hspace{\columnwidth}}
+	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\includegraphics[width=3in]{SUPNormalisedRADECS.eps}\hspace{\columnwidth}}
 	\caption{Neuton spectrum at the SUP, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from a naked Geant4 model~\cite{Platt13} and this work.}

### 2015-04-17 Paper2015.tex
working processing
working process

@@
 \begin{figure}[t]
-    \vspace{2in}
+%    \vspace{2in}
     \includegraphics[width=3in]{SUP10ColSpatialDistribution10MeVRADECS.png}
@@
 \begin{figure}[t]
-    \vspace{2in}
+%    \vspace{2in}
     \includegraphics[width=3in]{SUP10beamproFoldingRADECS.png}
@@
 \begin{figure}[t]
-    \vspace{2in}
+%    \vspace{2in}
 %	\subfloat[Integral fluence rate]{\todo{Integral spectra on log-log axes}\hspace{\columnwidth}}\\
 	\subfloat[Integral fluence rate]{\includegraphics[width=3in]{SUPcomparedIFluxRADECS.eps}\hspace{\columnwidth}}\\
-    \vspace{2in}
+%    \vspace{2in}
 %	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\todo{Normalised spectra on lethargy axes}\hspace{\columnwidth}}
@@
 \begin{figure}[t]
-    \vspace{2in}
+%    \vspace{2in}
     \includegraphics[width=3in]{CUP10ColSpatialDistribution10MeV.png}
@@
 \begin{figure}[t]
-    \vspace{2in}
+%    \vspace{2in}
     \includegraphics[width=3in]{CUPTOF10beamproRADECS.png}
@@
 \begin{figure}[t]
-    \vspace{2in}
-	\subfloat[Integral fluence rate]{\todo{Integral spectra on log-log axes: CUP}\hspace{\columnwidth}}\\
-    \vspace{2in}
-	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\todo{Normalised spectra on lethargy axes: CUP}\hspace{\columnwidth}}
+%    \vspace{2in}
+	\subfloat[Integral fluence rate]{\includegraphics[width=2.5in]{CUPcomparedProkofiev2014linearspaceIFlux.eps}\hspace{\columnwidth}}\\
+%    \vspace{2in}
+	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\includegraphics[width=3in]{CUPcomparedLetFluxRADECS.png}\hspace{\columnwidth}}
 	\caption{Neuton spectrum at the Close User Position, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from this work.}
@@
     \vspace{2in}
-    \subfloat[SUP]{
-%	SUP10ColSpatialDistributionAllG
-        \todo{Add gamma spatial distribution at SUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
+    \subfloat[SUP]{\includegraphics[width=3in]{SUP10ColSpatialDistributionAllG.png}
+%     \todo{Add gamma spatial distribution at SUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
         \label{fig:GammaSpatialDistributionSUP}
     }\\
-    \subfloat[CUP]{
-%    CUP10ColSpatialDistributionAllG
-        \todo{Add gamma spatial distribution at CUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
+    \subfloat[CUP]{\includegraphics[width=3in]{CUP10ColSpatialDistributionAllG.png}
+%     \todo{Add gamma spatial distribution at CUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
         \label{fig:GammaSpatialDistributionCUP}
@@
     \subfloat[SUP]{
-        \todo{Add gamma dose versus energy at SUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
+%	\todo{Add gamma dose versus energy at SUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
+        \includegraphics[width=3in]{DoseVSenergySUP.eps}\hspace{\columnwidth}
         \label{fig:GammaDoseEnergySUP}
@@
     \subfloat[CUP]{
-        \todo{Add gamma dose versus energy at CUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
+%     \todo{Add gamma dose versus energy at CUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
+        \includegraphics[width=3in]{DoseVSenergyCUP.eps}\hspace{\columnwidth}
         \label{fig:GammaDoseEnergyCUP}

### 2015-04-17 Paper2015.tex
working process, and no Time of flight spectra at CUP and SUP

@@
 %    \vspace{2in}
-	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\includegraphics[width=3in]{CUPcomparedLetFluxRADECS.png}\hspace{\columnwidth}}
+	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\includegraphics[width=3in]{CUPcomparedProkofiev2014NormalisedRADECS.eps}\hspace{\columnwidth}}
 	\caption{Neuton spectrum at the Close User Position, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from this work.}
@@
     \vspace{2in}
-    \todo{Show Comparison between Geant4 and MCNPX calculations}
-    \caption{Calculated neutron spectra at the CUP-TOF position, compared to independent MCPX calculations~\cite{Prokofiev14}}
+    \includegraphics[width=3in]{TOFcomparedLetFluxRADECS.png}
+% \todo{Show Comparison between Geant4 and MCNPX calculations}
+    \caption{Calculated neutron spectra at the CUP-TOF position, compared to independent MCNPX calculations~\cite{Prokofiev14}}
     \label{fig:MCComparison}

### 2015-04-17 Paper2015.tex
Work in progress.

--- 2015-04-16 Paper2015.tex
@@
 \begin{document}
-%----------------------------------------------------------------------------------------
-%	TITLE SECTION
-%----------------------------------------------------------------------------------------
-\title{Monte Carlo calculation to characterize neutron and gamma fields for ANITA neutron facility at TSL}
 
-\author{Q. Hong,
+\title{
+    Monte Carlo calculation to characterize neutron and gamma fields for ANITA neutron facility at TSL
+}
+
+\author{%
+    Q. Hong,
     S. P. Platt,
@@
     E. Passoth
-\thanks{further information}\\[2mm] 	% Your name
-%\normalsize University of Central Lancashire \\ 							% Your institution
-%\normalsize \href{qhong@uclan.ac.uk} 								% Your email address
-\vspace{-5mm}
+    \thanks{%
+        Qian Hong and Simon Platt are with the University of Central Lancashire, England. Alexander Prokofiev and Elke Passoth are with the The Svedberg Laboratory, University of Uppsala, Sweden.
     }
-
-%----------------------------------------------------------------------------------------
+}
 
@@
 \todo{Check title, affiliations etc.}
-%----------------------------------------------------------------------------------------
-%	ABSTRACT
-%----------------------------------------------------------------------------------------
 
@@
 \end{abstract}
-
-%----------------------------------------------------------------------------------------
-%	KEYWORDS
-%----------------------------------------------------------------------------------------
-
-%----------------------------------------------------------------------------------------
-%	ARTICLE CONTENTS
-%----------------------------------------------------------------------------------------
-
-\IEEEpeerreviewmaketitle
 
@@
 In addition, we are intested in the gamma field at CUP and SUP in spallation neutron source at the ANITA neutron facility at TSL for SEE testing.
-%------------------------------------------------
 
@@
 \begin{figure}[t]
-    \vspace{2in}
     \includegraphics[width=3in]{SUP10ColSpatialDistribution10MeVRADECS.png}
 % \todo{Show density of neutrons above \SI{10}{\MeV} at SUP}
-    \caption{Neutron fluence rate above \SI{10}{\MeV} at the Standard User Position.}
+    \caption{Spatial distribution of neutrons above \SI{10}{\MeV} at the Standard User Position.}
     \label{fig:SUPDensity}
@@
 \begin{figure}[t]
-    \vspace{2in}
     \includegraphics[width=3in]{SUP10beamproFoldingRADECS.png}
@@
 \begin{figure}[t]
-    \vspace{2in}
-%	\subfloat[Integral fluence rate]{\todo{Integral spectra on log-log axes}\hspace{\columnwidth}}\\
-	\subfloat[Integral fluence rate]{\includegraphics[width=3in]{SUPcomparedIFluxRADECS.eps}\hspace{\columnwidth}}\\
-    \vspace{2in}
-%	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\todo{Normalised spectra on lethargy axes}\hspace{\columnwidth}}
-	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\includegraphics[width=3in]{SUPNormalisedRADECS.eps}\hspace{\columnwidth}}
+	\subfloat[Integral fluence rate]{\includegraphics[width=3in]{ANITAIntYieldRADECS.eps}}\\
+	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\includegraphics[width=3in]{ANITALetYieldnormalisedRADECS.eps}}
 	\caption{Neuton spectrum at the SUP, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from a naked Geant4 model~\cite{Platt13} and this work.}
@@
 \begin{figure}[t]
-    \vspace{2in}
     \includegraphics[width=3in]{CUP10ColSpatialDistribution10MeV.png}
 % \todo{Show density of neutrons above \SI{10}{\MeV} at CUP}
-    \caption{Neutron fluence rate above \SI{10}{\MeV} at the Close User Position.}
+    \caption{Spatial distribution of neutrons above \SI{10}{\MeV} at the Close User Position.}
     \label{fig:CUPDensity}
@@
 \begin{figure}[t]
-    \vspace{2in}
     \includegraphics[width=3in]{CUPTOF10beamproRADECS.png}
@@
 
-\begin{figure}
+\begin{figure}[t]
     \centering
@@
 
-\begin{figure}
+\begin{figure}[t]
     \centering
-    \vspace{2in}
-    \hspace{\columnwidth}
     \includegraphics[width=3in]{gDYieldcomparedRADECS.eps}
@@
 \todo{Discussion}
-
-\ifCLASSOPTIONcaptionsoff
-  \newpage
-\fi
 
@@
 
-%----------------------------------------------------------------------------------------
+\cleardoublepage
 

### 2015-04-17 Paper2015.tex
Condensed modelling section and updated early part of results section.

@@
 \section{Modelling}
-
-A detailed model of the ANITA geometry was implemented in Geant4.
-This is illustrated in overview in Fig.~\ref{fig:ANITAoverview}
-Description of the geometry is given in \cite{Prokofiev2009,Prokofiev14}; a summary only is given here.
-The spallation target is a tungsten cylinder of diameter \SI{5}{\cm} and length \SI{2.4}{\cm}.
-The target is cooled by water and surrounded by a stainless-steel cooling jacket.
-The target assembly with its cooling jacket appears as a small blue rectangle in Fig.~\ref{fig:ANITAoverview}.
-Lead shielding blocks in the target region are also modelled, and shown in red Fig.~\ref{fig:ANITAoverview}.
-A large electromagnet surrounding the target is modelled and shown in Fig.~\ref{fig:ANITAoverview} in grey (iron) and yellow (copper).
-An iron collimator with variable apertures is modelled  and shown downstream of the target (grey).
-For brevity in this summary we only present results for the standard collimator size (\SI{10.2}{\cm} diameter); in the final paper we will present results for cylindrical collimators in the range from \SIrange{3}{30}{\cm} diameter.
+Simulations were conducted using Geant4 version 10.0 and the binary intranuclear cascade model, as recommended in~\cite{Platt13}.
+A detailed model of the ANITA geometry was implemented in Geant4, as illustrated in Fig.~\ref{fig:ANITAoverview}
+Description of the geometry is given in \cite{Prokofiev2009,Prokofiev14}.
+%; a summary only is given here.
+%The spallation target is a tungsten cylinder of diameter \SI{5}{\cm} and length \SI{2.4}{\cm}.
+%The target is cooled by water and surrounded by a stainless-steel cooling jacket.
+%The target assembly with its cooling jacket appears as a small blue rectangle in Fig.~\ref{fig:ANITAoverview}.
+%Lead shielding blocks in the target region are also modelled, and shown in red Fig.~\ref{fig:ANITAoverview}.
+%A large electromagnet surrounding the target is modelled and shown in Fig.~\ref{fig:ANITAoverview} in grey (iron) and yellow (copper).
+%An iron collimator with variable apertures is modelled  and shown downstream of the target (grey).
+Except where indicated otherwise, all results in this summary are for the standard collimator size (\SI{10.2}{\cm} diameter).
+In the final paper we will present results for cylindrical collimators in the range from \SIrange{3}{30}{\cm} diameter.
+Simulated protons were incident axially at an energy of \SI{180}{\MeV}.
+Resulting gamma and neutron fields were evaluated at several detector locations.
+In this paper results are presented for three of these: the Standard User Position (SUP), \SI{2.5}{\m} downstream of the target centre\todo{check centre}~\cite{Prokofiev2009}, the Close User Position (CUP), \SI{0.75}{\m} downstream of the target, and the CUP-TOF, \SI{0.84}{m} downstream of the target.
+The SUP and CUP positions are of interest as they are positions used for SEE tests; the CUP-TOF position is the location of thin-film breakdown counter (TFBC) detectors used for beam monitoring and characterisation using time-of-flight (TOF) techniques.
+Model validation will be demonstrated against CUP-TOF data (section~\ref{tbd}).
 
@@
 
-Simulations were conducted using Geant4 version 10.0.
-The binary intranuclear cascade model was selected in accordance with the results of earlier work~\cite{Platt13}, in which it performed well in simulations of neutron spallation in the region from \SIrange{0}{0}{\MeV}.\todo{Enter neutron energy range}
-In the simulation protons were incident axially at an energy of \SI{180}{\MeV}.
-Resulting gamma and neutron fields were evaluated at several locations.
-In this paper results are presented for three of these: The Standard User Position (SUP), \SI{2.5}{\m} downstream of the target centre\todo{check centre}~\cite{Prokofiev2009}, the Close User Position (CUP), \SI{0.75}{\m} downstream of the target, and the CUP-TOF, \SI{0.84}{m} downstream of the target.\todo{Enter CUP \& CUP-TOF ranges}
-The SUP, CUP and CUP-TOF positions are visible in blue in Fig.~\ref{fig:ANITAoverview}.
-The SUP and CUP positions are of interest as they are positions used for SEE tests; the CUP-TOF position is the location of thin-film breakdown counter (TFBC) detectors used for beam monitoring and characterisation using time-of-flight (TOF) techniques.
-Model validation will be demonstrated against CUP-TOF data (section~\ref{tbd}).
-
-%------------------------------------------------
 \section{Results}
-
 In previous work Platt et al.~\cite{Platt13} reported simulations of a naked ANITA target, demonstrating good qualitative agreement with independent calculations and measurements of the fast neutron field at ANITA SUP~\cite{Prokofiev2009}.
@@
 \subsection{Neutron fluence rate, spatial distribution and spectrum}
-
-Fig.~\ref{fig:SUPDensity} shows neutron spatial distribution at the SUP.
+Fig.~\ref{fig:SUPDensity} shows neutron spatial distribution at the SUP, for neutrons above \SI{10}{\MeV}.
 The collimation effect is clearly visible.
-Fig.~\ref{fig:SUPProfile} compares simulated and measured neutron fluence profile at the SUP.
-Measurements were taken with a TFBC in which \U238\ is the target material~\cite{Prokofiev2009}; accordingly, simulated results were folded in energy with the neutron fission cross section for \U238~\cite{tbd}.
-The results show~\todo{Explain SUP profile results. Include explanation of ``umbra'' and ``penumbra''}
-The predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{0}{\neutron\per\cm\squared\per\second}, compared to \SI{0}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt13} and \SI{0}{\neutron\per\cm\squared\per\second} from the parameterisation~\cite{Prokofiev2009}.
+Fig.~\ref{fig:SUPProfile} shows neutron fluence profile at the SUP.
+In Fig.~\ref{fig:SUPProfile} simulated data were folded in energy with the neutron fission cross section for \U238~\cite{tbd}, replicating measurement with a \U238\ TFBC~\cite{Prokofiev2009}.
+Within the beam umbra the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{0}{\neutron\per\cm\squared\per\second}, compared to \SI{0}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt13} and \SI{0}{\neutron\per\cm\squared\per\second} from the parameterisation~\cite{Prokofiev2009}.
 The parameterisation therefore exceeds the current calculations by tbd\%.\todo{Quantify integral yield}
@@
     \includegraphics[width=3in]{SUP10ColSpatialDistribution10MeVRADECS.png}
-% \todo{Show density of neutrons above \SI{10}{\MeV} at SUP}
-    \caption{Spatial distribution of neutrons above \SI{10}{\MeV} at the Standard User Position.}
+    \caption{
+        Spatial distribution of neutrons above \SI{10}{\MeV} at the SUP.
+        Concentric white circles indicate nominal umbra and penumbra limits.
+    }
     \label{fig:SUPDensity}
@@
     \includegraphics[width=3in]{SUP10beamproFoldingRADECS.png}
-% \todo{Show SUP profile, compared to measurements}
-    \caption{Neutron profile at the Standard User Position}
+    \caption{
+        Neutron profile at the SUP, normalised to fluence rate on axis.
+        Vertical lines indicate nominal umbra and penumbra limits.
+    }
     \label{fig:SUPProfile}

### 2015-04-17 Paper2015.tex
All images, updated

--- 2015-04-17 Paper2015.tex
@@
     \vspace{2in}
-    \includegraphics[width=3in]{TOFcomparedLetFluxRADECS.png}
+    \includegraphics[width=3in]{TOFcomparedLetFluxRADECS}
 % \todo{Show Comparison between Geant4 and MCNPX calculations}
@@
 	\centering
-	\subfloat[At the CUP-TOF position, with \SI{3}{\cm} collimator]{\todo{Add experimental data to TOF figure (CUP)\includegraphics[width=3in]{TOF3frameoverlap.eps}}
+	\subfloat[At the CUP-TOF position, with \SI{3}{\cm} collimator]{\todo{Add experimental data to TOF figure (CUP)\includegraphics[width=3in]{CUPTOFtofspectraRADECS.png}}
 	\label{fig:TOFFrameOverlapspectrum}}\\
-	\subfloat[At the SUP, with \SI{10.2}{\cm} collimator]{\todo{Add experimental data to TOF figure (SUP)}\includegraphics[width=3in]{SUP10frameoverlap.eps}
+	\subfloat[At the SUP, with \SI{10.2}{\cm} collimator]{\todo{Add experimental data to TOF figure (SUP)}\includegraphics[width=3in]{SUPtofspectraRADECS.png}
 	\label{fig:SUP10FrameOverlapspectrum}}

### 2015-04-17 Paper2015.tex
Several efforts made to correct bad spacing. Eventually, this seems to have been caused by the stfloats package.
Also now using subcaption package.
Also removed some redundant preamble content.

--- 2015-04-17 Paper2015.tex
@@
 
-% *** MISC UTILITY PACKAGES ***
-%
 \usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-   % pdf code
- %\else
-   % dvi code
-% \fi
-
-% *** CITATION PACKAGES ***
-%
 \usepackage{cite}
 
-% *** GRAPHICS RELATED PACKAGES ***
-%
 \ifCLASSINFOpdf
@@
 
-% *** MATH PACKAGES ***
-%
 \usepackage[cmex10]{amsmath}
 
-% *** SPECIALIZED LIST PACKAGES ***
-%
-\usepackage{algorithmic}
-
-% *** ALIGNMENT PACKAGES ***
-%
 \usepackage{array}
-
-% *** SUBFIGURE PACKAGES ***
-\ifCLASSOPTIONcompsoc
-  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-\else
-  \usepackage[caption=false,font=footnotesize]{subfig}
-\fi
-
-% *** FLOAT PACKAGES ***
-%
 \usepackage{fixltx2e}
-
-\usepackage{stfloats}
 
@@
 
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
 \usepackage{url}
@@
 \usepackage{booktabs}
+
 \usepackage{graphicx}
 \usepackage{epstopdf}
-\usepackage{subfig}
+
+\usepackage{caption}
+\usepackage{subcaption}
+\captionsetup{margin={0pt,20pt}}
+\captionsetup[sub]{margin={0pt,20pt}}
 
 \usepackage{todo}
+%\renewcommand\todo[1]{\relax}
+%\renewcommand\todos{\relax}
 
@@
 
-\begin{figure}[!t]
+\begin{figure}[t]
 	\centering
-	\includegraphics[width=3in]{overview.png}
-	\caption{Simulated ANITA facility overview seen from above (yellow: bending magnet; red: shielding components; blue: target cooling jacket (enclosing the target); grey: collimator; blue: detector system)}
+	\includegraphics[width=2.5in]{overview.png}
+	\caption{
+        Simulated ANITA facility overview seen from above (yellow: bending magnet; red: shielding components; blue: target cooling jacket (enclosing the target); grey: collimator; blue: detector system)
+    }
 	\label{fig:ANITAoverview}
@@
 \begin{figure}[t]
-    \includegraphics[width=3in]{SUP10ColSpatialDistribution10MeVRADECS.png}
+    \includegraphics[width=2.5in]{SUP10ColSpatialDistribution10MeVRADECS.png}
     \caption{
@@
 \begin{figure}[t]
-    \includegraphics[width=3in]{SUP10beamproFoldingRADECS.png}
+    \includegraphics[width=2.5in]{SUP10beamproFoldingRADECS.png}
     \caption{
@@
 Fig.~\ref{fig:SUPSpectraComparison} compares calculated neutron yield versus energy in the umbra at the SUP with that predicted by the naked-target simulation~\cite{Platt13} and with the standard ANITA SUP parameterisation~\cite{Prokofiev2009}.
-The results show\ldots\todo{Discuss the results. Compare current with earlier calculations. Compare calculations with parameterisation.}
+The results show\ldots
+\todo{Discuss the results. Compare current with earlier calculations. Compare calculations with parameterisation.}
 
 \begin{figure}[t]
-	\subfloat[Integral fluence rate]{\includegraphics[width=3in]{ANITAIntYieldRADECS.eps}}\\
-	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\includegraphics[width=3in]{ANITALetYieldnormalisedRADECS.eps}}
-	\caption{Neuton spectrum at the SUP, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from a naked Geant4 model~\cite{Platt13} and this work.}
+    \begin{minipage}{\columnwidth}
+        \includegraphics[width=2.5in]{ANITAIntYieldRADECS.eps}
+        \subcaption{Integral fluence rate}
+    \end{minipage}
+    \begin{minipage}{\columnwidth}
+        \includegraphics[width=2.5in]{ANITALetYieldnormalisedRADECS.eps}
+        \subcaption{Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}}
+    \end{minipage}
+	\caption{
+        Neutron spectrum at the SUP, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from a naked Geant4 model~\cite{Platt13} and this work.
+    }
 	\label{fig:SUPSpectraComparison}
@@
 Fig.~\ref{fig:CUPDensity} and Fig.~\ref{fig:CUPProfile} show neutron spatial distribution (for neutrons above \SI{10}{\MeV}) and profile (folded in energy with the \U238\ fission cross-section) at the CUP.
-The results show\ldots\todo{Describe the results: contours and profile at CUP}
+The results show\ldots
+\todo{Describe the results: contours and profile at CUP}
 
 \begin{figure}[t]
-    \includegraphics[width=3in]{CUP10ColSpatialDistribution10MeV.png}
+    \centering
+    \includegraphics[width=2.5in]{CUP10ColSpatialDistribution10MeV.png}
 % \todo{Show density of neutrons above \SI{10}{\MeV} at CUP}
-    \caption{Spatial distribution of neutrons above \SI{10}{\MeV} at the Close User Position.}
+    \caption{Spatial distribution of neutrons above \SI{10}{\MeV} at the CUP}
     \label{fig:CUPDensity}
@@
 \begin{figure}[t]
-    \includegraphics[width=3in]{CUPTOF10beamproRADECS.png}
+    \centering
+    \includegraphics[width=2.5in]{CUPTOF10beamproRADECS.png}
     % \todo{Show CUP profile, compared to measurements}
-    \caption{Neutron profile at the Close User Position}
+    \caption{Neutron profile at the CUP}
     \label{fig:CUPProfile}
@@
 
-Fig.~\ref{fig:CUPSpectraCOmparison} compares the spectrum calculated at the CUP with that from the standard parameterisation~\cite{Prokofiev14}.
+Fig.~\ref{fig:CUPSpectraComparison} compares the spectrum calculated at the CUP with that from the standard parameterisation~\cite{Prokofiev14}.
 The latter curve is derived from MCNPX calculations supported by TOF measurements with TFBCs.
-The results show\ldots\todo{Explain what the results show: CUP measurement comparison.}
+The results show\ldots
+\todo{Explain what the results show: CUP measurement comparison.}
 Fig.~\ref{fig:MCComparison} provides a direct comparison between the two Monte Carlo calculations.
-The results show\ldots\todo{Explain what the results show (comparison between independent MC calculations).}
+The results show\ldots
+\todo{Explain what the results show (comparison between independent MC calculations).}
 
 \begin{figure}[t]
-    \vspace{2in}
-	\subfloat[Integral fluence rate]{\todo{Integral spectra on log-log axes: CUP}\hspace{\columnwidth}}\\
-    \vspace{2in}
-	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\todo{Normalised spectra on lethargy axes: CUP}\hspace{\columnwidth}}
-	\caption{Neuton spectrum at the Close User Position, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from this work.}
+    \begin{minipage}{\columnwidth}
+        \todo{Integral spectra on log-log axes: CUP}
+        %\includegraphics[draft,width=2.5in]{CUPTOF10beamproRADECS.png}
+    	\subcaption{Integral fluence rate}
+    \end{minipage}
+    \begin{minipage}{\columnwidth}
+        %\includegraphics[draft,width=2.5in]{CUPTOF10beamproRADECS.png}
+        \todo{Normalised spectra on lethargy axes: CUP}
+    	\subcaption{Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}}
+    \end{minipage}
+	\caption{
+        Neutron spectrum at the Close User Position, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from this work.
+    }
 	\label{fig:CUPSpectraComparison}
@@
 \begin{figure}[t]
-    \vspace{2in}
     \todo{Show Comparison between Geant4 and MCNPX calculations}
-    \caption{Calculated neutron spectra at the CUP-TOF position, compared to independent MCPX calculations~\cite{Prokofiev14}}
+    %\includegraphics[draft,width=2.5in]{CUPTOF10beamproRADECS.png}
+    \caption{
+        Calculated neutron spectra at the CUP-TOF position, compared to independent MCPX calculations~\cite{Prokofiev14}
+    }
     \label{fig:MCComparison}
@@
     \centering
-    \includegraphics[width=3in]{DiffYieldComparedSUPCUP10.eps}
-    \caption{Differential neutron spectra at CUP and SUP, comparing results of this work to facility parameterisations~\cite{Prokofiev2009,Prokofiev14}}
+    \includegraphics[width=2.5in]{DiffYieldComparedSUPCUP10.eps}
+    \caption{
+        Differential neutron spectra at CUP and SUP, comparing results of this work to facility parameterisations~\cite{Prokofiev2009,Prokofiev14}
+    }
     \label{fig:DifferentialSpectra}
@@
 \subsection{Neutron time of flight}
-
 Neutron beam monitoring and characterisation at TSL uses time-of flight measurements with \U238\ TFBCs.
@@
 
-\begin{figure}[!t]
-	\centering
-	\subfloat[At the CUP-TOF position, with \SI{3}{\cm} collimator]{\todo{Add experimental data to TOF figure (CUP)\includegraphics[width=3in]{TOF3frameoverlap.eps}}
-	\label{fig:TOFFrameOverlapspectrum}}\\
-	\subfloat[At the SUP, with \SI{10.2}{\cm} collimator]{\todo{Add experimental data to TOF figure (SUP)}\includegraphics[width=3in]{SUP10frameoverlap.eps}
-	\label{fig:SUP10FrameOverlapspectrum}}
+\begin{figure}[t]
+    \begin{minipage}{\columnwidth}
+        \todo{Add experimental data to TOF figure (CUP)}
+        \includegraphics[width=2.5in]{TOF3frameoverlap.eps}
+        \subcaption{At the CUP-TOF position, with \SI{3}{\cm} collimator}
+    	\label{fig:TOFFrameOverlapspectrum}
+    \end{minipage}
+    \begin{minipage}{\columnwidth}
+        \todo{Add experimental data to TOF figure (SUP)}
+        \includegraphics[width=2.5in]{SUP10frameoverlap.eps}
+        \subcaption{At the SUP, with \SI{10.2}{\cm} collimator}
+        \label{fig:SUP10FrameOverlapspectrum}
+    \end{minipage}
     \caption{Simulated neutron time of flight spectra compared to measurements}
@@
 
-\begin{figure}[!t]
+\begin{figure}[t]
 	\centering
-	\includegraphics[width=3in]{TOF3Componentslinear.eps}
+	\includegraphics[width=2.5in]{TOF3Componentslinear.eps}
 	\caption{
         Simulated neutron yield with \SI{3}{\cm} collimator at the CUP-TOF position.
-    The three components are directly from the target, scattered forward from the target surroundings, and scattered back from the collimator front wall.}
+        The three components are directly from the target, scattered forward from the target surroundings, and scattered back from the collimator front wall.
+    }
 	\label{fig:TOF3Componentslinear}
@@
 \subsection{Gamma fluence rate, spatial distribution and dose rate}
-
 Fig.~\ref{fig:GammaSpatialDistribution} shows the calculated spatial distribution of gamma photons at SUP and CUP.
@@
 \begin{figure}[t]
-    \centering
-    \vspace{2in}
-    \subfloat[SUP]{
-%	SUP10ColSpatialDistributionAllG
-        \todo{Add gamma spatial distribution at SUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
+    \begin{minipage}{\columnwidth}
+        %\includegraphics[draft,width=2.5in]{CUPTOF10beamproRADECS.png}
+        \todo{Add gamma spatial distribution at SUP, \SI{10.2}{\cm} collimator}
+        \subcaption{SUP}
         \label{fig:GammaSpatialDistributionSUP}
-    }\\
-    \subfloat[CUP]{
-%    CUP10ColSpatialDistributionAllG
-        \todo{Add gamma spatial distribution at CUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
+    \end{minipage}
+    \begin{minipage}{\columnwidth}
+        \todo{Add gamma spatial distribution at CUP, \SI{10.2}{\cm} collimator}
+        %\includegraphics[draft,width=2.5in]{CUPTOF10beamproRADECS.png}
+        \subcaption{CUP}
         \label{fig:GammaSpatialDistributionCUP}
-    }
+    \end{minipage}
     \caption{Gamma spatial distribution}
@@
     \centering
-    \includegraphics[width=3in]{gDYieldcomparedRADECS.eps}
+    \includegraphics[width=2.5in]{gDYieldcomparedRADECS.eps}
     \caption{Calculated differential gamma spectra at CUP and SUP}
@@
 \begin{figure}[t]
-    \centering
-    \vspace{2in}
-    \subfloat[SUP]{
-        \todo{Add gamma dose versus energy at SUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
+    \begin{minipage}{\columnwidth}
+        %\includegraphics[draft,width=2.5in]{CUPTOF10beamproRADECS.png}
+        \todo{Add gamma dose versus energy at SUP, \SI{10.2}{\cm} collimator}
+        \subcaption{SUP}
         \label{fig:GammaDoseEnergySUP}
-    }\\
-    \subfloat[CUP]{
-        \todo{Add gamma dose versus energy at CUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
+    \end{minipage}
+    \begin{minipage}{\columnwidth}
+        %\includegraphics[draft,width=2.5in]{CUPTOF10beamproRADECS.png}
+        \todo{Add gamma dose versus energy at CUP, \SI{10.2}{\cm} collimator}
+        \subcaption{CUP}
         \label{fig:GammaDoseEnergyCUP}
-    }
+    \end{minipage}
     \caption{Gamma dose spectra}

### 2015-04-17 Paper2015.tex

@@
 %; a summary only is given here.
-%The spallation target is a tungsten cylinder of diameter \SI{5}{\cm} and length \SI{2.4}{\cm}.
+%The spallation target is a tungsten cylinder of diameter \SI{5}{\cm} and length \SI{2.4}{\cm}~\cite{ANITAdrawing}.
 %The target is cooled by water and surrounded by a stainless-steel cooling jacket.
@@
 Resulting gamma and neutron fields were evaluated at several detector locations.
-In this paper results are presented for three of these: the Standard User Position (SUP), \SI{2.5}{\m} downstream of the target centre\todo{check centre}~\cite{Prokofiev2009}, the Close User Position (CUP), \SI{0.75}{\m} downstream of the target, and the CUP-TOF, \SI{0.84}{m} downstream of the target.
+In this paper results are presented for three of these: the Standard User Position (SUP), \SI{2.5}{\m} downstream of the target centre\todo{check centre, it said that 250cm downstream of the production target in the paper}~\cite{Prokofiev2009}, the Close User Position (CUP), \SI{0.75}{\m} downstream of the target, and the CUP-TOF, \SI{0.84}{m} downstream of the target.
 The SUP and CUP positions are of interest as they are positions used for SEE tests; the CUP-TOF position is the location of thin-film breakdown counter (TFBC) detectors used for beam monitoring and characterisation using time-of-flight (TOF) techniques.
@@
 In Fig.~\ref{fig:SUPProfile} simulated data were folded in energy with the neutron fission cross section for \U238~\cite{tbd}, replicating measurement with a \U238\ TFBC~\cite{Prokofiev2009}.
-Within the beam umbra the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{0}{\neutron\per\cm\squared\per\second}, compared to \SI{0}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt13} and \SI{0}{\neutron\per\cm\squared\per\second} from the parameterisation~\cite{Prokofiev2009}.
-The parameterisation therefore exceeds the current calculations by tbd\%.\todo{Quantify integral yield}
+Within the beam umbra the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.1e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt13} and \SI{9.3e5}{\neutron\per\cm\squared\per\second} from the parameterisation~\cite{Prokofiev2009}.
+The parameterisation therefore exceeds the current calculations by tbd 31\%.\todo{Quantify integral yield}
 
@@
 
+\bibitem{ANITAdrawing}
+Prokofiev, A.V. 
+\newblock personal communication
+\newblock {\em TSL, Sep. 2013}
+
 \end{thebibliography}

### 2015-04-17 Paper2015.tex
Work in progress.

--- 2015-04-17 Paper2015.tex
@@
     Monte Carlo simulation of spallation neutron source of ANITA at TSL was used to analyze radiation fields at the Close User Position (CUP) and Standard User Position(SUP) for single-event effect testing.
-...\todo{Revise abstract}
+...
+    \todo{Revise abstract}
 \end{abstract}
@@
 Resulting gamma and neutron fields were evaluated at several detector locations.
-In this paper results are presented for three of these: the Standard User Position (SUP), \SI{2.5}{\m} downstream of the target centre\todo{check centre}~\cite{Prokofiev2009}, the Close User Position (CUP), \SI{0.75}{\m} downstream of the target, and the CUP-TOF, \SI{0.84}{m} downstream of the target.
+In this paper results are presented for three of these: the Standard User Position (SUP), \SI{2.5}{\m} downstream of the target centre~\cite{Prokofiev2009}, the Close User Position (CUP), \SI{0.75}{\m} downstream of the target, and the CUP-TOF, \SI{0.84}{m} downstream of the target.
+\todo{check centre}
 The SUP and CUP positions are of interest as they are positions used for SEE tests; the CUP-TOF position is the location of thin-film breakdown counter (TFBC) detectors used for beam monitoring and characterisation using time-of-flight (TOF) techniques.
@@
 	\centering
-	\includegraphics[width=2.5in]{overview.png}
+	\includegraphics[width=\columnwidth]{overview.png}
 	\caption{
@@
 In previous work Platt et al.~\cite{Platt13} reported simulations of a naked ANITA target, demonstrating good qualitative agreement with independent calculations and measurements of the fast neutron field at ANITA SUP~\cite{Prokofiev2009}.
-Part of the motivation for this work was to investigate whether improvements in the fidelity of the geometry used in the Geant4 model would lead to increased quantitative agreement.\todo{Review first part of Results section -- move to introduction?}
+Part of the motivation for this work was to investigate whether improvements in the fidelity of the geometry used in the Geant4 model would lead to increased quantitative agreement.
+\todo{Review first part of Results section -- move to introduction?}
 
@@
 Within the beam umbra the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{0}{\neutron\per\cm\squared\per\second}, compared to \SI{0}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt13} and \SI{0}{\neutron\per\cm\squared\per\second} from the parameterisation~\cite{Prokofiev2009}.
-The parameterisation therefore exceeds the current calculations by tbd\%.\todo{Quantify integral yield}
+The parameterisation therefore exceeds the current calculations by tbd\%.
+\todo{Quantify integral yield}
 
 \begin{figure}[t]
-    \includegraphics[width=2.5in]{SUP10ColSpatialDistribution10MeVRADECS.png}
+    \includegraphics[width=\columnwidth]{SUP10ColSpatialDistribution10MeVRADECS.png}
     \caption{
@@
 \begin{figure}[t]
-    \includegraphics[width=2.5in]{SUP10beamproFoldingRADECS.png}
+    \includegraphics[width=\columnwidth]{SUP10beamproFoldingRADECS.png}
     \caption{
@@
     \begin{minipage}{\columnwidth}
-        \includegraphics[width=2.5in]{ANITAIntYieldRADECS.eps}
+        \includegraphics[width=\columnwidth]{SUPComparedIFluxRADECS.eps}
         \subcaption{Integral fluence rate}
@@
     \begin{minipage}{\columnwidth}
-        \includegraphics[width=2.5in]{ANITALetYieldnormalisedRADECS.eps}
+        \includegraphics[width=\columnwidth]{SUPNormalisedRADECS.eps}
         \subcaption{Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}}
@@
     \centering
-    \includegraphics[width=2.5in]{CUP10ColSpatialDistribution10MeV.png}
-% \todo{Show density of neutrons above \SI{10}{\MeV} at CUP}
+    \includegraphics[width=\columnwidth]{CUP10ColSpatialDistribution10MeV.png}
     \caption{Spatial distribution of neutrons above \SI{10}{\MeV} at the CUP}
     \label{fig:CUPDensity}
+    \todo{Show density of neutrons above \SI{10}{\MeV} at CUP}
 \end{figure}
@@
     \centering
-    \includegraphics[width=2.5in]{CUPTOF10beamproRADECS.png}
-    % \todo{Show CUP profile, compared to measurements}
+    \includegraphics[width=\columnwidth]{CUPTOF10beamproRADECS.png}
     \caption{Neutron profile at the CUP}
     \label{fig:CUPProfile}
+    \todo{Show CUP profile, compared to measurements}
 \end{figure}
@@
     \begin{minipage}{\columnwidth}
+        \includegraphics[width=\columnwidth]{ANITAIntYieldRADECS.eps}
+        \subcaption{Integral fluence rate}
         \todo{Integral spectra on log-log axes: CUP}
-        %\includegraphics[draft,width=2.5in]{CUPTOF10beamproRADECS.png}
-    	\subcaption{Integral fluence rate}
     \end{minipage}
     \begin{minipage}{\columnwidth}
-        %\includegraphics[draft,width=2.5in]{CUPTOF10beamproRADECS.png}
+        \includegraphics[width=\columnwidth]{ANITALetYieldnormalisedRADECS.eps}
+    	\subcaption{Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}}
         \todo{Normalised spectra on lethargy axes: CUP}
-    	\subcaption{Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}}
     \end{minipage}
@@
 \begin{figure}[t]
-    \todo{Show Comparison between Geant4 and MCNPX calculations}
-    %\includegraphics[draft,width=2.5in]{CUPTOF10beamproRADECS.png}
+    \includegraphics[width=\columnwidth]{TOFcomparedLetFluxRADECS.png}
     \caption{
@@
     \label{fig:MCComparison}
+    \todo{Show Comparison between Geant4 and MCNPX calculations}
 \end{figure}
@@
 The SUP calculations and parameterisations agree very closely below \SI{20}{\MeV}; the parameterisation exceeds the calculations somewhat above that energy.
-At CUP the parameterisation exceeds the Geant4 calculations by about TBD\% below \SI{20}{\MeV} and slightly more above that energy.\todo{Improve precision of the summary description of differential spectra.}
+At CUP the parameterisation exceeds the Geant4 calculations by about TBD\% below \SI{20}{\MeV} and slightly more above that energy.
+\todo{Improve precision of the summary description of differential spectra.}
 
@@
     \centering
-    \includegraphics[width=2.5in]{DiffYieldComparedSUPCUP10.eps}
+    \includegraphics[width=\columnwidth]{DiffYieldComparedSUPCUP10.eps}
     \caption{
@@
 The simulated CUP-TOF results were calculated for the \SI{3}{\cm} collimator, to match the available measured data.
-The results show\ldots\todo{Explain what the results show.}
+The results show\ldots
+\todo{Explain what the results show.}
 
@@
     \begin{minipage}{\columnwidth}
-        \todo{Add experimental data to TOF figure (CUP)}
-        \includegraphics[width=2.5in]{TOF3frameoverlap.eps}
+        \includegraphics[width=\columnwidth]{CUPTOFtofspectraRADECS.png}
         \subcaption{At the CUP-TOF position, with \SI{3}{\cm} collimator}
     	\label{fig:TOFFrameOverlapspectrum}
+        \todo{Add experimental data to TOF figure (CUP)}
     \end{minipage}
     \begin{minipage}{\columnwidth}
-        \todo{Add experimental data to TOF figure (SUP)}
-        \includegraphics[width=2.5in]{SUP10frameoverlap.eps}
+        \includegraphics[width=\columnwidth]{SUPtofspectraRADECS.png}
         \subcaption{At the SUP, with \SI{10.2}{\cm} collimator}
         \label{fig:SUP10FrameOverlapspectrum}
+        \todo{Add experimental data to TOF figure (SUP)}
     \end{minipage}
@@
 The complex flight paths and energy losses in the scattered components break the one-to-one relationship between neutron energy and neutron time of flight from target to detector.
-We are able to reproduce this situation in our simulation, as shown by Fig.~\ref{fig:TOF3Componentslinear}, which shows good agreement with\ldots\todo{Complete description of the three components.}
+We are able to reproduce this situation in our simulation, as shown by Fig.~\ref{fig:TOF3Componentslinear}, which shows good agreement with\ldots
+\todo{Complete description of the three components.}
 
@@
 	\centering
-	\includegraphics[width=2.5in]{TOF3Componentslinear.eps}
+	\includegraphics[width=\columnwidth]{TOF3Componentslinear.eps}
 	\caption{
@@
 Fig.~\ref{fig:DifferentialGammaSpectra} shows the calculated differential gamma spectra within the central region of the spatial distribution.
-The results show\ldots\todo{Describe the gamma results}
+The results show\ldots
+\todo{Describe the gamma results}
 
@@
     \begin{minipage}{\columnwidth}
-        %\includegraphics[draft,width=2.5in]{CUPTOF10beamproRADECS.png}
-        \todo{Add gamma spatial distribution at SUP, \SI{10.2}{\cm} collimator}
+        \includegraphics[width=\columnwidth]{SUP10ColSpatialDistributionAllG.png}
         \subcaption{SUP}
@@
     \begin{minipage}{\columnwidth}
-        \todo{Add gamma spatial distribution at CUP, \SI{10.2}{\cm} collimator}
-        %\includegraphics[draft,width=2.5in]{CUPTOF10beamproRADECS.png}
+        \includegraphics[width=\columnwidth]{CUP10ColSpatialDistributionAllG.png}
         \subcaption{CUP}
@@
     \centering
-    \includegraphics[width=2.5in]{gDYieldcomparedRADECS.eps}
+    \includegraphics[width=\columnwidth]{gDYieldcomparedRADECS.eps}
     \caption{Calculated differential gamma spectra at CUP and SUP}
@@
 Fig.~\ref{fig:GammaDoseEnergy} shows the calculated distribution of gamma dose, obtained by folding the gamma spectra (Fig~\ref{fig:GammaDoseEnergy}) with dose conversion data from \cite{tbd}.
-The results show\ldots\todo{Describe the gamma dose versus energy graphs.}
-The calculated dose rate at \SI{200}{\nA} primary proton current is \SI{21}{\milli\gray\per\hour} at SUP and \SI{370}{\milli\gray\per\hour} at CUP.\todo{Discuss calculated dose rates}
+The results show\ldots
+\todo{Describe the gamma dose versus energy graphs.}
+The calculated dose rate at \SI{200}{\nA} primary proton current is \SI{21}{\milli\gray\per\hour} at SUP and \SI{370}{\milli\gray\per\hour} at CUP.
+\todo{Discuss calculated dose rates}
 
@@
     \begin{minipage}{\columnwidth}
-        %\includegraphics[draft,width=2.5in]{CUPTOF10beamproRADECS.png}
-        \todo{Add gamma dose versus energy at SUP, \SI{10.2}{\cm} collimator}
+        \includegraphics[width=\columnwidth]{DoseVSenergySUP.eps}
         \subcaption{SUP}
         \label{fig:GammaDoseEnergySUP}
+        \todo{Add gamma dose versus energy at SUP, \SI{10.2}{\cm} collimator}
     \end{minipage}
     \begin{minipage}{\columnwidth}
-        %\includegraphics[draft,width=2.5in]{CUPTOF10beamproRADECS.png}
-        \todo{Add gamma dose versus energy at CUP, \SI{10.2}{\cm} collimator}
+        \includegraphics[width=\columnwidth]{DoseVSenergyCUP.eps}
         \subcaption{CUP}
         \label{fig:GammaDoseEnergyCUP}
+        \todo{Add gamma dose versus energy at CUP, \SI{10.2}{\cm} collimator}
     \end{minipage}

### 2015-04-17 Paper2015.tex
Modified paper to remove reference to target centre in the geometric description.

@@
 Resulting gamma and neutron fields were evaluated at several detector locations.
-In this paper results are presented for three of these: the Standard User Position (SUP), \SI{2.5}{\m} downstream of the target centre~\cite{Prokofiev2009}, the Close User Position (CUP), \SI{0.75}{\m} downstream of the target, and the CUP-TOF, \SI{0.84}{m} downstream of the target.
-\todo{check centre}
+In this paper results are presented for three of these: the Standard User Position (SUP), \SI{2.5}{\m} downstream of the target~\cite{Prokofiev2009}, the Close User Position (CUP), \SI{0.75}{\m} downstream of the target, and the CUP-TOF, \SI{0.84}{m} downstream of the target.
+%N.B. This is downstream of the downstream edge of the target in Qian's model.
 The SUP and CUP positions are of interest as they are positions used for SEE tests; the CUP-TOF position is the location of thin-film breakdown counter (TFBC) detectors used for beam monitoring and characterisation using time-of-flight (TOF) techniques.

### 2015-04-17 Paper2015.tex

@@
 \todo{Quantify integral yield}
+Within the beam umbra the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.1e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt13} and \SI{9.3e5}{\neutron\per\cm\squared\per\second} from the parameterisation~\cite{Prokofiev2009}.
+The parameterisation therefore exceeds the current calculations by tbd 31\%.\todo{Quantify integral yield}
 

### 2015-04-17 Paper2015.tex
Removed SUP TOF spectra, for conciseness in the abstract.

@@
     \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
     \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
     \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
 \else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
     \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
     \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
     \DeclareGraphicsExtensions{.eps}
@@
 Neutron time of flight data from the simulation (time measured from the time of arrival of primary photons at the target to the time of arrival of secondary neutrons at the point of interest) were folded in energy with the \U238\ fission cross-section, convolved with a \SI{5}{\ns} rectangle function approximating the primary proton micropulse shape, and overlapped at \SI{45}{\ns}, representing the timing ambiguity due to the micropulse period.
-Results are for SUP and CUP-TOF positions and compared with measurements~\cite{Prokofiev2009,Prokofiev14} in Fig.~\ref{fig:TOFSpectra}.
+Results are presented here for the CUP-TOF position and compared with measurements~\cite{Prokofiev14} in Fig.~\ref{fig:TOFSpectra}.
 The simulated CUP-TOF results were calculated for the \SI{3}{\cm} collimator, to match the available measured data.
@@
 \begin{figure}[t]
-    \begin{minipage}{\columnwidth}
     \includegraphics[width=\columnwidth]{CUPTOFtofspectraRADECS.png}
-        \subcaption{At the CUP-TOF position, with \SI{3}{\cm} collimator}
-    	\label{fig:TOFFrameOverlapspectrum}
-        \todo{Add experimental data to TOF figure (CUP)}
-    \end{minipage}
-    \begin{minipage}{\columnwidth}
-        \includegraphics[width=\columnwidth]{SUPtofspectraRADECS.png}
-        \subcaption{At the SUP, with \SI{10.2}{\cm} collimator}
-        \label{fig:SUP10FrameOverlapspectrum}
-        \todo{Add experimental data to TOF figure (SUP)}
-    \end{minipage}
-    \caption{Simulated neutron time of flight spectra compared to measurements}
+    \caption{
+        Neutron time of flight spectra at the CUP-TOF position, with \SI{3}{\cm} collimator
+        }
     \label{fig:TOFSpectra}

### 2015-04-17 Paper2015.tex
Removed discussion of three components in the CUP TOF spectrum, for conciseness in the abstract.

@@
 
-Prokofiev et at.~\cite{Prokofiev14} explain the TOF spectrum upstream of the collimator as being the resultant of three components: directly from the target, scattered from the target surroundings, and backscattered from the collimator front face.
-The complex flight paths and energy losses in the scattered components break the one-to-one relationship between neutron energy and neutron time of flight from target to detector.
-We are able to reproduce this situation in our simulation, as shown by Fig.~\ref{fig:TOF3Componentslinear}, which shows good agreement with\ldots
-\todo{Complete description of the three components.}
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=\columnwidth]{TOF3Componentslinear.eps}
-	\caption{
-        Simulated neutron yield with \SI{3}{\cm} collimator at the CUP-TOF position.
-        The three components are directly from the target, scattered forward from the target surroundings, and scattered back from the collimator front wall.
-    }
-	\label{fig:TOF3Componentslinear}
-\end{figure}
-
 \subsection{Gamma fluence rate, spatial distribution and dose rate}

### 2015-04-17 Paper2015.tex
Made some figurs smaller, for conciseness
Removed comparison with MCNPX results, for conciseness in the abstract

@@
 \usepackage{subcaption}
-\captionsetup{margin={0pt,20pt}}
-\captionsetup[sub]{margin={0pt,20pt}}
 
@@
     \begin{minipage}{\columnwidth}
-        \includegraphics[width=\columnwidth]{SUPComparedIFluxRADECS.eps}
+        \centering
+        \includegraphics[width=0.9\columnwidth]{SUPComparedIFluxRADECS.eps}
         \subcaption{Integral fluence rate}
@@
     \begin{minipage}{\columnwidth}
-        \includegraphics[width=\columnwidth]{SUPNormalisedRADECS.eps}
+        \centering
+        \includegraphics[width=0.9\columnwidth]{SUPNormalisedRADECS.eps}
         \subcaption{Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}}
@@
 \todo{Explain what the results show: CUP measurement comparison.}
-Fig.~\ref{fig:MCComparison} provides a direct comparison between the two Monte Carlo calculations.
-The results show\ldots
-\todo{Explain what the results show (comparison between independent MC calculations).}
 
@@
     \begin{minipage}{\columnwidth}
-        \includegraphics[width=\columnwidth]{ANITAIntYieldRADECS.eps}
+        \centering
+        \includegraphics[width=0.9\columnwidth]{ANITAIntYieldRADECS.eps}
         \subcaption{Integral fluence rate}
-        \todo{Integral spectra on log-log axes: CUP}
     \end{minipage}
     \begin{minipage}{\columnwidth}
-        \includegraphics[width=\columnwidth]{ANITALetYieldnormalisedRADECS.eps}
+        \centering
+        \includegraphics[width=0.9\columnwidth]{ANITALetYieldnormalisedRADECS.eps}
     	\subcaption{Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}}
-        \todo{Normalised spectra on lethargy axes: CUP}
     \end{minipage}
@@
 	\label{fig:CUPSpectraComparison}
-\end{figure}
-
-\begin{figure}[t]
-    \includegraphics[width=\columnwidth]{TOFcomparedLetFluxRADECS.png}
-    \caption{
-        Calculated neutron spectra at the CUP-TOF position, compared to independent MCPX calculations~\cite{Prokofiev14}
-    }
-    \label{fig:MCComparison}
-    \todo{Show Comparison between Geant4 and MCNPX calculations}
 \end{figure}
@@
     \centering
-    \includegraphics[width=\columnwidth]{DiffYieldComparedSUPCUP10.eps}
+    \includegraphics[width=0.9\columnwidth]{DiffYieldComparedSUPCUP10.eps}
     \caption{
@@
     \centering
-    \includegraphics[width=\columnwidth]{gDYieldcomparedRADECS.eps}
+    \includegraphics[width=0.9\columnwidth]{gDYieldcomparedRADECS.eps}
     \caption{Calculated differential gamma spectra at CUP and SUP}
@@
     \begin{minipage}{\columnwidth}
-        \includegraphics[width=\columnwidth]{DoseVSenergySUP.eps}
+        \centering
+        \includegraphics[width=0.9\columnwidth]{DoseVSenergySUP.eps}
         \subcaption{SUP}
@@
     \begin{minipage}{\columnwidth}
-        \includegraphics[width=\columnwidth]{DoseVSenergyCUP.eps}
+        \centering
+        \includegraphics[width=0.9\columnwidth]{DoseVSenergyCUP.eps}
         \subcaption{CUP}

### 2015-04-17 Paper2015.tex
Minor editing

@@
 In Fig.~\ref{fig:SUPProfile} simulated data were folded in energy with the neutron fission cross section for \U238~\cite{tbd}, replicating measurement with a \U238\ TFBC~\cite{Prokofiev2009}.
-Within the beam umbra the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{0}{\neutron\per\cm\squared\per\second}, compared to \SI{0}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt13} and \SI{0}{\neutron\per\cm\squared\per\second} from the parameterisation~\cite{Prokofiev2009}.
-The parameterisation therefore exceeds the current calculations by tbd\%.
-\todo{Quantify integral yield}
+
 Within the beam umbra the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.1e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt13} and \SI{9.3e5}{\neutron\per\cm\squared\per\second} from the parameterisation~\cite{Prokofiev2009}.
-The parameterisation therefore exceeds the current calculations by tbd 31\%.\todo{Quantify integral yield}
+The parameterisation therefore exceeds the current calculations by 31\%.
 

### 2015-04-17 Paper2015.tex
Combined SUP and CUP results into the same figure and discussion.

@@
 The collimation effect is clearly visible.
-Fig.~\ref{fig:SUPProfile} shows neutron fluence profile at the SUP.
-In Fig.~\ref{fig:SUPProfile} simulated data were folded in energy with the neutron fission cross section for \U238~\cite{tbd}, replicating measurement with a \U238\ TFBC~\cite{Prokofiev2009}.
-
-Within the beam umbra the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.1e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt13} and \SI{9.3e5}{\neutron\per\cm\squared\per\second} from the parameterisation~\cite{Prokofiev2009}.
-The parameterisation therefore exceeds the current calculations by 31\%.
+Within the beam umbra the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.1e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt13} and \SI{9.3e5}{\neutron\per\cm\squared\per\second} from the standard facility parameterisation~\cite{Prokofiev2009}.
+The parameterisation therefore exceeds the present calculations by 31\%.
 
 \begin{figure}[t]
+    \begin{minipage}{\columnwidth}
         \includegraphics[width=\columnwidth]{SUP10ColSpatialDistribution10MeVRADECS.png}
-    \caption{
-        Spatial distribution of neutrons above \SI{10}{\MeV} at the SUP.
+        \subcaption{
+            Standard User Position.
             Concentric white circles indicate nominal umbra and penumbra limits.
@@
         \label{fig:SUPDensity}
+    \end{minipage}
+    \begin{minipage}{\columnwidth}
+        \includegraphics[width=\columnwidth]{CUP10ColSpatialDistribution10MeV.png}
+        \subcaption{Close User Position}
+        \label{fig:CUPDensity}
+    \end{minipage}
+    \caption{
+        Spatial distribution of neutrons above \SI{10}{\MeV} at SUP and CUP.
+        \SI{10.2}{\cm} diameter collimator.
+    }
+    \label{fig:SUPDensity}
 \end{figure}
+
+Fig.~\ref{fig:CUPDensity} shows equivalent data for the CUP.
+The results show\ldots
+\todo{Describe the results: contours and profile at CUP}
+In the central region the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{0}{\neutron\per\cm\squared\per\second}, compared to \SI{0}{\neutron\per\cm\squared\per\second} from the standard facility parameterisation~\cite{Prokofie14}.
+The parameterisation therefore exceeds the present calculations about TBD\%.
+\todo{Complete quantification at CUP}.
+
+Fig.~\ref{fig:SUPProfile} shows neutron fluence profile at the SUP.
+In Fig.~\ref{fig:SUPProfile} simulated data were folded in energy with the neutron fission cross section for \U238~\cite{tbd}, replicating measurement with a \U238\ TFBC~\cite{Prokofiev2009}.
 

### 2015-04-17 Paper2015.tex
Removed results for profile at SUP.

@@
     }
-    \label{fig:SUPDensity}
 \end{figure}
@@
 Fig.~\ref{fig:CUPDensity} shows equivalent data for the CUP.
+In the central region the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{0}{\neutron\per\cm\squared\per\second}, compared to \SI{0}{\neutron\per\cm\squared\per\second} from the standard facility parameterisation~\cite{Prokofiev14}.
+The parameterisation therefore exceeds the present calculations about TBD\%.
+\todo{Complete quantification at CUP}.
+The results show\ldots
+\todo{Describe the results: contours and profile at CUP and SUP}
+
+Fig.~\ref{fig:CUPProfile} shows neutron fluence profile at the CUP, compared with measurements.
+In Fig.~\ref{fig:CUPProfile} simulated data were folded in energy with the neutron fission cross section for \U238~\cite{tbd}, replicating the measurements which were made with a \U238\ TFBC~\cite{Prokofiev2009}.
 The results show\ldots
 \todo{Describe the results: contours and profile at CUP}
-In the central region the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{0}{\neutron\per\cm\squared\per\second}, compared to \SI{0}{\neutron\per\cm\squared\per\second} from the standard facility parameterisation~\cite{Prokofie14}.
-The parameterisation therefore exceeds the present calculations about TBD\%.
-\todo{Complete quantification at CUP}.
-
-Fig.~\ref{fig:SUPProfile} shows neutron fluence profile at the SUP.
-In Fig.~\ref{fig:SUPProfile} simulated data were folded in energy with the neutron fission cross section for \U238~\cite{tbd}, replicating measurement with a \U238\ TFBC~\cite{Prokofiev2009}.
 
 \begin{figure}[t]
-    \includegraphics[width=\columnwidth]{SUP10beamproFoldingRADECS.png}
-    \caption{
-        Neutron profile at the SUP, normalised to fluence rate on axis.
-        Vertical lines indicate nominal umbra and penumbra limits.
-    }
-    \label{fig:SUPProfile}
+    \centering
+    \includegraphics[width=\columnwidth]{CUPTOF10beamproRADECS.png}
+    \caption{Neutron profile at the CUP, normalised to fluence rate on axis.}
+    \label{fig:CUPProfile}
 \end{figure}
@@
 	\label{fig:SUPSpectraComparison}
-\end{figure}
-
-Fig.~\ref{fig:CUPDensity} and Fig.~\ref{fig:CUPProfile} show neutron spatial distribution (for neutrons above \SI{10}{\MeV}) and profile (folded in energy with the \U238\ fission cross-section) at the CUP.
-The results show\ldots
-\todo{Describe the results: contours and profile at CUP}
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=\columnwidth]{CUP10ColSpatialDistribution10MeV.png}
-    \caption{Spatial distribution of neutrons above \SI{10}{\MeV} at the CUP}
-    \label{fig:CUPDensity}
-    \todo{Show density of neutrons above \SI{10}{\MeV} at CUP}
-\end{figure}
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=\columnwidth]{CUPTOF10beamproRADECS.png}
-    \caption{Neutron profile at the CUP}
-    \label{fig:CUPProfile}
-    \todo{Show CUP profile, compared to measurements}
 \end{figure}

### 2015-04-17 Paper2015.tex
Introduced a combined figure for CUP and SUP spectra, and removed separate figures.

@@
 
-Fig.~\ref{fig:SUPSpectraComparison} compares calculated neutron yield versus energy in the umbra at the SUP with that predicted by the naked-target simulation~\cite{Platt13} and with the standard ANITA SUP parameterisation~\cite{Prokofiev2009}.
-The results show\ldots
-\todo{Discuss the results. Compare current with earlier calculations. Compare calculations with parameterisation.}
+Fig.~\ref{fig:Lethargyplots}
 
@@
         \centering
-        \includegraphics[width=0.9\columnwidth]{SUPComparedIFluxRADECS.eps}
-        \subcaption{Integral fluence rate}
+        \includegraphics[width=0.9\columnwidth]{SUPNormalisedRADECS.eps}
+        \subcaption{
+            SUP.
+            The comparison is against preliminary Geant4 modelling with a naked target model~\cite{Platt13} and against the standard facility parameterisation~\cite{Prokofiev2009}
+        }
     \end{minipage}
@@
         \centering
-        \includegraphics[width=0.9\columnwidth]{SUPNormalisedRADECS.eps}
-        \subcaption{Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}}
+        \includegraphics[width=0.9\columnwidth]{ANITALetYieldnormalisedRADECS.eps}
+        \subcaption{
+            CUP. 
+            The comparison is against the standard facility parameterisation~\cite{Prokofiev2009}
+        }
     \end{minipage}
 	\caption{
-        Neutron spectrum at the SUP, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from a naked Geant4 model~\cite{Platt13} and this work.
+        Calculated neutron spectra, normalised to fluence above \SI{10}{\MeV}
     }
-	\label{fig:SUPSpectraComparison}
+	\label{fig:Lethargyplots}
 \end{figure}
+
+Fig.~\ref{fig:SUPSpectraComparison} compares calculated neutron yield versus energy in the umbra at the SUP with that predicted by the naked-target simulation~\cite{Platt13} and with the standard ANITA SUP parameterisation~\cite{Prokofiev2009}.
+The results show\ldots
+\todo{Discuss the results. Compare current with earlier calculations. Compare calculations with parameterisation.}
 
@@
 \todo{Explain what the results show: CUP measurement comparison.}
-
-\begin{figure}[t]
-    \begin{minipage}{\columnwidth}
-        \centering
-        \includegraphics[width=0.9\columnwidth]{ANITAIntYieldRADECS.eps}
-        \subcaption{Integral fluence rate}
-    \end{minipage}
-    \begin{minipage}{\columnwidth}
-        \centering
-        \includegraphics[width=0.9\columnwidth]{ANITALetYieldnormalisedRADECS.eps}
-    	\subcaption{Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}}
-    \end{minipage}
-	\caption{
-        Neutron spectrum at the Close User Position, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from this work.
-    }
-	\label{fig:CUPSpectraComparison}
-\end{figure}
 

### 2015-04-17 Paper2015.tex
Modified text on neutron results

@@
 
-\subsection{Neutron fluence rate, spatial distribution and spectrum}
+\subsection{Neutrons}
 Fig.~\ref{fig:SUPDensity} shows neutron spatial distribution at the SUP, for neutrons above \SI{10}{\MeV}.
@@
 
-Fig.~\ref{fig:Lethargyplots}
+Fig.~\ref{fig:Lethargyplots} compares calculates spectra at SUP and CUP with their respective standard facility models~\cite{Prokofiev2009,Prokofiev14}.
+The SUP data are also compared with results from preliminary Geant4 simulations~\cite{Platt13}.
+The results show\ldots
+\todo{Describe the neutron spectra.}
 
@@
 
-Fig.~\ref{fig:SUPSpectraComparison} compares calculated neutron yield versus energy in the umbra at the SUP with that predicted by the naked-target simulation~\cite{Platt13} and with the standard ANITA SUP parameterisation~\cite{Prokofiev2009}.
-The results show\ldots
-\todo{Discuss the results. Compare current with earlier calculations. Compare calculations with parameterisation.}
-
-Fig.~\ref{fig:CUPSpectraComparison} compares the spectrum calculated at the CUP with that from the standard parameterisation~\cite{Prokofiev14}.
-The latter curve is derived from MCNPX calculations supported by TOF measurements with TFBCs.
-The results show\ldots
-\todo{Explain what the results show: CUP measurement comparison.}
-
 Fig.~\ref{fig:DifferentialSpectra} summarise neutron yield results by comparing differential flux as calculated in this work with facility parameterisations~\cite{Prokofiev2009,Prokofiev14}.
@@
 
-\subsection{Neutron time of flight}
-Neutron beam monitoring and characterisation at TSL uses time-of flight measurements with \U238\ TFBCs.
-Our Geant4 model permits these measurements to be simulated.
-Neutron time of flight data from the simulation (time measured from the time of arrival of primary photons at the target to the time of arrival of secondary neutrons at the point of interest) were folded in energy with the \U238\ fission cross-section, convolved with a \SI{5}{\ns} rectangle function approximating the primary proton micropulse shape, and overlapped at \SI{45}{\ns}, representing the timing ambiguity due to the micropulse period.
-Results are presented here for the CUP-TOF position and compared with measurements~\cite{Prokofiev14} in Fig.~\ref{fig:TOFSpectra}.
-The simulated CUP-TOF results were calculated for the \SI{3}{\cm} collimator, to match the available measured data.
+Neutron beam monitoring and characterisation at TSL includes time-of flight measurements with \U238\ TFBCs~\cite{Prokofiev14}.
+Fig.~\ref{fig:TOFSpectra} compares simulated and measured TOF spectra at the CUP-TOF position.
+The simulated CUP-TOF results were calculated for the \SI{3}{\cm} collimator, to match the measured data.
+Neutron time of flight data from the simulation were folded in energy with the \U238\ fission cross-section, convolved with a \SI{5}{\ns} rectangle function approximating the primary proton micropulse shape, and overlapped at \SI{45}{\ns}, representing the timing ambiguity due to the micropulse period.
 The results show\ldots
@@
 
-\subsection{Gamma fluence rate, spatial distribution and dose rate}
+\subsection{Photons}
 Fig.~\ref{fig:GammaSpatialDistribution} shows the calculated spatial distribution of gamma photons at SUP and CUP.

### 2015-04-17 Paper2015.tex
General editing.

@@
 
-Fig.~\ref{fig:CUPProfile} shows neutron fluence profile at the CUP, compared with measurements.
-In Fig.~\ref{fig:CUPProfile} simulated data were folded in energy with the neutron fission cross section for \U238~\cite{tbd}, replicating the measurements which were made with a \U238\ TFBC~\cite{Prokofiev2009}.
+Neutron beam monitoring and characterisation at TSL includes measurements with \U238\ TFBCs~\cite{Prokofiev14}.
+Fig.~\ref{fig:CUPProfile} shows neutron fluence profile at the CUP, compared with measurements~\cite{Prokofiev14}.
+In Fig.~\ref{fig:CUPProfile} simulated data were folded in energy with the neutron fission cross section for \U238~\cite{tbd}.
 The results show\ldots
@@
     \includegraphics[width=\columnwidth]{CUPTOF10beamproRADECS.png}
-    \caption{Neutron profile at the CUP, normalised to fluence rate on axis.}
+    \caption{
+        Neutron profile at the CUP, normalised to fluence rate on axis.
+        \SI{10.2}{\cm} collimator}
     \label{fig:CUPProfile}
+\end{figure}
+
+Fig.~\ref{fig:TOFSpectra} compares simulated and measured TOF spectra at the CUP-TOF position.
+Neutron time of flight data from the simulation were folded in energy with the \U238\ fission cross-section, convolved with a \SI{5}{\ns} rectangle function approximating the primary proton micropulse shape, and overlapped at \SI{45}{\ns}, representing the timing ambiguity due to the micropulse period.
+The results show\ldots
+\todo{Explain what the results show.}
+
+\begin{figure}[t]
+    \includegraphics[width=\columnwidth]{CUPTOFtofspectraRADECS.png}
+    \caption{
+        Neutron time of flight spectra at the CUP-TOF position, with \SI{3}{\cm} collimator
+        }
+    \label{fig:TOFSpectra}
 \end{figure}
@@
 	\caption{
-        Calculated neutron spectra, normalised to fluence above \SI{10}{\MeV}
+        Calculated neutron spectra, normalised to fluence above \SI{10}{\MeV}.
+        \SI{10.2}{\cm} collimator
     }
@@
     \caption{
-        Differential neutron spectra at CUP and SUP, comparing results of this work to facility parameterisations~\cite{Prokofiev2009,Prokofiev14}
+        Differential neutron spectra at CUP and SUP (\SI{10.2}{\cm} collimator), comparing results of this work to facility parameterisations~\cite{Prokofiev2009,Prokofiev14}
     }
     \label{fig:DifferentialSpectra}
-\end{figure}
-
-Neutron beam monitoring and characterisation at TSL includes time-of flight measurements with \U238\ TFBCs~\cite{Prokofiev14}.
-Fig.~\ref{fig:TOFSpectra} compares simulated and measured TOF spectra at the CUP-TOF position.
-The simulated CUP-TOF results were calculated for the \SI{3}{\cm} collimator, to match the measured data.
-Neutron time of flight data from the simulation were folded in energy with the \U238\ fission cross-section, convolved with a \SI{5}{\ns} rectangle function approximating the primary proton micropulse shape, and overlapped at \SI{45}{\ns}, representing the timing ambiguity due to the micropulse period.
-The results show\ldots
-\todo{Explain what the results show.}
-
-\begin{figure}[t]
-    \includegraphics[width=\columnwidth]{CUPTOFtofspectraRADECS.png}
-    \caption{
-        Neutron time of flight spectra at the CUP-TOF position, with \SI{3}{\cm} collimator
-        }
-    \label{fig:TOFSpectra}
 \end{figure}
@@
         \includegraphics[width=\columnwidth]{SUP10ColSpatialDistributionAllG.png}
-        \subcaption{SUP}
+        \subcaption{Standard User Position}
         \label{fig:GammaSpatialDistributionSUP}
@@
         \includegraphics[width=\columnwidth]{CUP10ColSpatialDistributionAllG.png}
-        \subcaption{CUP}
+        \subcaption{Close User Position}
         \label{fig:GammaSpatialDistributionCUP}
     \end{minipage}
-    \caption{Gamma spatial distribution}
+    \caption{
+        Calculated gamma spatial distribution.
+        \SI{10.2}{\cm}collimator
+    }
     \todo{It would be better if gamma spatial distribution were expressed as dose, rather than number of photons. Not in time for the abstract submission, however!}
@@
     \includegraphics[width=0.9\columnwidth]{gDYieldcomparedRADECS.eps}
-    \caption{Calculated differential gamma spectra at CUP and SUP}
+    \caption{
+        Calculated gamma spectra at CUP and SUP.
+        \SI{10.2}{\cm} collimator
+    }
     \label{fig:DifferentialGammaSpectra}
@@
         \includegraphics[width=0.9\columnwidth]{DoseVSenergySUP.eps}
-        \subcaption{SUP}
+        \subcaption{Standard User Position}
         \label{fig:GammaDoseEnergySUP}
-        \todo{Add gamma dose versus energy at SUP, \SI{10.2}{\cm} collimator}
     \end{minipage}
@@
         \includegraphics[width=0.9\columnwidth]{DoseVSenergyCUP.eps}
-        \subcaption{CUP}
+        \subcaption{Close User Position}
         \label{fig:GammaDoseEnergyCUP}
-        \todo{Add gamma dose versus energy at CUP, \SI{10.2}{\cm} collimator}
     \end{minipage}
-    \caption{Gamma dose spectra}
+    \caption{
+        Calculated gamma dose spectra.
+        \SI{10.2}{\cm} collimator
+    }
     \label{fig:GammaDoseEnergy}

### 2015-04-17 Paper2015.tex
Changed title to that upon which we agreed in January.
General editing

@@
 \title{
-    Monte Carlo calculation to characterize neutron and gamma fields for ANITA neutron facility at TSL
+    Detailed Geant4 simulations of the ANITA and ANITA-CUP neutron facilities
 }
@@
 
-\maketitle % Insert title
-\todo{Check title, affiliations etc.}
+\maketitle
 
@@
 The collimation effect is clearly visible.
-Within the beam umbra the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.1e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt13} and \SI{9.3e5}{\neutron\per\cm\squared\per\second} from the standard facility parameterisation~\cite{Prokofiev2009}.
-The parameterisation therefore exceeds the present calculations by 31\%.
+Within the beam umbra the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.1e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt13} and \SI{9.3e5}{\neutron\per\cm\squared\per\second} from an analytical model~\cite{Prokofiev2009}.
+The analytical model therefore exceeds the present calculations by 31\%.
 
@@
 Fig.~\ref{fig:CUPDensity} shows equivalent data for the CUP.
-In the central region the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{0}{\neutron\per\cm\squared\per\second}, compared to \SI{0}{\neutron\per\cm\squared\per\second} from the standard facility parameterisation~\cite{Prokofiev14}.
-The parameterisation therefore exceeds the present calculations about TBD\%.
+In the central region the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{0}{\neutron\per\cm\squared\per\second}, compared to \SI{0}{\neutron\per\cm\squared\per\second} from an analytical model~\cite{Prokofiev14}.
+The analytical model therefore exceeds the present calculations about TBD\%.
 \todo{Complete quantification at CUP}.
@@
 
-Neutron beam monitoring and characterisation at TSL includes measurements with \U238\ TFBCs~\cite{Prokofiev14}.
-Fig.~\ref{fig:CUPProfile} shows neutron fluence profile at the CUP, compared with measurements~\cite{Prokofiev14}.
+Fig.~\ref{fig:CUPProfile} shows neutron fluence profile at the CUP, compared with measurements made with \U238\ TFBCs~\cite{Prokofiev14}.
 In Fig.~\ref{fig:CUPProfile} simulated data were folded in energy with the neutron fission cross section for \U238~\cite{tbd}.
@@
         Neutron profile at the CUP, normalised to fluence rate on axis.
-        \SI{10.2}{\cm} collimator}
+        \SI{10.2}{\cm} diameter collimator}
     \label{fig:CUPProfile}
@@
     \caption{
-        Neutron time of flight spectra at the CUP-TOF position, with \SI{3}{\cm} collimator
+        Neutron time of flight spectra at the CUP-TOF position, with \SI{3}{\cm} diameter collimator
         }
@@
 
-Fig.~\ref{fig:Lethargyplots} compares calculates spectra at SUP and CUP with their respective standard facility models~\cite{Prokofiev2009,Prokofiev14}.
+Fig.~\ref{fig:Lethargyplots} compares calculated spectra at SUP and CUP with their respective analytical models~\cite{Prokofiev2009,Prokofiev14}.
 The SUP data are also compared with results from preliminary Geant4 simulations~\cite{Platt13}.
@@
             SUP.
-            The comparison is against preliminary Geant4 modelling with a naked target model~\cite{Platt13} and against the standard facility parameterisation~\cite{Prokofiev2009}
+            The comparison is against preliminary Geant4 modelling with a naked target model~\cite{Platt13} and against an analytical model~\cite{Prokofiev2009}
         }
@@
             CUP.
-            The comparison is against the standard facility parameterisation~\cite{Prokofiev2009}
+            The comparison is against the a standard analytical model~\cite{Prokofiev2009}
         }
@@
         Calculated neutron spectra, normalised to fluence above \SI{10}{\MeV}.
-        \SI{10.2}{\cm} collimator
+        \SI{10.2}{\cm} diameter collimator
     }
@@
 
-Fig.~\ref{fig:DifferentialSpectra} summarise neutron yield results by comparing differential flux as calculated in this work with facility parameterisations~\cite{Prokofiev2009,Prokofiev14}.
-The SUP calculations and parameterisations agree very closely below \SI{20}{\MeV}; the parameterisation exceeds the calculations somewhat above that energy.
-At CUP the parameterisation exceeds the Geant4 calculations by about TBD\% below \SI{20}{\MeV} and slightly more above that energy.
+Fig.~\ref{fig:DifferentialSpectra} summarises neutron spectra results by comparing differential flux as calculated in this work with analytical models~\cite{Prokofiev2009,Prokofiev14}.
+The SUP calculations and analytical models agree very closely below \SI{20}{\MeV}; the analytical model exceeds the calculations somewhat above that energy.
+At CUP the analytical model exceeds the Geant4 calculations by about TBD\% below \SI{20}{\MeV} and slightly more above that energy.
 \todo{Improve precision of the summary description of differential spectra.}
@@
     \caption{
-        Differential neutron spectra at CUP and SUP (\SI{10.2}{\cm} collimator), comparing results of this work to facility parameterisations~\cite{Prokofiev2009,Prokofiev14}
+        Differential neutron spectra at CUP and SUP (\SI{10.2}{\cm} diameter collimator), comparing results of this work to analytical models~\cite{Prokofiev2009,Prokofiev14}
     }
@@
         Calculated gamma spatial distribution.
-        \SI{10.2}{\cm}collimator
+        \SI{10.2}{\cm} diameter collimator
     }
@@
         Calculated gamma spectra at CUP and SUP.
-        \SI{10.2}{\cm} collimator
+        \SI{10.2}{\cm} diameter collimator
     }
@@
         Calculated gamma dose spectra.
-        \SI{10.2}{\cm} collimator
+        \SI{10.2}{\cm} diameter collimator
     }

### 2015-04-17 Paper2015.tex
Edited bibliography and citations.

@@
 \todo{Review introduction}
-\IEEEPARstart{M}{onte} Carlo simulations of naked spallation neutron sources at Los Alamos Neutron Science Center (LANSCE) Weapons Neutron Research (WNR) Target 4\cite{Wender87} and the ANITA beam at the University of Uppsala The Svedberg Laboratory (TSL) have been completed using Geant4 and proved that Binary intranuclear cascade (INC) model gave a good representation of neutron spectra than Bertini INC model did\cite{Platt13}.
+\IEEEPARstart{M}{onte} Carlo simulations of naked spallation neutron sources at Los Alamos Neutron Science Center (LANSCE) Weapons Neutron Research (WNR) Target 4\cite{Wender87} and the ANITA beam at the University of Uppsala The Svedberg Laboratory (TSL) have been completed using Geant4 and proved that Binary intranuclear cascade (INC) model gave a good representation of neutron spectra than Bertini INC model did\cite{Platt2013}.
 Simulation result of neutron spectra using Geant4 with Binary INC model is below measurement data from ANITA neutron facility.
@@
 \section{Modelling}
-Simulations were conducted using Geant4 version 10.0 and the binary intranuclear cascade model, as recommended in~\cite{Platt13}.
+Simulations were conducted using Geant4 version 10.0 and the binary intranuclear cascade model, as recommended in~\cite{Platt2013}.
 A detailed model of the ANITA geometry was implemented in Geant4, as illustrated in Fig.~\ref{fig:ANITAoverview}
-Description of the geometry is given in \cite{Prokofiev2009,Prokofiev14}.
+Description of the geometry is given in \cite{Prokofiev2009,Prokofiev2014}.
 %; a summary only is given here.
@@
 \section{Results}
-In previous work Platt et al.~\cite{Platt13} reported simulations of a naked ANITA target, demonstrating good qualitative agreement with independent calculations and measurements of the fast neutron field at ANITA SUP~\cite{Prokofiev2009}.
+In previous work Platt et al.~\cite{Platt2013} reported simulations of a naked ANITA target, demonstrating good qualitative agreement with independent calculations and measurements of the fast neutron field at ANITA SUP~\cite{Prokofiev2009}.
 Part of the motivation for this work was to investigate whether improvements in the fidelity of the geometry used in the Geant4 model would lead to increased quantitative agreement.
@@
 The collimation effect is clearly visible.
-Within the beam umbra the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.1e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt13} and \SI{9.3e5}{\neutron\per\cm\squared\per\second} from an analytical model~\cite{Prokofiev2009}.
+Within the beam umbra the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.1e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt2013} and \SI{9.3e5}{\neutron\per\cm\squared\per\second} from an analytical model~\cite{Prokofiev2009}.
 The analytical model therefore exceeds the present calculations by 31\%.
@@
 Fig.~\ref{fig:CUPDensity} shows equivalent data for the CUP.
-In the central region the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{0}{\neutron\per\cm\squared\per\second}, compared to \SI{0}{\neutron\per\cm\squared\per\second} from an analytical model~\cite{Prokofiev14}.
+In the central region the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{0}{\neutron\per\cm\squared\per\second}, compared to \SI{0}{\neutron\per\cm\squared\per\second} from an analytical model~\cite{Prokofiev2014}.
 The analytical model therefore exceeds the present calculations about TBD\%.
@@
 
-Fig.~\ref{fig:CUPProfile} shows neutron fluence profile at the CUP, compared with measurements made with \U238\ TFBCs~\cite{Prokofiev14}.
+Fig.~\ref{fig:CUPProfile} shows neutron fluence profile at the CUP, compared with measurements made with \U238\ TFBCs~\cite{Prokofiev2014}.
 In Fig.~\ref{fig:CUPProfile} simulated data were folded in energy with the neutron fission cross section for \U238~\cite{tbd}.
@@
 
-Fig.~\ref{fig:Lethargyplots} compares calculated spectra at SUP and CUP with their respective analytical models~\cite{Prokofiev2009,Prokofiev14}.
-The SUP data are also compared with results from preliminary Geant4 simulations~\cite{Platt13}.
+Fig.~\ref{fig:Lethargyplots} compares calculated spectra at SUP and CUP with their respective analytical models~\cite{Prokofiev2009,Prokofiev2014}.
+The SUP data are also compared with results from preliminary Geant4 simulations~\cite{Platt2013}.
 The results show\ldots
@@
             SUP.
-            The comparison is against preliminary Geant4 modelling with a naked target model~\cite{Platt13} and against an analytical model~\cite{Prokofiev2009}
+            The comparison is against preliminary Geant4 modelling with a naked target model~\cite{Platt2013} and against an analytical model~\cite{Prokofiev2009}
         }
@@
 
-Fig.~\ref{fig:DifferentialSpectra} summarises neutron spectra results by comparing differential flux as calculated in this work with analytical models~\cite{Prokofiev2009,Prokofiev14}.
+Fig.~\ref{fig:DifferentialSpectra} summarises neutron spectra results by comparing differential flux as calculated in this work with analytical models~\cite{Prokofiev2009,Prokofiev2014}.
 The SUP calculations and analytical models agree very closely below \SI{20}{\MeV}; the analytical model exceeds the calculations somewhat above that energy.
@@
     \caption{
-        Differential neutron spectra at CUP and SUP (\SI{10.2}{\cm} diameter collimator), comparing results of this work to analytical models~\cite{Prokofiev2009,Prokofiev14}
+        Differential neutron spectra at CUP and SUP (\SI{10.2}{\cm} diameter collimator), comparing results of this work to analytical models~\cite{Prokofiev2009,Prokofiev2014}
     }
@@
 
-\bibitem{Wender87}
-S.A. Wender and P.W. Lisowski,
-\newblock A white neutron source from 1 to 400 MeV,										% title	
-\newblock {\em Nucl. Instr. Meth. Phys. Res. B}, vol. 24-25, pp. 897-900.					% vol:page, 2011
+\bibitem{Prokofiev2009}
+Prokofiev, A. V. et al., 
+\newblock CUP-A New High-Flux Irradiation Position at the ANITA Neutron Facility at TSL,		\newblock {\em Proc. IEEE Trans. Nucl. Sci. 2014}, pp 1929-1936
 
-\bibitem{Platt13}
-Platt, S.P. and Hong, Q. and Mein, S.J. and Zhang, L.H.,
-\newblock Neutron and gamma fields at neutron spallation sources for single-event-effects testing,		% title	
-\newblock {\em in Proc. 14th European Conf. Radiat. Effects Compon. Syst. 2013,} pp 1-4			% vol:page, 2011
+\bibitem{Prokofiev2014}
+Prokofiev, A. V. et al.,
+\newblock Characterization of the ANITA Neutron Source for Accelerated SEE Testing at the Svedberg Laboratory,
+\newblock {\em in Proc. IEEE Radiat. Effects Data Work. 2009,} pp 166-173
 
-\bibitem{Prokofiev14}
-Prokofiev, A.V. and Blomgren, J. and Majerle, M. and Nolte, R. and Rottger, S. and Platt, S.P. and Cai Xiao Xiao and Smirnov, A.N.,
-\newblock Characterization of the ANITA Neutron Source for Accelerated SEE Testing at the Svedberg Laboratory,		% title	
-\newblock {\em in Proc. IEEE Radiation Effects Data Workshop. 2009,} pp 166-173 									% vol:page, 2011
+\bibitem{Platt2013}
+Platt, S. P. et al.,
+\newblock Neutron and gamma fields at neutron spallation sources for single-event-effects testing,
+\newblock {\em in Proc. 14th Euro. Conf. Radiat. Effects Compon. Syst. 2013}
 
-\bibitem{Prokofiev2009}
-Prokofiev, A.V. and Passoth, E. and Hjalmarsson, A. and Majerle, M.,
-\newblock CUP-A New High-Flux Irradiation Position at the ANITA Neutron Facility at TSL,		% title	
-\newblock {\em in Proc. IEEE Trans. Nucl. Sci. 2014}, pp 1929-1936 							% vol:page, 2011
+\bibitem{tbd0} \todo{Add referencefor Geant4}
 
-\bibitem{ANITAdrawing}
-Prokofiev, A.V.
-\newblock personal communication
-\newblock {\em TSL, Sep. 2013}
+\bibitem{tbd1} \todo{Complete reference for \U238}
+
+\bibitem{tbd2} \todo{Complete reference for dose conversion}
 

### 2015-04-17 Paper2015.tex
working process

@@
 Fig.~\ref{fig:CUPDensity} shows equivalent data for the CUP.
-In the central region the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{0}{\neutron\per\cm\squared\per\second}, compared to \SI{0}{\neutron\per\cm\squared\per\second} from an analytical model~\cite{Prokofiev2014}.
-The analytical model therefore exceeds the present calculations about TBD\%.
+In the central region the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.85e6}{\neutron\per\cm\squared\per\second}, compared to \SI{1.17e7}{\neutron\per\cm\squared\per\second} from an analytical model~\cite{Prokofiev2014}.
+The analytical model therefore exceeds the present calculations about 49\%.
 \todo{Complete quantification at CUP}.
@@
 
-\bibitem{tbd0} \todo{Add referencefor Geant4}
+\bibitem{Truscott2006} 
+Truscott, P. et al.,
+\newblock Neutron Energy-Deposition Spectra Measurements, and Comparisons with Geant4 Predictions
+\newblock{\em Proc. IEEE Trans. Nucl. Sci. 2006} pp 1883-1889
 
-\bibitem{tbd1} \todo{Complete reference for \U238}
+\bibitem{Carlson2009}
+Carlson, A. D. et al.,
+\newblock International Evaluation of Neutron Cross Section Standards
+\newblock{\em Proc. Nucl. Data Sheets 2009} pp 3215-3324
 
-\bibitem{tbd2} \todo{Complete reference for dose conversion}
+\bibitem{Kwon1980} 
+Kwon, S.-G. et al.,
+\newblock Calculation of Neutron and Gamma-Ray Flux-to-Dose-Rate Conversion Factors
+\newblock{\em Proc. J. Kor. Nucl. Soc. 1980}, pp171-179
 

### 2015-04-17 Paper2015.tex
Some editing work in progress.

@@
 Simulated protons were incident axially at an energy of \SI{180}{\MeV}.
-Resulting gamma and neutron fields were evaluated at several detector locations.
-In this paper results are presented for three of these: the Standard User Position (SUP), \SI{2.5}{\m} downstream of the target~\cite{Prokofiev2009}, the Close User Position (CUP), \SI{0.75}{\m} downstream of the target, and the CUP-TOF, \SI{0.84}{m} downstream of the target.
+Resulting neutron and gamma fields were evaluated at several detector locations.
+In this paper results are presented for three of these: the Standard User Position (SUP), \SI{2.5}{\m} downstream of the target, the Close User Position (CUP), \SI{0.75}{\m} downstream of the target, and the CUP-TOF, \SI{0.84}{m} downstream of the target.
 %N.B. This is downstream of the downstream edge of the target in Qian's model.
-The SUP and CUP positions are of interest as they are positions used for SEE tests; the CUP-TOF position is the location of thin-film breakdown counter (TFBC) detectors used for beam monitoring and characterisation using time-of-flight (TOF) techniques.
-Model validation will be demonstrated against CUP-TOF data (section~\ref{tbd}).
+The SUP and CUP positions are of interest as they are positions used for SEE tests; the CUP-TOF position is the location of thin-film breakdown counter (TFBC) detectors used for beam monitoring and characterisation.
+TFBC data are used to validate simulation results.
 
@@
 	\caption{
-        Simulated ANITA facility overview seen from above (yellow: bending magnet; red: shielding components; blue: target cooling jacket (enclosing the target); grey: collimator; blue: detector system)
+        Simulated ANITA facility overview seen from above (yellow: bending magnet; red: shielding components; blue: target assembly; grey: collimator; blue: detector system)
     }
@@
 Fig.~\ref{fig:SUPDensity} shows neutron spatial distribution at the SUP, for neutrons above \SI{10}{\MeV}.
-The collimation effect is clearly visible.
-Within the beam umbra the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.1e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt2013} and \SI{9.3e5}{\neutron\per\cm\squared\per\second} from an analytical model~\cite{Prokofiev2009}.
-The analytical model therefore exceeds the present calculations by 31\%.
+The SUP is downstream of the collimator, whose effect is clearly visible.
+Within the beam umbra the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.1e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt2013} and \SI{9.3e5}{\neutron\per\cm\squared\per\second} from an analytical model reported by Prokofiev et al.~\cite{Prokofiev2009}.
+The analytical model therefore exceeds the present calculations by about 30\%.
 
@@
     \caption{
-        Spatial distribution of neutrons above \SI{10}{\MeV} at SUP and CUP.
-        \SI{10.2}{\cm} diameter collimator.
+        Spatial distribution of neutrons above \SI{10}{\MeV} at SUP and CUP, with \SI{10.2}{\cm} diameter collimator
     }
@@
 
-Fig.~\ref{fig:CUPDensity} shows equivalent data for the CUP.
-In the central region the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.85e6}{\neutron\per\cm\squared\per\second}, compared to \SI{1.17e7}{\neutron\per\cm\squared\per\second} from an analytical model~\cite{Prokofiev2014}.
-The analytical model therefore exceeds the present calculations about 49\%.
-\todo{Complete quantification at CUP}.
+Fig.~\ref{fig:CUPDensity} shows equivalent data for the CUP, which is upstream of the collimator.
+In the central region the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.85e6}{\neutron\per\cm\squared\per\second}, compared to \SI{1.17e7}{\neutron\per\cm\squared\per\second} from an analytical model reported by Prokofiev et al.~\cite{Prokofiev2014}.
+The analytical model therefore exceeds the present calculations about 50\%.
 The results show\ldots
-\todo{Describe the results: contours and profile at CUP and SUP}
+\todo{Describe the results: contours at CUP and SUP}
 
-Fig.~\ref{fig:CUPProfile} shows neutron fluence profile at the CUP, compared with measurements made with \U238\ TFBCs~\cite{Prokofiev2014}.
-In Fig.~\ref{fig:CUPProfile} simulated data were folded in energy with the neutron fission cross section for \U238~\cite{tbd}.
+Fig.~\ref{fig:CUPProfile} shows neutron fluence profile at the CUP, compared with measurements made with \U238\ TFBCs.
+Results of calculations were folded in energy with the neutron fission cross section for \U238~\cite{Carlson2009}.
 The results show\ldots
-\todo{Describe the results: contours and profile at CUP}
+\todo{Describe the results: profile at CUP}
 
@@
     \caption{
-        Neutron profile at the CUP, normalised to fluence rate on axis.
+        Neutron profile at the CUP, normalised to fluence rate on axis, with
         \SI{10.2}{\cm} diameter collimator}
@@
 
-Fig.~\ref{fig:Lethargyplots} compares calculated spectra at SUP and CUP with their respective analytical models~\cite{Prokofiev2009,Prokofiev2014}.
+Fig.~\ref{fig:Lethargyplots} compares calculated spectra at SUP and CUP with their respective analytical models.
 The SUP data are also compared with results from preliminary Geant4 simulations~\cite{Platt2013}.
@@
             SUP.
-            The comparison is against preliminary Geant4 modelling with a naked target model~\cite{Platt2013} and against an analytical model~\cite{Prokofiev2009}
-        }
+            The comparison is against the fit of Prokofiev et al.~\cite{Prokofiev2009} and preliminary Geant4 modelling by Platt et al.~\cite{Platt2013} }
     \end{minipage}
@@
             CUP.
-            The comparison is against the a standard analytical model~\cite{Prokofiev2009}
+            The comparison is against the fit of Prokofiev et al.~\cite{Prokofiev2009}
         }
@@
 	\caption{
-        Calculated neutron spectra, normalised to fluence above \SI{10}{\MeV}.
+        Calculated neutron spectra, normalised to fluence above \SI{10}{\MeV}, with
         \SI{10.2}{\cm} diameter collimator
@@
 
-Fig.~\ref{fig:DifferentialSpectra} summarises neutron spectra results by comparing differential flux as calculated in this work with analytical models~\cite{Prokofiev2009,Prokofiev2014}.
+Fig.~\ref{fig:DifferentialSpectra} summarises neutron spectra results by comparing differential flux as calculated in this work with fits of  models~\cite{Prokofiev2009,Prokofiev2014}.
 The SUP calculations and analytical models agree very closely below \SI{20}{\MeV}; the analytical model exceeds the calculations somewhat above that energy.
@@
     \caption{
-        Calculated gamma spatial distribution.
+        Calculated gamma spatial distribution, with
         \SI{10.2}{\cm} diameter collimator
@@
     \caption{
-        Calculated gamma spectra at CUP and SUP.
+        Calculated gamma spectra at CUP and SUP, with
         \SI{10.2}{\cm} diameter collimator
@@
     \caption{
-        Calculated gamma dose spectra.
+        Calculated gamma dose spectra, with
         \SI{10.2}{\cm} diameter collimator
@@
 \newblock Neutron Energy-Deposition Spectra Measurements, and Comparisons with Geant4 Predictions
-\newblock{\em Proc. IEEE Trans. Nucl. Sci. 2006} pp 1883-1889
+\newblock{\em Proc. IEEE Trans. Nucl. Sci. 2006} pp. 1883-1889
 
@@
 \newblock International Evaluation of Neutron Cross Section Standards
-\newblock{\em Proc. Nucl. Data Sheets 2009} pp 3215-3324
+\newblock{\em Proc. Nucl. Data Sheets 2009} pp. 3215-3324
 
@@
 \newblock Calculation of Neutron and Gamma-Ray Flux-to-Dose-Rate Conversion Factors
-\newblock{\em Proc. J. Kor. Nucl. Soc. 1980}, pp171-179
+\newblock{\em Proc. J. Kor. Nucl. Soc. 1980}, pp. 171-179
 

### 2015-04-17 Paper2015.tex
Changed figure for CUP spectrum (the wrong figure was used before).
Version sent to Alexander on Friday evening.
Introductory text and references updated.

@@
 \section{Introduction}
-\todo{Review introduction}
-\IEEEPARstart{M}{onte} Carlo simulations of naked spallation neutron sources at Los Alamos Neutron Science Center (LANSCE) Weapons Neutron Research (WNR) Target 4\cite{Wender87} and the ANITA beam at the University of Uppsala The Svedberg Laboratory (TSL) have been completed using Geant4 and proved that Binary intranuclear cascade (INC) model gave a good representation of neutron spectra than Bertini INC model did\cite{Platt2013}.
-Simulation result of neutron spectra using Geant4 with Binary INC model is below measurement data from ANITA neutron facility.
-It is likely to be influenced by our omission of collimator, shielding, and bending magnet component.
-This work is to verify this hypothesis is correct.
-In addition, we are intested in the gamma field at CUP and SUP in spallation neutron source at the ANITA neutron facility at TSL for SEE testing.
+
+The ANITA facility at The Svedberg Laboratory has been widely used for accelerated testing for neutron single-event effects (SEE)~\cite{Prokofiev2009}.
+A high-flux facility, ANITA-CUP, has recently been introduced and reported by Prokofiev et al.~\cite{Prokofiev2014}.
+
+Platt et al. have reported preliminary Monte Carlo models of neutron and gamma production at ANITA~\cite{Platt2013}.
+That work was motivated by a desire to understand the possibility of gamma sensitivity in detectors used for beam monitoring during SEE tests.
+Simulations of a bare spallation target showed demonstrating good qualitative agreement with independent calculations and measurements of the fast neutron field at the standard ANITA facility.
+The current work was motivation partly by a desire to investigate whether improvements in the fidelity of the geometry used in the simulations model would lead to increased quantitative agreement with independent data, and partly to extend the work to encompass the new facility at ANITA-CUP.
+
+Accordingly, in this paper we will present a comprehensive set of analyses of neutron and gamma fields at ANITA and ANITA-CUP, with comparison against independent models and validation against measurements.
+We present a subset of those results in this extended abstract.
 
 \section{Modelling}
-Simulations were conducted using Geant4 version 10.0 and the binary intranuclear cascade model, as recommended in~\cite{Platt2013}.
-A detailed model of the ANITA geometry was implemented in Geant4, as illustrated in Fig.~\ref{fig:ANITAoverview}
-Description of the geometry is given in \cite{Prokofiev2009,Prokofiev2014}.
+Simulations were conducted using Geant4 version 10.0~\cite{Agostinelli2003,Allison2006} with the binary intranuclear cascade model~\cite{Platt2013}.
+A detailed model of the ANITA geometry~\cite{Prokofiev2009,Prokofiev2014} was implemented in Geant4, as illustrated in Fig.~\ref{fig:ANITAoverview}.
 %; a summary only is given here.
@@
 %An iron collimator with variable apertures is modelled  and shown downstream of the target (grey).
-Except where indicated otherwise, all results in this summary are for the standard collimator size (\SI{10.2}{\cm} diameter).
-In the final paper we will present results for cylindrical collimators in the range from \SIrange{3}{30}{\cm} diameter.
 Simulated protons were incident axially at an energy of \SI{180}{\MeV}.
@@
 %N.B. This is downstream of the downstream edge of the target in Qian's model.
+The SUP position is downstream of a collimator with variable aperture; the CUP and CUP-TOF positions are upstream of the same collimator.
 The SUP and CUP positions are of interest as they are positions used for SEE tests; the CUP-TOF position is the location of thin-film breakdown counter (TFBC) detectors used for beam monitoring and characterisation.
@@
 \section{Results}
-In previous work Platt et al.~\cite{Platt2013} reported simulations of a naked ANITA target, demonstrating good qualitative agreement with independent calculations and measurements of the fast neutron field at ANITA SUP~\cite{Prokofiev2009}.
-Part of the motivation for this work was to investigate whether improvements in the fidelity of the geometry used in the Geant4 model would lead to increased quantitative agreement.
-\todo{Review first part of Results section -- move to introduction?}
 
@@
 Fig.~\ref{fig:SUPDensity} shows neutron spatial distribution at the SUP, for neutrons above \SI{10}{\MeV}.
-The SUP is downstream of the collimator, whose effect is clearly visible.
-Within the beam umbra the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.1e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt2013} and \SI{9.3e5}{\neutron\per\cm\squared\per\second} from an analytical model reported by Prokofiev et al.~\cite{Prokofiev2009}.
+Collimation is clearly visible.
+Within the beam umbra the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.1e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt2013} and \SI{9.3e5}{\neutron\per\cm\squared\per\second} from an established analytical model~\cite{Prokofiev2009}.
 The analytical model therefore exceeds the present calculations by about 30\%.
@@
         \centering
-        \includegraphics[width=0.9\columnwidth]{ANITALetYieldnormalisedRADECS.eps}
+        \includegraphics[width=0.9\columnwidth]{CUPcomparedProkofiev2014NormalisedRADECS.eps}
         \subcaption{
             CUP.
-            The comparison is against the fit of Prokofiev et al.~\cite{Prokofiev2009}
+            The comparison is against the fit of Prokofiev et al.~\cite{Prokofiev2014}
         }
@@
 
-Fig.~\ref{fig:DifferentialSpectra} summarises neutron spectra results by comparing differential flux as calculated in this work with fits of  models~\cite{Prokofiev2009,Prokofiev2014}.
-The SUP calculations and analytical models agree very closely below \SI{20}{\MeV}; the analytical model exceeds the calculations somewhat above that energy.
-At CUP the analytical model exceeds the Geant4 calculations by about TBD\% below \SI{20}{\MeV} and slightly more above that energy.
+Fig.~\ref{fig:DifferentialSpectra} summarises neutron spectra results by comparing differential flux as calculated in this work with the Prokofiev et al. models~\cite{Prokofiev2009,Prokofiev2014}.
+The SUP calculations and analytical model agree very closely below \SI{20}{\MeV}; the analytical model exceeds the calculations somewhat above that energy.
+At CUP the analytical model exceeds the Geant4 calculations by about 50\%, slightly more than that above \SI{20}{\MeV}.
 \todo{Improve precision of the summary description of differential spectra.}
@@
     }
-    \todo{It would be better if gamma spatial distribution were expressed as dose, rather than number of photons. Not in time for the abstract submission, however!}
     \label{fig:GammaSpatialDistribution}
@@
 
-Fig.~\ref{fig:GammaDoseEnergy} shows the calculated distribution of gamma dose, obtained by folding the gamma spectra (Fig~\ref{fig:GammaDoseEnergy}) with dose conversion data from \cite{tbd}.
+Fig.~\ref{fig:GammaDoseEnergy} shows the calculated distribution of gamma dose, obtained by folding the gamma spectra (Fig~\ref{fig:GammaDoseEnergy}) with dose conversion data from \cite{Kwon1980}.
 The results show\ldots
@@
 
-\todo{Complete citations}
-
 \begin{thebibliography}{99} % Bibliography - this is intentionally simple in this template
@@
 Prokofiev, A. V. et al.,
-\newblock CUP-A New High-Flux Irradiation Position at the ANITA Neutron Facility at TSL,		\newblock {\em Proc. IEEE Trans. Nucl. Sci. 2014}, pp 1929-1936
+\newblock ``Characterization of the ANITA neutron source for accelerated SEE testing at The Svedberg Laboratory'',
+\newblock {\em 2009 IEEE Radiat. Effects Data Workshop Record}, pp.~166-173
 
@@
 Prokofiev, A. V. et al.,
-\newblock Characterization of the ANITA Neutron Source for Accelerated SEE Testing at the Svedberg Laboratory,
-\newblock {\em in Proc. IEEE Radiat. Effects Data Work. 2009,} pp 166-173
+\newblock ``CUP--A new high-flux irradiation position at the ANITA neutron facility at TSL'',		\newblock {\em IEEE Trans. Nucl. Sci.} vol.~61 no.~4, pp.~1929-1936, 2014
 
@@
 Platt, S. P. et al.,
-\newblock Neutron and gamma fields at neutron spallation sources for single-event-effects testing,
-\newblock {\em in Proc. 14th Euro. Conf. Radiat. Effects Compon. Syst. 2013}
+\newblock ``Neutron and gamma fields at neutron spallation sources for single-event-effects testing'',
+\newblock {\em Proc. 14th European Conf. Radiat. Effects Compon. Syst.}, 2013
 
-\bibitem{Truscott2006}
-Truscott, P. et al.,
-\newblock Neutron Energy-Deposition Spectra Measurements, and Comparisons with Geant4 Predictions
-\newblock{\em Proc. IEEE Trans. Nucl. Sci. 2006} pp. 1883-1889
+\bibitem{Agostinelli2003}
+Agostinelli, S. et al.,
+\newblock``Geant4--a simulation toolkit'',
+\newblock {\em Nucl. Unst. Meth. Phys. Res. A} vol.~506, pp.~250--303, 2003
+
+\bibitem{Allison2006}
+Allison, J. et al.,
+\newblock ``Geant4 developments and applications'',
+\newblock {\em IEEE Trans. Nucl. Sci.} vol.~53 no.~1, pp.~270--278, 2006
 
@@
 Carlson, A. D. et al.,
-\newblock International Evaluation of Neutron Cross Section Standards
-\newblock{\em Proc. Nucl. Data Sheets 2009} pp. 3215-3324
+\newblock ``International evaluation of neutron cross section standards'',
+\newblock{\em Nucl. Data Sheets} vol.~110 no.~12, pp.~3215-3324, 2009
 
@@
 Kwon, S.-G. et al.,
-\newblock Calculation of Neutron and Gamma-Ray Flux-to-Dose-Rate Conversion Factors
-\newblock{\em Proc. J. Kor. Nucl. Soc. 1980}, pp. 171-179
+\newblock ``Calculation of neutron and gamma-ray flux-to-dose-rate conversion factors'',
+\newblock{\em J. Kor. Nucl. Soc.} vol.~12 no.~3, pp.~171-179, 1980
 

### 2015-04-17 Paper2015.tex
Using class option peerreviewca and conference-style author details.
Corrected some typographical errors.

@@
 % Paper 2015
-\documentclass[11pt,a4paper]{IEEEtran}
+\documentclass[peerreviewca,11pt,a4paper]{IEEEtran}
 
@@
 
-\author{%
-    Q. Hong,
-    S. P. Platt,
-    A. V. Prokofiev,
-    E. Passoth
-    \thanks{%
-        Qian Hong and Simon Platt are with the University of Central Lancashire, England. Alexander Prokofiev and Elke Passoth are with the The Svedberg Laboratory, University of Uppsala, Sweden.
+\author{
+    \IEEEauthorblockN{
+        Q. Hong\IEEEauthorrefmark{1},
+        S. P. Platt\IEEEauthorrefmark{1},
+        A. V. Prokofiev\IEEEauthorrefmark{2} and
+        E. Passoth\IEEEauthorrefmark{2}
+    }
+    \IEEEauthorblockA{
+        \IEEEauthorrefmark{1}
+        University of Central Lancashire
+    }
+    \IEEEauthorblockA{
+        \IEEEauthorrefmark{2}
+        The Svedberg Laboratory, University of Uppsala
     }
@@
 
+\IEEEpeerreviewmaketitle
+
 \section{Introduction}
@@
 That work was motivated by a desire to understand the possibility of gamma sensitivity in detectors used for beam monitoring during SEE tests.
-Simulations of a bare spallation target showed demonstrating good qualitative agreement with independent calculations and measurements of the fast neutron field at the standard ANITA facility.
-The current work was motivation partly by a desire to investigate whether improvements in the fidelity of the geometry used in the simulations model would lead to increased quantitative agreement with independent data, and partly to extend the work to encompass the new facility at ANITA-CUP.
+Simulations of a bare spallation target showed qualitative agreement with independent calculations and measurements of the fast neutron field at the standard ANITA facility.
+The present work was motivated partly by a desire to investigate whether improvements in the fidelity of the geometry used in the simulations would lead to closer quantitative agreement with independent data, and partly to extend the work to encompass the new facility at ANITA-CUP.
 
@@
             Standard User Position.
-            Concentric white circles indicate nominal umbra and penumbra limits.
+            Concentric white circles indicate nominal umbra and penumbra limits
         }
@@
 \newblock``Geant4--a simulation toolkit'',
-\newblock {\em Nucl. Unst. Meth. Phys. Res. A} vol.~506, pp.~250--303, 2003
+\newblock {\em Nucl. Inst. Meth. Phys. Res. A} vol.~506, pp.~250--303, 2003
 

### 2015-04-20 Paper2015.tex
Prior to incorporating Alexander's comments.

@@
 \DeclareSIUnit\neutron{n}
+\DeclareSIUnit{\seivert}{Sv}
 
@@
 That work was motivated by a desire to understand the possibility of gamma sensitivity in detectors used for beam monitoring during SEE tests.
-Simulations of a bare spallation target showed qualitative agreement with independent calculations and measurements of the fast neutron field at the standard ANITA facility.
-The present work was motivated partly by a desire to investigate whether improvements in the fidelity of the geometry used in the simulations would lead to closer quantitative agreement with independent data, and partly to extend the work to encompass the new facility at ANITA-CUP.
+Simulations of a bare spallation target showed qualitative agreement with independent calculations and measurements of the fast neutron field at the standard ANITA facility~\cite{Prokofiev2009}.
+The present work was motivated partly by a desire to investigate whether improvements in the fidelity of the geometry used in the simulations would lead to closer quantitative agreement with independent data, and partly to extend the work to encompass the new facility at ANITA-CUP~\cite{Prokofiev2014}.
 
@@
 Resulting neutron and gamma fields were evaluated at several detector locations.
-In this paper results are presented for three of these: the Standard User Position (SUP), \SI{2.5}{\m} downstream of the target, the Close User Position (CUP), \SI{0.75}{\m} downstream of the target, and the CUP-TOF, \SI{0.84}{m} downstream of the target.
+In this paper results are presented for three of these: the Standard User Position (SUP), \SI{2.5}{\m} downstream of the target, the Close User Position (CUP), \SI{0.75}{\m} downstream of the target, and the CUP-TOF position, \SI{0.84}{m} downstream of the target.
 %N.B. This is downstream of the downstream edge of the target in Qian's model.
 The SUP position is downstream of a collimator with variable aperture; the CUP and CUP-TOF positions are upstream of the same collimator.
-The SUP and CUP positions are of interest as they are positions used for SEE tests; the CUP-TOF position is the location of thin-film breakdown counter (TFBC) detectors used for beam monitoring and characterisation.
+The SUP and CUP positions are of interest as they are positions used for SEE tests; the CUP-TOF position is the location of thin-film breakdown counter (TFBC) detectors used for beam monitoring and characterisation including neutron time of flight (TOF) measurements.
 TFBC data are used to validate simulation results.
@@
 Collimation is clearly visible.
-Within the beam umbra the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.1e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt2013} and \SI{9.3e5}{\neutron\per\cm\squared\per\second} from an established analytical model~\cite{Prokofiev2009}.
+Within the beam umbra the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.1e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt2013} and \SI{9.3e5}{\neutron\per\cm\squared\per\second} from well-established analytical model~\cite{Prokofiev2009}.
 The analytical model therefore exceeds the present calculations by about 30\%.
@@
     \begin{minipage}{\columnwidth}
-        \includegraphics[width=\columnwidth]{SUP10ColSpatialDistribution10MeVRADECS.png}
+        \includegraphics[width=0.9\columnwidth]{SUP10ColSpatialDistribution10MeVRADECS.png}
         \subcaption{
@@
     \begin{minipage}{\columnwidth}
-        \includegraphics[width=\columnwidth]{CUP10ColSpatialDistribution10MeV.png}
+        \includegraphics[width=0.9\columnwidth]{CUP10ColSpatialDistribution10MeV.png}
         \subcaption{Close User Position}
@@
 
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=0.9\columnwidth]{CUPTOF10beamproRADECS.png}
+    \caption{
+        Vertical neutron profile at the CUP, normalised to fluence rate on axis, with
+        \SI{10.2}{\cm} diameter collimator.
+    }
+    \label{fig:CUPProfile}
+\end{figure}
+
 Fig.~\ref{fig:CUPDensity} shows equivalent data for the CUP, which is upstream of the collimator.
@@
 The analytical model therefore exceeds the present calculations about 50\%.
-The results show\ldots
-\todo{Describe the results: contours at CUP and SUP}
 
-Fig.~\ref{fig:CUPProfile} shows neutron fluence profile at the CUP, compared with measurements made with \U238\ TFBCs.
+Fig.~\ref{fig:CUPProfile} shows the vertical neutron fluence profile at the CUP, compared with measurements made with \U238\ TFBCs.
 Results of calculations were folded in energy with the neutron fission cross section for \U238~\cite{Carlson2009}.
-The results show\ldots
-\todo{Describe the results: profile at CUP}
+The results show close agreement between measurement and simulation, although the sharp cut-off between about \SI{10}{\cm} and about \SI{15}{\cm} is not fully reproduced by the simulation.%
+\todo{
+    Improve presentation of results for CUP profile.
+    Make calculations at the same positions as those used for the measurements.
+}
+
+Fig.~\ref{fig:TOFSpectra} compares simulated and measured TOF spectra at the CUP-TOF position.
+Neutron time of flight data from the simulation were folded in energy with the \U238\ fission cross-section, convolved with a \SI{5}{\ns} rectangle function approximating the primary proton micropulse shape, and overlapped at \SI{45}{\ns}, representing the timing ambiguity due to the micropulse period.
+The results show very close agreement in the position and width of the TOF peak.
+Prokofiev et al.~\cite{Prokofiev2014} note that the TOF spectrum at the CUP comprises three parts, a component directly from the target, one scattered forward from target surroundings, and one scattered backwards from the front face of the collimator block.
+The present simulations confirm the Prokofiev et al. semi-empirical multicomponent model. Details of this confirmation will be presented in the full paper but are omitted here for brevity.
+In this summary we limit ourselves to the observation that direct reproduction of the deceptively complex TOF spectrum, as shown by Fig.~\ref{fig:TOFSpectra} reflects the fidelity of the present model spectrum and geometry.\todo{Improve phrasing here.}
 
@@
     \centering
-    \includegraphics[width=\columnwidth]{CUPTOF10beamproRADECS.png}
+    \includegraphics[width=0.9\columnwidth]{CUPTOFtofspectraRADECS.png}
     \caption{
-        Neutron profile at the CUP, normalised to fluence rate on axis, with
-        \SI{10.2}{\cm} diameter collimator}
-    \label{fig:CUPProfile}
-\end{figure}
-
-Fig.~\ref{fig:TOFSpectra} compares simulated and measured TOF spectra at the CUP-TOF position.
-Neutron time of flight data from the simulation were folded in energy with the \U238\ fission cross-section, convolved with a \SI{5}{\ns} rectangle function approximating the primary proton micropulse shape, and overlapped at \SI{45}{\ns}, representing the timing ambiguity due to the micropulse period.
-The results show\ldots
-\todo{Explain what the results show.}
-
-\begin{figure}[t]
-    \includegraphics[width=\columnwidth]{CUPTOFtofspectraRADECS.png}
-    \caption{
-        Neutron time of flight spectra at the CUP-TOF position, with \SI{3}{\cm} diameter collimator
+        Neutron time of flight spectra at the CUP-TOF position, with \SI{3}{\cm} diameter collimator.
         }
@@
 
-Fig.~\ref{fig:Lethargyplots} compares calculated spectra at SUP and CUP with their respective analytical models.
-The SUP data are also compared with results from preliminary Geant4 simulations~\cite{Platt2013}.
-The results show\ldots
-\todo{Describe the neutron spectra.}
-
 \begin{figure}[t]
@@
         \centering
-        \includegraphics[width=0.9\columnwidth]{SUPNormalisedRADECS.eps}
+        \includegraphics[width=0.8\columnwidth]{SUPNormalisedRADECS.eps}
         \subcaption{
             SUP.
-            The comparison is against the fit of Prokofiev et al.~\cite{Prokofiev2009} and preliminary Geant4 modelling by Platt et al.~\cite{Platt2013} }
+            The comparison is against the fit of Prokofiev et al.~\cite{Prokofiev2009} and preliminary Geant4 modelling by Platt et al.~\cite{Platt2013}
+        }
+        \label{fig:LethargyplotSUP}
     \end{minipage}
@@
         \centering
-        \includegraphics[width=0.9\columnwidth]{CUPcomparedProkofiev2014NormalisedRADECS.eps}
+        \includegraphics[width=0.8\columnwidth]{CUPcomparedProkofiev2014NormalisedRADECS.eps}
         \subcaption{
@@
         }
+        \label{fig:LethargyplotCUP}
     \end{minipage}
@@
 
-Fig.~\ref{fig:DifferentialSpectra} summarises neutron spectra results by comparing differential flux as calculated in this work with the Prokofiev et al. models~\cite{Prokofiev2009,Prokofiev2014}.
-The SUP calculations and analytical model agree very closely below \SI{20}{\MeV}; the analytical model exceeds the calculations somewhat above that energy.
-At CUP the analytical model exceeds the Geant4 calculations by about 50\%, slightly more than that above \SI{20}{\MeV}.
-\todo{Improve precision of the summary description of differential spectra.}
-
-\begin{figure}[t]
+\begin{figure}[!t]
     \centering
-    \includegraphics[width=0.9\columnwidth]{DiffYieldComparedSUPCUP10.eps}
+    \includegraphics[width=0.8\columnwidth]{DiffYieldComparedSUPCUP10.eps}
     \caption{
@@
 
+Fig.~\ref{fig:Lethargyplots} compares calculated spectra at SUP and CUP with their respective analytical models.
+The SUP data are also compared with results from preliminary Geant4 simulations~\cite{Platt2013}.
+These curves are normalised to neutron fluence above \SI{10}{\MeV} an presented as lethargy plots to emphasis the shape of the spectra rather than their integral fluence rate.
+The increased integral fluence rate at SUP from the present calculations, compared to the preliminary results of \cite{Platt2013} is therefore not visible in Fig.~\ref{fig:LethargyplotSUP}.
+Fig.~\ref{fig:LethargyplotSUP} does show an increased contribution below about \SI{1}{\MeV}, consistent with interactions in materials other than the target, which were absent from the preliminary simulations.
+Fig.~\ref{fig:LethargyplotCUP} shows extremely close agreement with the analytical model from~\cite{Prokofiev2014} (the analytical model smooths out the structure in the evaporation peak around \SI{1}{\MeV}).
+When compared to the analytical models the calculated spectra from the current work lead to slightly lower neutron yield and slightly higher peak energies in the higher energy peak near \SI{100}{\MeV}.
+It is not surprising that this is not affected by the improved model geometry as this peak arises from intranuclear cascades in the target.
+We continue to investigate this discrepancy and will discuss it further in our final paper.
+
+Fig.~\ref{fig:DifferentialSpectra} summarises neutron spectra results by comparing differential flux as calculated in this work with the Prokofiev et al. models~\cite{Prokofiev2009,Prokofiev2014}.
+The SUP calculations and analytical model agree very closely below \SI{20}{\MeV}; the analytical model exceeds the calculations somewhat above that energy.
+At CUP the analytical model exceeds the Geant4 calculations by about 50\%, slightly more than that above \SI{20}{\MeV}.
+
 \subsection{Photons}
-Fig.~\ref{fig:GammaSpatialDistribution} shows the calculated spatial distribution of gamma photons at SUP and CUP.
+Fig.~\ref{fig:GammaSpatialDistribution} shows the calculated spatial distribution of gamma photons at SUP and CUP, and shows a gamma radiation distribution that is qualitatively very similar to that for neutrons at both locations.
 Fig.~\ref{fig:DifferentialGammaSpectra} shows the calculated differential gamma spectra within the central region of the spatial distribution.
-The results show\ldots
-\todo{Describe the gamma results}
+There is a broad continuum up to an energy of about \SI{10}{\MeV}, with a peak in the fluence spectrum at about \SI{0.5}{\MeV} (where the annihilation peak is visible).
+The gamma fluence rate is an order of magnitude greater at CUP that at SUP, consistent with the closer range to the target and its immediate surroundings.
+The CUP spectrum also shows a backscatter peak around \SI{0.2}{\MeV}.
 
@@
     \begin{minipage}{\columnwidth}
-        \includegraphics[width=\columnwidth]{SUP10ColSpatialDistributionAllG.png}
+        \includegraphics[width=0.9\columnwidth]{SUP10ColSpatialDistributionAllG.png}
         \subcaption{Standard User Position}
@@
     \begin{minipage}{\columnwidth}
-        \includegraphics[width=\columnwidth]{CUP10ColSpatialDistributionAllG.png}
+        \includegraphics[width=0.9\columnwidth]{CUP10ColSpatialDistributionAllG.png}
         \subcaption{Close User Position}
@@
 
-Fig.~\ref{fig:GammaDoseEnergy} shows the calculated distribution of gamma dose, obtained by folding the gamma spectra (Fig~\ref{fig:GammaDoseEnergy}) with dose conversion data from \cite{Kwon1980}.
-The results show\ldots
-\todo{Describe the gamma dose versus energy graphs.}
-The calculated dose rate at \SI{200}{\nA} primary proton current is \SI{21}{\milli\gray\per\hour} at SUP and \SI{370}{\milli\gray\per\hour} at CUP.
-\todo{Discuss calculated dose rates}
-
 \begin{figure}[t]
@@
 \end{figure}
+
+Fig.~\ref{fig:GammaDoseEnergy} shows the calculated distribution of gamma dose, obtained by folding the gamma spectra (Fig~\ref{fig:GammaDoseEnergy}) with dose conversion data from \cite{Kwon1980}.
+The results show structure with peaks around \SI{1.5}{\MeV}, \SI{3}{\MeV}, \SI{6}{\MeV} and \SI{9}{\MeV}.
+Note that these are not coincidence peaks, as the simulation counts individual photons.
+The calculated dose rate at \SI{200}{\nA} primary proton current is \SI{21}{\milli\seivert\per\hour} at SUP and \SI{370}{\milli\seivert\per\hour} at CUP.
+The calculated value at SUP is slightly more than and therefore consistent with that predicted from a bare spallation target (\SI{17}{\milli\seivert\per\hour}) and is also consistent with an estimated upper limit reported in~\cite{Prokofiev2009} (\SI{40}{\milli\seivert\per\hour}).
+The calculated value at CUP is consistent with that calculated at SUP (a ratio of 17:1 is somewhat greater than $1/R^2$, as would be expected), but rather more than the estimated upper limit given in \cite{Prokofiev2014} (\SI{170}{\milli\seivert\per\hour}).
+We continue to evaluate our gamma calculations and will discuss them at greater length in the final paper.
 

### 2015-04-20 Paper2015.tex
Incorporated Alexander's page 1 comments.

@@
         A. V. Prokofiev\IEEEauthorrefmark{2} and
-        E. Passoth\IEEEauthorrefmark{2}
+        E. Passoth\IEEEauthorrefmark{3}
     }
@@
         \IEEEauthorrefmark{1}
-        University of Central Lancashire
+        University of Central Lancashire, England
     }
@@
         \IEEEauthorrefmark{2}
+        Division of Applied Nuclear Physics and The Svedberg Laboratory, University of Uppsala, Sweden
+    }
+    \IEEEauthorblockA{
+        \IEEEauthorrefmark{3}
         The Svedberg Laboratory, University of Uppsala
@@
 
-The ANITA facility at The Svedberg Laboratory has been widely used for accelerated testing for neutron single-event effects (SEE)~\cite{Prokofiev2009}.
-A high-flux facility, ANITA-CUP, has recently been introduced and reported by Prokofiev et al.~\cite{Prokofiev2014}.
+The ANITA facility~\cite{Prokofiev2009} at The Svedberg Laboratory (TSL) in Uppsala, Sweden, has been widely used for studies and accelerated testing for neutron single-event effects (SEE).
+A high-flux upgrade of the facility, ANITA-CUP, has recently been introduced and reported by Prokofiev et al.~\cite{Prokofiev2014}.
 
-Platt et al. have reported preliminary Monte Carlo models of neutron and gamma production at ANITA~\cite{Platt2013}.
-That work was motivated by a desire to understand the possibility of gamma sensitivity in detectors used for beam monitoring during SEE tests.
+Platt et al. have reported preliminary Monte Carlo simulations of neutron and gamma production at the standard ANITA facility~\cite{Platt2013}.
+That work was motivated by a need to understand possible sensitivity to gamma rays in detectors used for beam monitoring during SEE tests.
 Simulations of a bare spallation target showed qualitative agreement with independent calculations and measurements of the fast neutron field at the standard ANITA facility~\cite{Prokofiev2009}.
-The present work was motivated partly by a desire to investigate whether improvements in the fidelity of the geometry used in the simulations would lead to closer quantitative agreement with independent data, and partly to extend the work to encompass the new facility at ANITA-CUP~\cite{Prokofiev2014}.
+The present work was motivated partly by a desire to investigate whether improvements in the fidelity of the geometry used in the simulations would lead to closer quantitative agreement with independent data, and partly by a need to extend the work to encompass the new ANITA-CUP facility~\cite{Prokofiev2014}.
 
-Accordingly, in this paper we will present a comprehensive set of analyses of neutron and gamma fields at ANITA and ANITA-CUP, with comparison against independent models and validation against measurements.
+Accordingly, in this paper we present a comprehensive set of analyses of neutron and gamma fields at ANITA and ANITA-CUP, with comparison to independent models and validation against measurements.
 We present a subset of those results in this extended abstract.
@@
 %N.B. This is downstream of the downstream edge of the target in Qian's model.
-The SUP position is downstream of a collimator with variable aperture; the CUP and CUP-TOF positions are upstream of the same collimator.
+The SUP position is downstream of a frontal wall with a collimator with variable aperture; the CUP and CUP-TOF positions are upstream of the same collimator.
 The SUP and CUP positions are of interest as they are positions used for SEE tests; the CUP-TOF position is the location of thin-film breakdown counter (TFBC) detectors used for beam monitoring and characterisation including neutron time of flight (TOF) measurements.
@@
 	\caption{
-        Simulated ANITA facility overview seen from above (yellow: bending magnet; red: shielding components; blue: target assembly; grey: collimator; blue: detector system)
+        Simulated ANITA facility overview seen from above (yellow: bending magnet; red: shielding components; blue: neutron production target assembly; grey: collimator; blue: virtual detector system)
     }
@@
 Collimation is clearly visible.
-Within the beam umbra the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.1e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt2013} and \SI{9.3e5}{\neutron\per\cm\squared\per\second} from well-established analytical model~\cite{Prokofiev2009}.
+Within the beam umbra the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.1e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt2013} and \SI{9.3e5}{\neutron\per\cm\squared\per\second} from an analytical model derived from measurements~\cite{Prokofiev2009}.
 The analytical model therefore exceeds the present calculations by about 30\%.

### 2015-04-20 Paper2015.tex
Incorporated second page of comments from Alexander.

@@
 \section{Modelling}
-Simulations were conducted using Geant4 version 10.0~\cite{Agostinelli2003,Allison2006} with the binary intranuclear cascade model~\cite{Platt2013}.
+Simulations were conducted using Geant4 version 10.0~\cite{Agostinelli2003,Allison2006} with the binary intranuclear cascade model (see also~\cite{Platt2013}).
 A detailed model of the ANITA geometry~\cite{Prokofiev2009,Prokofiev2014} was implemented in Geant4, as illustrated in Fig.~\ref{fig:ANITAoverview}.
@@
 \subsection{Neutrons}
-Fig.~\ref{fig:SUPDensity} shows neutron spatial distribution at the SUP, for neutrons above \SI{10}{\MeV}.
-Collimation is clearly visible.
-Within the beam umbra the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.1e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt2013} and \SI{9.3e5}{\neutron\per\cm\squared\per\second} from an analytical model derived from measurements~\cite{Prokofiev2009}.
-The analytical model therefore exceeds the present calculations by about 30\%.
+Fig.~\ref{fig:SUPDensity} shows neutron distribution at the SUP, for neutrons above \SI{10}{\MeV}.
+The collimator ensures that the beam is circular.
+Within the beam umbra the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.1e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt2013} and \SI{9.3e5}{\neutron\per\cm\squared\per\second} from measurements.
+The measurements therefore exceed the present calculations by about 30\%.
+\todo{Check SUP flux.}
 
@@
         \label{fig:SUPDensity}
+        \todo{
+            Fig.~\ref{fig:SUPDensity} replace with 1D profile for neutrons above \SI{10}{\MeV}.
+             Show position of collimator.
+        }
     \end{minipage}
@@
     \caption{
-        Vertical neutron profile at the CUP, normalised to fluence rate on axis, with
-        \SI{10.2}{\cm} diameter collimator.
+        Vertical profile of \U238\ fission events at the CUP, with \SI{10.2}{\cm} diameter collimator. }
+    \label{fig:CUPProfile}
+    \todo{
+        Fig.~\ref{fig:CUPProfile}.
+        Revise legend.
+        Plot lines +symbols.
+        Add vertical lines?
     }
-    \label{fig:CUPProfile}
 \end{figure}
 
-Fig.~\ref{fig:CUPDensity} shows equivalent data for the CUP, which is upstream of the collimator.
-In the central region the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.85e6}{\neutron\per\cm\squared\per\second}, compared to \SI{1.17e7}{\neutron\per\cm\squared\per\second} from an analytical model reported by Prokofiev et al.~\cite{Prokofiev2014}.
-The analytical model therefore exceeds the present calculations about 50\%.
+Fig.~\ref{fig:CUPDensity} shows the spatial distribution of neutrons above \SI{10}{\MeV} at the CUP.
+As CUP is upstream of the collimator the distribution is not not circularly symmetric.
+In the central region the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.85e6}{\neutron\per\cm\squared\per\second}, compared to \SI{1.17e7}{\neutron\per\cm\squared\per\second} from measurements~\cite{Prokofiev2014}.
+The measurements therefore exceeds the present calculations about 50\%.
+\todo{Check current consistency -- make \SI{215}{\nA}, check Elke's report.}
 
-Fig.~\ref{fig:CUPProfile} shows the vertical neutron fluence profile at the CUP, compared with measurements made with \U238\ TFBCs.
-Results of calculations were folded in energy with the neutron fission cross section for \U238~\cite{Carlson2009}.
-The results show close agreement between measurement and simulation, although the sharp cut-off between about \SI{10}{\cm} and about \SI{15}{\cm} is not fully reproduced by the simulation.%
+TFBCs equipped with \U238\ targets were used to measure beam profile and time of flight spectra at the CUP-TOF position.
+Simulated neutron counts were folded in energy with the \U238\ fission cross-section~\cite{Carlson2009} and compared with measurements.
+Fig.~\ref{fig:CUPProfile} shows the resulting vertical distribution of the neutron-induced fission rate in \U238.
+The results show close agreement between measurement and simulation, although the sharp cut-off beyond \SI{11}{\cm} is not fully reproduced by the simulation.%
 \todo{
@@
 
-Fig.~\ref{fig:TOFSpectra} compares simulated and measured TOF spectra at the CUP-TOF position.
-Neutron time of flight data from the simulation were folded in energy with the \U238\ fission cross-section, convolved with a \SI{5}{\ns} rectangle function approximating the primary proton micropulse shape, and overlapped at \SI{45}{\ns}, representing the timing ambiguity due to the micropulse period.
+In Fig.~\ref{fig:TOFSpectra} we compare simulated and measured TOF spectra at the CUP-TOF position.
+Neutron TOF data from the simulation were folded in energy with the \U238\ fission cross-section, convolved with a \SI{5}{\ns} rectangle function approximating the primary proton micropulse shape, and overlapped at \SI{45}{\ns}, representing the timing ambiguity due to the micropulse period.
 The results show very close agreement in the position and width of the TOF peak.
+The continuum beyond about \SI{30}{\ns}, corresponding to neutrons below about \SI{40}{\MeV}, is somewhat higher in the calculation than in the measurement.
+This might indicate a relative overestimate of lower energy neutrons in the calculations -- or an corresponding underestimate of higher-energy neutrons.
 Prokofiev et al.~\cite{Prokofiev2014} note that the TOF spectrum at the CUP comprises three parts, a component directly from the target, one scattered forward from target surroundings, and one scattered backwards from the front face of the collimator block.
 The present simulations confirm the Prokofiev et al. semi-empirical multicomponent model. Details of this confirmation will be presented in the full paper but are omitted here for brevity.
-In this summary we limit ourselves to the observation that direct reproduction of the deceptively complex TOF spectrum, as shown by Fig.~\ref{fig:TOFSpectra} reflects the fidelity of the present model spectrum and geometry.\todo{Improve phrasing here.}
 
@@
     \caption{
-        Neutron time of flight spectra at the CUP-TOF position, with \SI{3}{\cm} diameter collimator.
+        Time of flight spectra for \U238 fission events at the CUP-TOF position, with \SI{3}{\cm} diameter collimator.
         }
     \label{fig:TOFSpectra}
+    \todo{
+        Figure:~\ref{fig:TOFSpectra}: Edit legend, edit y label, make simulated data a curve.
+    }
 \end{figure}

### 2015-04-20 Paper2015.tex
Incorporated comments from third page.

@@
         \label{fig:LethargyplotSUP}
+        \todo{
+            Fig.~\ref{fig:LethargyplotSUP}: update legend. Make dotted curve dash-dotted.
+        }
     \end{minipage}
@@
 
-Fig.~\ref{fig:Lethargyplots} compares calculated spectra at SUP and CUP with their respective analytical models.
+Fig.~\ref{fig:Lethargyplots} compares calculated spectra at SUP and CUP with analytical fits based on MCNPX simulations~\cite{Prokofiev2009,Prokofiev2014}.
 The SUP data are also compared with results from preliminary Geant4 simulations~\cite{Platt2013}.
-These curves are normalised to neutron fluence above \SI{10}{\MeV} an presented as lethargy plots to emphasis the shape of the spectra rather than their integral fluence rate.
-The increased integral fluence rate at SUP from the present calculations, compared to the preliminary results of \cite{Platt2013} is therefore not visible in Fig.~\ref{fig:LethargyplotSUP}.
-Fig.~\ref{fig:LethargyplotSUP} does show an increased contribution below about \SI{1}{\MeV}, consistent with interactions in materials other than the target, which were absent from the preliminary simulations.
-Fig.~\ref{fig:LethargyplotCUP} shows extremely close agreement with the analytical model from~\cite{Prokofiev2014} (the analytical model smooths out the structure in the evaporation peak around \SI{1}{\MeV}).
-When compared to the analytical models the calculated spectra from the current work lead to slightly lower neutron yield and slightly higher peak energies in the higher energy peak near \SI{100}{\MeV}.
+These curves are normalised to neutron fluence above \SI{10}{\MeV} and presented as lethargy plots to emphasis the shape of the spectra rather than their integral fluence rate.
+%The increased integral fluence rate at SUP from the present calculations, compared to the preliminary results of \cite{Platt2013}, is therefore not visible in Fig.~\ref{fig:LethargyplotSUP}.
+Fig.~\ref{fig:LethargyplotSUP} shows an increased contribution below about \SI{1}{\MeV}, consistent with interactions in materials other than the target, absent from the preliminary simulations.
+Fig.~\ref{fig:LethargyplotCUP} shows extremely close agreement with the analytical model from~\cite{Prokofiev2014} (the analytical model does not reproduce the structure in the evaporation peak around \SI{1}{\MeV}).
+When compared to the fits the calculated spectra from the current work lead to slightly lower neutron yield and slightly higher peak energies in the higher energy peak near \SI{100}{\MeV}.
+This is consistent with the TOF spectra (see Fig.~\ref{fig:TOFSpectra} and associated discussion.)
 It is not surprising that this is not affected by the improved model geometry as this peak arises from intranuclear cascades in the target.
@@
 
-Fig.~\ref{fig:DifferentialSpectra} summarises neutron spectra results by comparing differential flux as calculated in this work with the Prokofiev et al. models~\cite{Prokofiev2009,Prokofiev2014}.
-The SUP calculations and analytical model agree very closely below \SI{20}{\MeV}; the analytical model exceeds the calculations somewhat above that energy.
-At CUP the analytical model exceeds the Geant4 calculations by about 50\%, slightly more than that above \SI{20}{\MeV}.
+Fig.~\ref{fig:DifferentialSpectra} summarises neutron spectra results by comparing differential flux as calculated in this work with the analytical fits~\cite{Prokofiev2009,Prokofiev2014}.
+The SUP calculations and analytical fit agree very closely below \SI{20}{\MeV}; the analytical fit exceeds the calculations somewhat above that energy.
+At CUP the analytical fit exceeds the Geant4 calculations by about 50\%, slightly more than that above \SI{20}{\MeV}.
 

### 2015-04-20 Paper2015.tex
Considered page 4's comments.
Updated abstract.

@@
 \begin{abstract}
-    Monte Carlo simulation of spallation neutron source of ANITA at TSL was used to analyze radiation fields at the Close User Position (CUP) and Standard User Position(SUP) for single-event effect testing.
-...
-    \todo{Revise abstract}
+    Simulations of the ANITA spallation neutron source at The Svedberg Laboratory (TSL) are described.
+    Neutron field calculates show close agreement with measurements at both standard and close user positions.
+    Gamma radiation characteristics are also predicted.
 \end{abstract}
@@
         \label{fig:GammaSpatialDistributionSUP}
+        \todo{Fig~\ref{fig:GammaSpatialDistributionSUP}: consider what to do with this figure.}
     \end{minipage}
@@
     \label{fig:GammaDoseEnergy}
+    \todo{Fig.~\ref{fig:GammaDoseEnergy}: correct y axis units. Consider whether to combine.}
 \end{figure}

### 2015-04-20 Paper2015.tex
New figure for SUP collimation. New caption for differential neutron spectra.

@@
     \begin{minipage}{\columnwidth}
-        \includegraphics[width=0.9\columnwidth]{SUP10ColSpatialDistribution10MeVRADECS.png}
+        \includegraphics[width=0.9\columnwidth]{SUP10ColRadiusEffect10MeV.png}
         \subcaption{
             Standard User Position.
-            Concentric white circles indicate nominal umbra and penumbra limits
+            Vertical lines indicate nominal umbra and penumbra limits
         }
@@
     \caption{
-        Differential neutron spectra at CUP and SUP (\SI{10.2}{\cm} diameter collimator), comparing results of this work to analytical models~\cite{Prokofiev2009,Prokofiev2014}
+        Differential neutron spectra at CUP (upper curves) and SUP (lower curves), comparing results of this work to analytical models~\cite{Prokofiev2009,Prokofiev2014}.
+        With \SI{10.2}{\cm} diameter collimator
     }

### 2015-04-20 Paper2015.tex
Added conclusion. General editing, mostly for space.

@@
         S. P. Platt\IEEEauthorrefmark{1},
-        A. V. Prokofiev\IEEEauthorrefmark{2} and
+        A. V. Prokofiev\IEEEauthorrefmark{2}\IEEEauthorrefmark{3} and
         E. Passoth\IEEEauthorrefmark{3}
@@
         \IEEEauthorrefmark{2}
-        Division of Applied Nuclear Physics and The Svedberg Laboratory, University of Uppsala, Sweden
+        Division of Applied Nuclear Physics, University of
+        Uppsala, Sweden
     }
@@
         \IEEEauthorrefmark{3}
-        The Svedberg Laboratory, University of Uppsala
+        The Svedberg Laboratory, University of Uppsala, Sweden
     }
@@
     Simulations of the ANITA spallation neutron source at The Svedberg Laboratory (TSL) are described.
-    Neutron field calculates show close agreement with measurements at both standard and close user positions.
+    Neutron field calculations show close agreement with measurements at both standard and close user positions.
     Gamma radiation characteristics are also predicted.
@@
 
-The ANITA facility~\cite{Prokofiev2009} at The Svedberg Laboratory (TSL) in Uppsala, Sweden, has been widely used for studies and accelerated testing for neutron single-event effects (SEE).
+The ANITA facility~\cite{Prokofiev2009} at The Svedberg Laboratory (TSL) in Uppsala, Sweden, has been widely used for accelerated testing for neutron single-event effects (SEE).
 A high-flux upgrade of the facility, ANITA-CUP, has recently been introduced and reported by Prokofiev et al.~\cite{Prokofiev2014}.
@@
 That work was motivated by a need to understand possible sensitivity to gamma rays in detectors used for beam monitoring during SEE tests.
-Simulations of a bare spallation target showed qualitative agreement with independent calculations and measurements of the fast neutron field at the standard ANITA facility~\cite{Prokofiev2009}.
-The present work was motivated partly by a desire to investigate whether improvements in the fidelity of the geometry used in the simulations would lead to closer quantitative agreement with independent data, and partly by a need to extend the work to encompass the new ANITA-CUP facility~\cite{Prokofiev2014}.
+Simulations of a bare spallation target showed qualitative agreement with independent calculations and measurements of the fast neutron field~\cite{Prokofiev2009}.
+The present work was motivated partly by a desire to investigate whether improvements to the geometry used in the simulations would lead to closer quantitative agreement with measurements, and partly by a need to extend the work to encompass the new ANITA-CUP facility~\cite{Prokofiev2014}.
 
@@
 Simulations were conducted using Geant4 version 10.0~\cite{Agostinelli2003,Allison2006} with the binary intranuclear cascade model (see also~\cite{Platt2013}).
-A detailed model of the ANITA geometry~\cite{Prokofiev2009,Prokofiev2014} was implemented in Geant4, as illustrated in Fig.~\ref{fig:ANITAoverview}.
+A detailed model of the ANITA geometry was implemented in Geant4, as illustrated in Fig.~\ref{fig:ANITAoverview}.
 %; a summary only is given here.
@@
 Simulated protons were incident axially at an energy of \SI{180}{\MeV}.
-Resulting neutron and gamma fields were evaluated at several detector locations.
+Resulting neutron and gamma fields were evaluated at several virtual detector locations.
 In this paper results are presented for three of these: the Standard User Position (SUP), \SI{2.5}{\m} downstream of the target, the Close User Position (CUP), \SI{0.75}{\m} downstream of the target, and the CUP-TOF position, \SI{0.84}{m} downstream of the target.
 %N.B. This is downstream of the downstream edge of the target in Qian's model.
-The SUP position is downstream of a frontal wall with a collimator with variable aperture; the CUP and CUP-TOF positions are upstream of the same collimator.
+The SUP position is downstream of a collimator with variable aperture; the CUP and CUP-TOF positions are upstream of the same collimator.
 The SUP and CUP positions are of interest as they are positions used for SEE tests; the CUP-TOF position is the location of thin-film breakdown counter (TFBC) detectors used for beam monitoring and characterisation including neutron time of flight (TOF) measurements.
@@
 
-\section{Results}
+\section{Results and discussion}
 
@@
 The collimator ensures that the beam is circular.
-Within the beam umbra the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.1e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt2013} and \SI{9.3e5}{\neutron\per\cm\squared\per\second} from measurements.
-The measurements therefore exceed the present calculations by about 30\%.
-\todo{Check SUP flux.}
-
+Within the beam umbra the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.6e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt2013} and \SI{1.0e6}{\neutron\per\cm\squared\per\second} from measurements.
+The present calculations therefore underestimate measurements by 24\%. 
 \begin{figure}[t]
@@
         \label{fig:SUPDensity}
-        \todo{
-            Fig.~\ref{fig:SUPDensity} replace with 1D profile for neutrons above \SI{10}{\MeV}.
-             Show position of collimator.
-        }
     \end{minipage}
@@
     \label{fig:CUPProfile}
-    \todo{
-        Fig.~\ref{fig:CUPProfile}.
-        Revise legend.
-        Plot lines +symbols.
-        Add vertical lines?
-    }
 \end{figure}
@@
 As CUP is upstream of the collimator the distribution is not not circularly symmetric.
-In the central region the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.85e6}{\neutron\per\cm\squared\per\second}, compared to \SI{1.17e7}{\neutron\per\cm\squared\per\second} from measurements~\cite{Prokofiev2014}.
-The measurements therefore exceeds the present calculations about 50\%.
-\todo{Check current consistency -- make \SI{215}{\nA}, check Elke's report.}
+In the central region the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{215}{\nA} is \SI{8.44e6}{\neutron\per\cm\squared\per\second}, compared to \SI{1.17e7}{\neutron\per\cm\squared\per\second} from measurements~\cite{Prokofiev2014}.
+The present results underestimate measurements by 28\%.
 
@@
 Fig.~\ref{fig:CUPProfile} shows the resulting vertical distribution of the neutron-induced fission rate in \U238.
-The results show close agreement between measurement and simulation, although the sharp cut-off beyond \SI{11}{\cm} is not fully reproduced by the simulation.%
-\todo{
-    Improve presentation of results for CUP profile.
-    Make calculations at the same positions as those used for the measurements.
-}
+The results are in general agreement although the simulation results are somewhat broader than calculations and the sharp cut-off beyond \SI{11}{\cm} is not fully reproduced by the simulation.
 
@@
 This might indicate a relative overestimate of lower energy neutrons in the calculations -- or an corresponding underestimate of higher-energy neutrons.
-Prokofiev et al.~\cite{Prokofiev2014} note that the TOF spectrum at the CUP comprises three parts, a component directly from the target, one scattered forward from target surroundings, and one scattered backwards from the front face of the collimator block.
+
+Prokofiev et al.~\cite{Prokofiev2014} note that the TOF spectrum at the CUP consists of three parts, a component directly from the target, one scattered forward from target surroundings, and one scattered backwards from the front face of the collimator block.
 The present simulations confirm the Prokofiev et al. semi-empirical multicomponent model. Details of this confirmation will be presented in the full paper but are omitted here for brevity.
@@
             SUP.
-            The comparison is against the fit of Prokofiev et al.~\cite{Prokofiev2009} and preliminary Geant4 modelling by Platt et al.~\cite{Platt2013}
+            The comparison is to the fit of Prokofiev et al.~\cite{Prokofiev2009} and preliminary Geant4 modelling by Platt et al.~\cite{Platt2013}
         }
@@
             CUP.
-            The comparison is against the fit of Prokofiev et al.~\cite{Prokofiev2014}
+            The comparison is to the fit of Prokofiev et al.~\cite{Prokofiev2014}
         }
@@
 
+Fig.~\ref{fig:Lethargyplots} compares calculated spectra at SUP and CUP with analytical fits based on MCNPX simulations~\cite{Prokofiev2009,Prokofiev2014}.
+The SUP data are also compared with results from preliminary Geant4 simulations~\cite{Platt2013}.
+These curves are normalised to neutron fluence above \SI{10}{\MeV} and presented as lethargy plots to emphasis the shape of the spectra rather than their integral fluence rate.
+%The increased integral fluence rate at SUP from the present calculations, compared to the preliminary results of \cite{Platt2013}, is therefore not visible in Fig.~\ref{fig:LethargyplotSUP}.
+The present results show an increased contribution below about \SI{1}{\MeV}, consistent with interactions in materials other than the target, absent from the preliminary simulations.
+Fig.~\ref{fig:LethargyplotCUP} shows extremely close agreement between the present results and the analytical fit from~\cite{Prokofiev2014} (which cannot reproduce the structure in the evaporation peak around \SI{1}{\MeV}).
+
+When compared to the fits the calculated spectra from the current work lead to slightly lower neutron yield and slightly higher peak energies in the higher energy peak near \SI{100}{\MeV}.
+This is consistent with results for TOF spectra (see Fig.~\ref{fig:TOFSpectra} and associated discussion.)
+It is not surprising that this is unaffected by the improved model geometry as this peak arises from intranuclear cascades in the target.
+We continue to investigate this discrepancy and will discuss it further in our final paper.
+
 \begin{figure}[!t]
@@
     \caption{
-        Differential neutron spectra at CUP (upper curves) and SUP (lower curves), comparing results of this work to analytical models~\cite{Prokofiev2009,Prokofiev2014}.
-        With \SI{10.2}{\cm} diameter collimator
+        Differential neutron spectra at CUP (upper curves) and SUP (lower curves), each with the \SI{10.2}{\cm} collimator.
+        Comparison is to the fits of Prokofiev et al.~\cite{Prokofiev2009,Prokofiev2014}.
     }
@@
 
-Fig.~\ref{fig:Lethargyplots} compares calculated spectra at SUP and CUP with analytical fits based on MCNPX simulations~\cite{Prokofiev2009,Prokofiev2014}.
-The SUP data are also compared with results from preliminary Geant4 simulations~\cite{Platt2013}.
-These curves are normalised to neutron fluence above \SI{10}{\MeV} and presented as lethargy plots to emphasis the shape of the spectra rather than their integral fluence rate.
-%The increased integral fluence rate at SUP from the present calculations, compared to the preliminary results of \cite{Platt2013}, is therefore not visible in Fig.~\ref{fig:LethargyplotSUP}.
-Fig.~\ref{fig:LethargyplotSUP} shows an increased contribution below about \SI{1}{\MeV}, consistent with interactions in materials other than the target, absent from the preliminary simulations.
-Fig.~\ref{fig:LethargyplotCUP} shows extremely close agreement with the analytical model from~\cite{Prokofiev2014} (the analytical model does not reproduce the structure in the evaporation peak around \SI{1}{\MeV}).
-When compared to the fits the calculated spectra from the current work lead to slightly lower neutron yield and slightly higher peak energies in the higher energy peak near \SI{100}{\MeV}.
-This is consistent with the TOF spectra (see Fig.~\ref{fig:TOFSpectra} and associated discussion.)
-It is not surprising that this is not affected by the improved model geometry as this peak arises from intranuclear cascades in the target.
-We continue to investigate this discrepancy and will discuss it further in our final paper.
-
-Fig.~\ref{fig:DifferentialSpectra} summarises neutron spectra results by comparing differential flux as calculated in this work with the analytical fits~\cite{Prokofiev2009,Prokofiev2014}.
-The SUP calculations and analytical fit agree very closely below \SI{20}{\MeV}; the analytical fit exceeds the calculations somewhat above that energy.
-At CUP the analytical fit exceeds the Geant4 calculations by about 50\%, slightly more than that above \SI{20}{\MeV}.
+Fig.~\ref{fig:DifferentialSpectra} summarises neutron spectra results by comparing differential flux as calculated in this work with the analytical fits.
+The SUP calculations and fit agree very closely below \SI{20}{\MeV}; the fit exceeds the calculations somewhat above that energy.
+At CUP the fit exceeds the Geant4 calculations by about 50\%, slightly more than that above \SI{20}{\MeV}.
 
@@
 Fig.~\ref{fig:DifferentialGammaSpectra} shows the calculated differential gamma spectra within the central region of the spatial distribution.
-There is a broad continuum up to an energy of about \SI{10}{\MeV}, with a peak in the fluence spectrum at about \SI{0.5}{\MeV} (where the annihilation peak is visible).
+There is a broad continuum up to an energy of about \SI{10}{\MeV}, with a peak in the fluence spectrum at about \SI{0.5}{\MeV} (where the annihilation peak is also visible).
 The gamma fluence rate is an order of magnitude greater at CUP that at SUP, consistent with the closer range to the target and its immediate surroundings.
@@
 
-Fig.~\ref{fig:GammaDoseEnergy} shows the calculated distribution of gamma dose, obtained by folding the gamma spectra (Fig~\ref{fig:GammaDoseEnergy}) with dose conversion data from \cite{Kwon1980}.
+Fig.~\ref{fig:GammaDoseEnergy} shows the calculated gamma dose spectrum, obtained by folding the gamma spectra (Fig~\ref{fig:GammaDoseEnergy}) with dose conversion data from \cite{Kwon1980}.
 The results show structure with peaks around \SI{1.5}{\MeV}, \SI{3}{\MeV}, \SI{6}{\MeV} and \SI{9}{\MeV}.
@@
 
-\section{Discussion}
-\todo{Discussion}
+\section{Conclusion}
+We have used Geant4 for detailed Monte Carlo simulations of the ANITA and ANITA-CUP neutron SEE test facilities at The Svedberg Laboratory.
+Neutron fluence rate, energy spectrum, time profile and and spatial distribution show good agreement with measurements and independent simulations (using MCNPX).
+Gamma radiation characteristics have also been predicted and preliminary evaluations indicate that they are consistent with a limited set of measurement data.
+For reasons of space only a small subset of results are presented here.
+Evaluation of our results is still in progress; additional data and evaluation will be presented in our final paper.
 
-\begin{thebibliography}{99} % Bibliography - this is intentionally simple in this template
-
+\begin{thebibliography}{9} 
 \bibitem{Prokofiev2009}
-Prokofiev, A. V. et al.,
+A.V. Prokofiev et al.,
 \newblock ``Characterization of the ANITA neutron source for accelerated SEE testing at The Svedberg Laboratory'',
@@
 \bibitem{Prokofiev2014}
-Prokofiev, A. V. et al.,
+A.V. Prokofiev et al.,
 \newblock ``CUP--A new high-flux irradiation position at the ANITA neutron facility at TSL'',		\newblock {\em IEEE Trans. Nucl. Sci.} vol.~61 no.~4, pp.~1929-1936, 2014
@@
 \bibitem{Platt2013}
-Platt, S. P. et al.,
+S. P. Platt et al.,
 \newblock ``Neutron and gamma fields at neutron spallation sources for single-event-effects testing'',
@@
 \bibitem{Agostinelli2003}
-Agostinelli, S. et al.,
+S. Agostinelli et al.,
 \newblock``Geant4--a simulation toolkit'',
@@
 \bibitem{Allison2006}
-Allison, J. et al.,
+J. Allison et al.,
 \newblock ``Geant4 developments and applications'',
@@
 \bibitem{Carlson2009}
-Carlson, A. D. et al.,
+A. D. Carlson et al.,
 \newblock ``International evaluation of neutron cross section standards'',
@@
 \bibitem{Kwon1980}
-Kwon, S.-G. et al.,
+S.-G. Kwon et al.,
 \newblock ``Calculation of neutron and gamma-ray flux-to-dose-rate conversion factors'',

### 2015-04-20 Paper2015.tex
working process

--- 2015-04-20 Paper2015.tex
@@
 \DeclareSIUnit\neutron{n}
-\DeclareSIUnit{\seivert}{Sv}
 
@@
         A. V. Prokofiev\IEEEauthorrefmark{2} and
-        E. Passoth\IEEEauthorrefmark{3}
+        E. Passoth\IEEEauthorrefmark{2}
     }
@@
         \IEEEauthorrefmark{1}
-        University of Central Lancashire, England
+        University of Central Lancashire
     }
@@
         \IEEEauthorrefmark{2}
-        Division of Applied Nuclear Physics and The Svedberg Laboratory, University of Uppsala, Sweden
-    }
-    \IEEEauthorblockA{
-        \IEEEauthorrefmark{3}
         The Svedberg Laboratory, University of Uppsala
@@
 \begin{abstract}
-    Simulations of the ANITA spallation neutron source at The Svedberg Laboratory (TSL) are described.
-    Neutron field calculates show close agreement with measurements at both standard and close user positions.
-    Gamma radiation characteristics are also predicted.
+    Monte Carlo simulation of spallation neutron source of ANITA at TSL was used to analyze radiation fields at the Close User Position (CUP) and Standard User Position(SUP) for single-event effect testing.
+...
+    \todo{Revise abstract}
 \end{abstract}
@@
 
-The ANITA facility~\cite{Prokofiev2009} at The Svedberg Laboratory (TSL) in Uppsala, Sweden, has been widely used for studies and accelerated testing for neutron single-event effects (SEE).
-A high-flux upgrade of the facility, ANITA-CUP, has recently been introduced and reported by Prokofiev et al.~\cite{Prokofiev2014}.
+The ANITA facility at The Svedberg Laboratory has been widely used for accelerated testing for neutron single-event effects (SEE)~\cite{Prokofiev2009}.
+A high-flux facility, ANITA-CUP, has recently been introduced and reported by Prokofiev et al.~\cite{Prokofiev2014}.
 
-Platt et al. have reported preliminary Monte Carlo simulations of neutron and gamma production at the standard ANITA facility~\cite{Platt2013}.
-That work was motivated by a need to understand possible sensitivity to gamma rays in detectors used for beam monitoring during SEE tests.
-Simulations of a bare spallation target showed qualitative agreement with independent calculations and measurements of the fast neutron field at the standard ANITA facility~\cite{Prokofiev2009}.
-The present work was motivated partly by a desire to investigate whether improvements in the fidelity of the geometry used in the simulations would lead to closer quantitative agreement with independent data, and partly by a need to extend the work to encompass the new ANITA-CUP facility~\cite{Prokofiev2014}.
+Platt et al. have reported preliminary Monte Carlo models of neutron and gamma production at ANITA~\cite{Platt2013}.
+That work was motivated by a desire to understand the possibility of gamma sensitivity in detectors used for beam monitoring during SEE tests.
+Simulations of a bare spallation target showed qualitative agreement with independent calculations and measurements of the fast neutron field at the standard ANITA facility.
+The present work was motivated partly by a desire to investigate whether improvements in the fidelity of the geometry used in the simulations would lead to closer quantitative agreement with independent data, and partly to extend the work to encompass the new facility at ANITA-CUP.
 
-Accordingly, in this paper we present a comprehensive set of analyses of neutron and gamma fields at ANITA and ANITA-CUP, with comparison to independent models and validation against measurements.
+Accordingly, in this paper we will present a comprehensive set of analyses of neutron and gamma fields at ANITA and ANITA-CUP, with comparison against independent models and validation against measurements.
 We present a subset of those results in this extended abstract.
@@
 \section{Modelling}
-Simulations were conducted using Geant4 version 10.0~\cite{Agostinelli2003,Allison2006} with the binary intranuclear cascade model (see also~\cite{Platt2013}).
+Simulations were conducted using Geant4 version 10.0~\cite{Agostinelli2003,Allison2006} with the binary intranuclear cascade model~\cite{Platt2013}.
 A detailed model of the ANITA geometry~\cite{Prokofiev2009,Prokofiev2014} was implemented in Geant4, as illustrated in Fig.~\ref{fig:ANITAoverview}.
@@
 Resulting neutron and gamma fields were evaluated at several detector locations.
-In this paper results are presented for three of these: the Standard User Position (SUP), \SI{2.5}{\m} downstream of the target, the Close User Position (CUP), \SI{0.75}{\m} downstream of the target, and the CUP-TOF position, \SI{0.84}{m} downstream of the target.
+In this paper results are presented for three of these: the Standard User Position (SUP), \SI{2.5}{\m} downstream of the target, the Close User Position (CUP), \SI{0.75}{\m} downstream of the target, and the CUP-TOF, \SI{0.84}{m} downstream of the target.
 %N.B. This is downstream of the downstream edge of the target in Qian's model.
-The SUP position is downstream of a frontal wall with a collimator with variable aperture; the CUP and CUP-TOF positions are upstream of the same collimator.
-The SUP and CUP positions are of interest as they are positions used for SEE tests; the CUP-TOF position is the location of thin-film breakdown counter (TFBC) detectors used for beam monitoring and characterisation including neutron time of flight (TOF) measurements.
+The SUP position is downstream of a collimator with variable aperture; the CUP and CUP-TOF positions are upstream of the same collimator.
+The SUP and CUP positions are of interest as they are positions used for SEE tests; the CUP-TOF position is the location of thin-film breakdown counter (TFBC) detectors used for beam monitoring and characterisation.
 TFBC data are used to validate simulation results.
@@
 	\caption{
-        Simulated ANITA facility overview seen from above (yellow: bending magnet; red: shielding components; blue: neutron production target assembly; grey: collimator; blue: virtual detector system)
+        Simulated ANITA facility overview seen from above (yellow: bending magnet; red: shielding components; blue: target assembly; grey: collimator; blue: detector system)
     }
@@
 \subsection{Neutrons}
-Fig.~\ref{fig:SUPDensity} shows neutron distribution at the SUP, for neutrons above \SI{10}{\MeV}.
-The collimator ensures that the beam is circular.
-Within the beam umbra the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.1e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt2013} and \SI{9.3e5}{\neutron\per\cm\squared\per\second} from measurements.
-The measurements therefore exceed the present calculations by about 30\%.
-\todo{Check SUP flux.}
+Fig.~\ref{fig:SUPDensity} shows neutron spatial distribution at the SUP, for neutrons above \SI{10}{\MeV}.
+Collimation is clearly visible.
+Within the beam umbra the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.1e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt2013} and \SI{9.3e5}{\neutron\per\cm\squared\per\second} from an established analytical model~\cite{Prokofiev2009}.
+The analytical model therefore exceeds the present calculations by about 30\%.
 
@@
     \begin{minipage}{\columnwidth}
-        \includegraphics[width=0.9\columnwidth]{SUP10ColSpatialDistribution10MeVRADECS.png}
+        \includegraphics[width=\columnwidth]{SUP10ColRadiusEffect10MeV.png}
         \subcaption{
             Standard User Position.
-            Concentric white circles indicate nominal umbra and penumbra limits
+            Concentric white circles indicate nominal umbra and penumbra limits.
         }
         \label{fig:SUPDensity}
-        \todo{
-            Fig.~\ref{fig:SUPDensity} replace with 1D profile for neutrons above \SI{10}{\MeV}.
-             Show position of collimator.
-        }
     \end{minipage}
     \begin{minipage}{\columnwidth}
-        \includegraphics[width=0.9\columnwidth]{CUP10ColSpatialDistribution10MeV.png}
+        \includegraphics[width=\columnwidth]{CUP10ColSpatialDistribution10MeV.png}
         \subcaption{Close User Position}
@@
 
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=0.9\columnwidth]{CUPTOF10beamproRADECS.png}
-    \caption{
-        Vertical profile of \U238\ fission events at the CUP, with \SI{10.2}{\cm} diameter collimator. }
-    \label{fig:CUPProfile}
-    \todo{
-        Fig.~\ref{fig:CUPProfile}.
-        Revise legend.
-        Plot lines +symbols.
-        Add vertical lines?
-    }
-\end{figure}
+Fig.~\ref{fig:CUPDensity} shows equivalent data for the CUP, which is upstream of the collimator.
+In the central region the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.85e6}{\neutron\per\cm\squared\per\second}, compared to \SI{1.17e7}{\neutron\per\cm\squared\per\second} from an analytical model reported by Prokofiev et al.~\cite{Prokofiev2014}.
+The analytical model therefore exceeds the present calculations about 50\%.
+The results show\ldots
+\todo{Describe the results: contours at CUP and SUP}
 
-Fig.~\ref{fig:CUPDensity} shows the spatial distribution of neutrons above \SI{10}{\MeV} at the CUP.
-As CUP is upstream of the collimator the distribution is not not circularly symmetric.
-In the central region the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.85e6}{\neutron\per\cm\squared\per\second}, compared to \SI{1.17e7}{\neutron\per\cm\squared\per\second} from measurements~\cite{Prokofiev2014}.
-The measurements therefore exceeds the present calculations about 50\%.
-\todo{Check current consistency -- make \SI{215}{\nA}, check Elke's report.}
-
-TFBCs equipped with \U238\ targets were used to measure beam profile and time of flight spectra at the CUP-TOF position.
-Simulated neutron counts were folded in energy with the \U238\ fission cross-section~\cite{Carlson2009} and compared with measurements.
-Fig.~\ref{fig:CUPProfile} shows the resulting vertical distribution of the neutron-induced fission rate in \U238.
-The results show close agreement between measurement and simulation, although the sharp cut-off beyond \SI{11}{\cm} is not fully reproduced by the simulation.%
-\todo{
-    Improve presentation of results for CUP profile.
-    Make calculations at the same positions as those used for the measurements.
-}
-
-In Fig.~\ref{fig:TOFSpectra} we compare simulated and measured TOF spectra at the CUP-TOF position.
-Neutron TOF data from the simulation were folded in energy with the \U238\ fission cross-section, convolved with a \SI{5}{\ns} rectangle function approximating the primary proton micropulse shape, and overlapped at \SI{45}{\ns}, representing the timing ambiguity due to the micropulse period.
-The results show very close agreement in the position and width of the TOF peak.
-The continuum beyond about \SI{30}{\ns}, corresponding to neutrons below about \SI{40}{\MeV}, is somewhat higher in the calculation than in the measurement.
-This might indicate a relative overestimate of lower energy neutrons in the calculations -- or an corresponding underestimate of higher-energy neutrons.
-Prokofiev et al.~\cite{Prokofiev2014} note that the TOF spectrum at the CUP comprises three parts, a component directly from the target, one scattered forward from target surroundings, and one scattered backwards from the front face of the collimator block.
-The present simulations confirm the Prokofiev et al. semi-empirical multicomponent model. Details of this confirmation will be presented in the full paper but are omitted here for brevity.
+Fig.~\ref{fig:CUPProfile} shows neutron fluence profile at the CUP, compared with measurements made with \U238\ TFBCs.
+Results of calculations were folded in energy with the neutron fission cross section for \U238~\cite{Carlson2009}.
+The results show\ldots
+\todo{Describe the results: profile at CUP}
 
@@
     \centering
-    \includegraphics[width=0.9\columnwidth]{CUPTOFtofspectraRADECS.png}
+    \includegraphics[width=\columnwidth]{CUPTOF10beamproRADECS.png}
     \caption{
-        Time of flight spectra for \U238 fission events at the CUP-TOF position, with \SI{3}{\cm} diameter collimator.
+        Neutron profile at the CUP, normalised to fluence rate on axis, with
+        \SI{10.2}{\cm} diameter collimator}
+    \label{fig:CUPProfile}
+\end{figure}
+
+Fig.~\ref{fig:TOFSpectra} compares simulated and measured TOF spectra at the CUP-TOF position.
+Neutron time of flight data from the simulation were folded in energy with the \U238\ fission cross-section, convolved with a \SI{5}{\ns} rectangle function approximating the primary proton micropulse shape, and overlapped at \SI{45}{\ns}, representing the timing ambiguity due to the micropulse period.
+The results show\ldots
+\todo{Explain what the results show.}
+
+\begin{figure}[t]
+    \includegraphics[width=\columnwidth]{CUPTOFtofspectraRADECS.png}
+    \caption{
+        Neutron time of flight spectra at the CUP-TOF position, with \SI{3}{\cm} diameter collimator
         }
     \label{fig:TOFSpectra}
-    \todo{
-        Figure:~\ref{fig:TOFSpectra}: Edit legend, edit y label, make simulated data a curve.
-    }
 \end{figure}
+
+Fig.~\ref{fig:Lethargyplots} compares calculated spectra at SUP and CUP with their respective analytical models.
+The SUP data are also compared with results from preliminary Geant4 simulations~\cite{Platt2013}.
+The results show\ldots
+\todo{Describe the neutron spectra.}
 
@@
         \centering
-        \includegraphics[width=0.8\columnwidth]{SUPNormalisedRADECS.eps}
+        \includegraphics[width=0.9\columnwidth]{SUPNormalisedRADECS.eps}
         \subcaption{
             SUP.
-            The comparison is against the fit of Prokofiev et al.~\cite{Prokofiev2009} and preliminary Geant4 modelling by Platt et al.~\cite{Platt2013}
-        }
-        \label{fig:LethargyplotSUP}
-        \todo{
-            Fig.~\ref{fig:LethargyplotSUP}: update legend. Make dotted curve dash-dotted.
-        }
+            The comparison is against the fit of Prokofiev et al.~\cite{Prokofiev2009} and preliminary Geant4 modelling by Platt et al.~\cite{Platt2013} }
     \end{minipage}
@@
         \centering
-        \includegraphics[width=0.8\columnwidth]{CUPcomparedProkofiev2014NormalisedRADECS.eps}
+        \includegraphics[width=0.9\columnwidth]{CUPcomparedProkofiev2014NormalisedRADECS.eps}
         \subcaption{
@@
         }
-        \label{fig:LethargyplotCUP}
     \end{minipage}
@@
 
-\begin{figure}[!t]
+Fig.~\ref{fig:DifferentialSpectra} summarises neutron spectra results by comparing differential flux as calculated in this work with the Prokofiev et al. models~\cite{Prokofiev2009,Prokofiev2014}.
+The SUP calculations and analytical model agree very closely below \SI{20}{\MeV}; the analytical model exceeds the calculations somewhat above that energy.
+At CUP the analytical model exceeds the Geant4 calculations by about 50\%, slightly more than that above \SI{20}{\MeV}.
+\todo{Improve precision of the summary description of differential spectra.}
+
+\begin{figure}[t]
     \centering
-    \includegraphics[width=0.8\columnwidth]{DiffYieldComparedSUPCUP10.eps}
+    \includegraphics[width=0.9\columnwidth]{DiffYieldComparedSUPCUP10.eps}
     \caption{
@@
 
-Fig.~\ref{fig:Lethargyplots} compares calculated spectra at SUP and CUP with analytical fits based on MCNPX simulations~\cite{Prokofiev2009,Prokofiev2014}.
-The SUP data are also compared with results from preliminary Geant4 simulations~\cite{Platt2013}.
-These curves are normalised to neutron fluence above \SI{10}{\MeV} and presented as lethargy plots to emphasis the shape of the spectra rather than their integral fluence rate.
-%The increased integral fluence rate at SUP from the present calculations, compared to the preliminary results of \cite{Platt2013}, is therefore not visible in Fig.~\ref{fig:LethargyplotSUP}.
-Fig.~\ref{fig:LethargyplotSUP} shows an increased contribution below about \SI{1}{\MeV}, consistent with interactions in materials other than the target, absent from the preliminary simulations.
-Fig.~\ref{fig:LethargyplotCUP} shows extremely close agreement with the analytical model from~\cite{Prokofiev2014} (the analytical model does not reproduce the structure in the evaporation peak around \SI{1}{\MeV}).
-When compared to the fits the calculated spectra from the current work lead to slightly lower neutron yield and slightly higher peak energies in the higher energy peak near \SI{100}{\MeV}.
-This is consistent with the TOF spectra (see Fig.~\ref{fig:TOFSpectra} and associated discussion.)
-It is not surprising that this is not affected by the improved model geometry as this peak arises from intranuclear cascades in the target.
-We continue to investigate this discrepancy and will discuss it further in our final paper.
-
-Fig.~\ref{fig:DifferentialSpectra} summarises neutron spectra results by comparing differential flux as calculated in this work with the analytical fits~\cite{Prokofiev2009,Prokofiev2014}.
-The SUP calculations and analytical fit agree very closely below \SI{20}{\MeV}; the analytical fit exceeds the calculations somewhat above that energy.
-At CUP the analytical fit exceeds the Geant4 calculations by about 50\%, slightly more than that above \SI{20}{\MeV}.
-
 \subsection{Photons}
-Fig.~\ref{fig:GammaSpatialDistribution} shows the calculated spatial distribution of gamma photons at SUP and CUP, and shows a gamma radiation distribution that is qualitatively very similar to that for neutrons at both locations.
+Fig.~\ref{fig:GammaSpatialDistribution} shows the calculated spatial distribution of gamma photons at SUP and CUP.
 Fig.~\ref{fig:DifferentialGammaSpectra} shows the calculated differential gamma spectra within the central region of the spatial distribution.
-There is a broad continuum up to an energy of about \SI{10}{\MeV}, with a peak in the fluence spectrum at about \SI{0.5}{\MeV} (where the annihilation peak is visible).
-The gamma fluence rate is an order of magnitude greater at CUP that at SUP, consistent with the closer range to the target and its immediate surroundings.
-The CUP spectrum also shows a backscatter peak around \SI{0.2}{\MeV}.
+The results show\ldots
+\todo{Describe the gamma results}
 
@@
     \begin{minipage}{\columnwidth}
-        \includegraphics[width=0.9\columnwidth]{SUP10ColSpatialDistributionAllG.png}
+        \includegraphics[width=\columnwidth]{SUP10ColSpatialDistributionAllG.png}
         \subcaption{Standard User Position}
         \label{fig:GammaSpatialDistributionSUP}
-        \todo{Fig~\ref{fig:GammaSpatialDistributionSUP}: consider what to do with this figure.}
     \end{minipage}
     \begin{minipage}{\columnwidth}
-        \includegraphics[width=0.9\columnwidth]{CUP10ColSpatialDistributionAllG.png}
+        \includegraphics[width=\columnwidth]{CUP10ColSpatialDistributionAllG.png}
         \subcaption{Close User Position}
@@
 
+Fig.~\ref{fig:GammaDoseEnergy} shows the calculated distribution of gamma dose, obtained by folding the gamma spectra (Fig~\ref{fig:GammaDoseEnergy}) with dose conversion data from \cite{Kwon1980}.
+The results show\ldots
+\todo{Describe the gamma dose versus energy graphs.}
+The calculated dose rate at \SI{200}{\nA} primary proton current is \SI{21}{\milli\gray\per\hour} at SUP and \SI{370}{\milli\gray\per\hour} at CUP.
+\todo{Discuss calculated dose rates}
+
 \begin{figure}[t]
@@
     \label{fig:GammaDoseEnergy}
-    \todo{Fig.~\ref{fig:GammaDoseEnergy}: correct y axis units. Consider whether to combine.}
 \end{figure}
-
-Fig.~\ref{fig:GammaDoseEnergy} shows the calculated distribution of gamma dose, obtained by folding the gamma spectra (Fig~\ref{fig:GammaDoseEnergy}) with dose conversion data from \cite{Kwon1980}.
-The results show structure with peaks around \SI{1.5}{\MeV}, \SI{3}{\MeV}, \SI{6}{\MeV} and \SI{9}{\MeV}.
-Note that these are not coincidence peaks, as the simulation counts individual photons.
-The calculated dose rate at \SI{200}{\nA} primary proton current is \SI{21}{\milli\seivert\per\hour} at SUP and \SI{370}{\milli\seivert\per\hour} at CUP.
-The calculated value at SUP is slightly more than and therefore consistent with that predicted from a bare spallation target (\SI{17}{\milli\seivert\per\hour}) and is also consistent with an estimated upper limit reported in~\cite{Prokofiev2009} (\SI{40}{\milli\seivert\per\hour}).
-The calculated value at CUP is consistent with that calculated at SUP (a ratio of 17:1 is somewhat greater than $1/R^2$, as would be expected), but rather more than the estimated upper limit given in \cite{Prokofiev2014} (\SI{170}{\milli\seivert\per\hour}).
-We continue to evaluate our gamma calculations and will discuss them at greater length in the final paper.
 
@@
 \newblock``Geant4--a simulation toolkit'',
-\newblock {\em Nucl. Inst. Meth. Phys. Res. A} vol.~506, pp.~250--303, 2003
+\newblock {\em Nucl. Unst. Meth. Phys. Res. A} vol.~506, pp.~250--303, 2003
 

### 2015-04-20 Paper2015.tex
Improved some figures - in eps.
All figures are modified. But not check the current from 200nA to 215nA.
Work in progress.

--- 2015-04-20 Paper2015.tex
@@
 The ANITA facility~\cite{Prokofiev2009} at The Svedberg Laboratory (TSL) in Uppsala, Sweden, has been widely used for accelerated testing for neutron single-event effects (SEE).
-A high-flux upgrade of the facility, ANITA-CUP, has recently been introduced and reported by Prokofiev et al.~\cite{Prokofiev2014}.
+A high-flux upgrade of the facility, ANITA-CUP, has recently been introduced and reported~\cite{Prokofiev2014}.
 
@@
 The collimator ensures that the beam is circular.
-Within the beam umbra the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.6e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt2013} and \SI{1.0e6}{\neutron\per\cm\squared\per\second} from measurements.
-The present calculations therefore underestimate measurements by 24\%. 
+Within the beam umbra the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{215}{\nA} is \SI{7.6e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt2013} and \SI{1.0e6}{\neutron\per\cm\squared\per\second} from measurements~\cite{Prokofiev2009}.
+The present calculations therefore underestimate measurements at the SUP by 24\%.
+\todo{Give SUP fluence rates to 3 s.f.}
+
 \begin{figure}[t]
     \begin{minipage}{\columnwidth}
-        \includegraphics[width=0.9\columnwidth]{SUP10ColRadiusEffect10MeV.png}
+        \includegraphics[width=0.9\columnwidth]{SUP10ColRadiusEffect10MeV.eps}
         \subcaption{
             Standard User Position.
-            Vertical lines indicate nominal umbra and penumbra limits
+            Dashed lines indicate nominal umbra and penumbra limits
         }
@@
     \centering
-    \includegraphics[width=0.9\columnwidth]{CUPTOF10beamproRADECS.png}
+    \includegraphics[width=0.9\columnwidth]{CUPTOF10beamproRADECS.eps}
     \caption{
-        Vertical profile of \U238\ fission events at the CUP, with \SI{10.2}{\cm} diameter collimator. }
+        Vertical profile of \U238\ fission events at the CUP, with \SI{10.2}{\cm} diameter collimator.
+        Dashed lines indicate expected quasi-collimation by the target surroundings.
+    }
     \label{fig:CUPProfile}
@@
 In the central region the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{215}{\nA} is \SI{8.44e6}{\neutron\per\cm\squared\per\second}, compared to \SI{1.17e7}{\neutron\per\cm\squared\per\second} from measurements~\cite{Prokofiev2014}.
-The present results underestimate measurements by 28\%.
+The present results underestimate measurements at the CUP by 28\%.
 
@@
 Simulated neutron counts were folded in energy with the \U238\ fission cross-section~\cite{Carlson2009} and compared with measurements.
-Fig.~\ref{fig:CUPProfile} shows the resulting vertical distribution of the neutron-induced fission rate in \U238.
-The results are in general agreement although the simulation results are somewhat broader than calculations and the sharp cut-off beyond \SI{11}{\cm} is not fully reproduced by the simulation.
+Fig.~\ref{fig:CUPProfile} shows the resulting vertical profiles of the neutron-induced fission rate in \U238.
+The results are in general agreement although the simulation results are somewhat broader than measurements and the sharp cut-off beyond \SI{11}{\cm} is not fully reproduced by the simulation.
 
@@
     \centering
-    \includegraphics[width=0.9\columnwidth]{CUPTOFtofspectraRADECS.png}
+    \includegraphics[width=0.9\columnwidth]{CUPTOFtofspectraRADECS.eps}
     \caption{
@@
         \centering
-        \includegraphics[width=0.8\columnwidth]{SUPNormalisedRADECS.eps}
+        \includegraphics[width=0.9\columnwidth]{SUPNormalisedRADECS.eps}
         \subcaption{
@@
 Fig.~\ref{fig:Lethargyplots} compares calculated spectra at SUP and CUP with analytical fits based on MCNPX simulations~\cite{Prokofiev2009,Prokofiev2014}.
-The SUP data are also compared with results from preliminary Geant4 simulations~\cite{Platt2013}.
+The SUP data are also compared with results from Geant4 simulations of the bare target~\cite{Platt2013}.
 These curves are normalised to neutron fluence above \SI{10}{\MeV} and presented as lethargy plots to emphasis the shape of the spectra rather than their integral fluence rate.
@@
 This is consistent with results for TOF spectra (see Fig.~\ref{fig:TOFSpectra} and associated discussion.)
-It is not surprising that this is unaffected by the improved model geometry as this peak arises from intranuclear cascades in the target.
+It is not surprising that this is unaffected by the improved model geometry as this peak arises from nucleon cascades in the target.
 We continue to investigate this discrepancy and will discuss it further in our final paper.
@@
     \centering
-    \includegraphics[width=0.8\columnwidth]{DiffYieldComparedSUPCUP10.eps}
+    \includegraphics[width=0.9\columnwidth]{DiffYieldComparedSUPCUP10.eps}
     \caption{
@@
 At CUP the fit exceeds the Geant4 calculations by about 50\%, slightly more than that above \SI{20}{\MeV}.
+\todo{Check this once the curves have been renormalised to the same current!}
 
@@
 Note that these are not coincidence peaks, as the simulation counts individual photons.
+\todo{Discuss photon counting with Qian.}
 The calculated dose rate at \SI{200}{\nA} primary proton current is \SI{21}{\milli\seivert\per\hour} at SUP and \SI{370}{\milli\seivert\per\hour} at CUP.
-The calculated value at SUP is slightly more than and therefore consistent with that predicted from a bare spallation target (\SI{17}{\milli\seivert\per\hour}) and is also consistent with an estimated upper limit reported in~\cite{Prokofiev2009} (\SI{40}{\milli\seivert\per\hour}).
-The calculated value at CUP is consistent with that calculated at SUP (a ratio of 17:1 is somewhat greater than $1/R^2$, as would be expected), but rather more than the estimated upper limit given in \cite{Prokofiev2014} (\SI{170}{\milli\seivert\per\hour}).
+The calculated value at SUP is slightly more than and therefore consistent with that predicted from a bare spallation target (\SI{17}{\milli\seivert\per\hour}) and is also consistent with an estimated upper limit of \SI{40}{\milli\seivert\per\hour} reported in~\cite{Prokofiev2009}.
+The calculated value at CUP is consistent with that calculated at SUP (a ratio of 17:1 is somewhat greater than $1/R^2$, as would be expected), but rather more than the estimated upper limit (\SI{170}{\milli\seivert\per\hour}) given in \cite{Prokofiev2014}.
 We continue to evaluate our gamma calculations and will discuss them at greater length in the final paper.

### 2015-04-20 Paper2015.tex
Work in progress.

@@
     Simulations of the ANITA spallation neutron source at The Svedberg Laboratory (TSL) are described.
-    Neutron field calculations show close agreement with measurements at both standard and close user positions.
+    Neutron radiation calculations show close agreement with measurements at both standard and close user positions.
     Gamma radiation characteristics are also predicted.
@@
     \label{fig:TOFSpectra}
-    \todo{
-        Figure:~\ref{fig:TOFSpectra}: Edit legend, edit y label, make simulated data a curve.
-    }
 \end{figure}

### 2015-04-20 Paper2015.tex

@@
 TFBC data are used to validate simulation results.
+Except where noted otherwise, all results in this summary are for the standard collimator aperture, with \SI{10.2}{\cm} diameter.
+Results for other collimator apertures will be presented in the full paper.
 
@@
 The present calculations therefore underestimate measurements at the SUP by 24\%.
+\todo{Check SUP fluence rates.}
 \todo{Give SUP fluence rates to 3 s.f.}
@@
     \caption{
-        Spatial distribution of neutrons above \SI{10}{\MeV} at SUP and CUP, with \SI{10.2}{\cm} diameter collimator
+        Spatial distribution of neutrons above \SI{10}{\MeV} at SUP and CUP
     }
@@
     \caption{
-        Vertical profile of \U238\ fission events at the CUP, with \SI{10.2}{\cm} diameter collimator.
+        Vertical profile of \U238\ fission events at the CUP.
         Dashed lines indicate expected quasi-collimation by the target surroundings.
@@
 The present results underestimate measurements at the CUP by 28\%.
+\todo{Check CUP fluence rates.}
 
@@
 The continuum beyond about \SI{30}{\ns}, corresponding to neutrons below about \SI{40}{\MeV}, is somewhat higher in the calculation than in the measurement.
-This might indicate a relative overestimate of lower energy neutrons in the calculations -- or an corresponding underestimate of higher-energy neutrons.
+This might indicate a relative overestimate of lower energy neutrons in the calculations.
 
@@
         \label{fig:LethargyplotSUP}
-        \todo{
-            Fig.~\ref{fig:LethargyplotSUP}: update legend. Make dotted curve dash-dotted.
-        }
     \end{minipage}
@@
 	\caption{
-        Calculated neutron spectra, normalised to fluence above \SI{10}{\MeV}, with
-        \SI{10.2}{\cm} diameter collimator
-    }
+        Calculated neutron spectra, normalised to fluence above \SI{10}{\MeV} }
 	\label{fig:Lethargyplots}
@@
     \centering
-    \includegraphics[width=0.9\columnwidth]{DiffYieldComparedSUPCUP10.eps}
+    \includegraphics[width=0.9\columnwidth]{DiffYieldComparedSUPCUP10RADECS.eps}
     \caption{
-        Differential neutron spectra at CUP (upper curves) and SUP (lower curves), each with the \SI{10.2}{\cm} collimator.
+        Differential neutron spectra at CUP (upper curves) and SUP (lower curves).
         Comparison is to the fits of Prokofiev et al.~\cite{Prokofiev2009,Prokofiev2014}.
@@
 At CUP the fit exceeds the Geant4 calculations by about 50\%, slightly more than that above \SI{20}{\MeV}.
-\todo{Check this once the curves have been renormalised to the same current!}
+\todo{Check differential flux comparison one the curves have been renormalised to the same current.}
 
@@
     \begin{minipage}{\columnwidth}
-        \includegraphics[width=0.9\columnwidth]{SUP10ColSpatialDistributionAllG.png}
+        \includegraphics[width=0.9\columnwidth]{GSUPRadiusEffectaboveAllRADECS.eps}
         \subcaption{Standard User Position}
         \label{fig:GammaSpatialDistributionSUP}
-        \todo{Fig~\ref{fig:GammaSpatialDistributionSUP}: consider what to do with this figure.}
     \end{minipage}
@@
     \caption{
-        Calculated gamma spatial distribution, with
-        \SI{10.2}{\cm} diameter collimator
+        Calculated gamma spatial distribution
     }
@@
     \caption{
-        Calculated gamma spectra at CUP and SUP, with
-        \SI{10.2}{\cm} diameter collimator
-    }
+        Calculated gamma spectra at CUP (upper curve) and SUP (lower curve) }
     \label{fig:DifferentialGammaSpectra}
@@
 \begin{figure}[t]
-    \begin{minipage}{\columnwidth}
     \centering
-        \includegraphics[width=0.9\columnwidth]{DoseVSenergySUP.eps}
-        \subcaption{Standard User Position}
-        \label{fig:GammaDoseEnergySUP}
-    \end{minipage}
-    \begin{minipage}{\columnwidth}
-        \centering
-        \includegraphics[width=0.9\columnwidth]{DoseVSenergyCUP.eps}
-        \subcaption{Close User Position}
-        \label{fig:GammaDoseEnergyCUP}
-    \end{minipage}
+    \includegraphics[width=0.9\columnwidth]{DoseVSenergycomparedRADECS.eps}
     \caption{
-        Calculated gamma dose spectra, with
-        \SI{10.2}{\cm} diameter collimator
-    }
+        Calculated gamma dose spectra }
     \label{fig:GammaDoseEnergy}
-    \todo{Fig.~\ref{fig:GammaDoseEnergy}: correct y axis units. Consider whether to combine.}
+    \todo{Fig.~\ref{fig:GammaDoseEnergy}: correct y axis units.}
 \end{figure}

### 2015-04-20 Paper2015.tex
Spell check.

@@
 Fig.~\ref{fig:CUPDensity} shows the spatial distribution of neutrons above \SI{10}{\MeV} at the CUP.
-As CUP is upstream of the collimator the distribution is not not circularly symmetric.
+As CUP is upstream of the collimator the distribution is not circularly symmetric.
 In the central region the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{215}{\nA} is \SI{8.44e6}{\neutron\per\cm\squared\per\second}, compared to \SI{1.17e7}{\neutron\per\cm\squared\per\second} from measurements~\cite{Prokofiev2014}.
@@
 Prokofiev et al.~\cite{Prokofiev2014} note that the TOF spectrum at the CUP consists of three parts, a component directly from the target, one scattered forward from target surroundings, and one scattered backwards from the front face of the collimator block.
-The present simulations confirm the Prokofiev et al. semi-empirical multicomponent model. Details of this confirmation will be presented in the full paper but are omitted here for brevity.
+The present simulations confirm the Prokofiev et al. semi-empirical multi-component model. Details of this confirmation will be presented in the full paper but are omitted here for brevity.
 
@@
 We have used Geant4 for detailed Monte Carlo simulations of the ANITA and ANITA-CUP neutron SEE test facilities at The Svedberg Laboratory.
-Neutron fluence rate, energy spectrum, time profile and and spatial distribution show good agreement with measurements and independent simulations (using MCNPX).
+Neutron fluence rate, energy spectrum, time profile and spatial distribution show good agreement with measurements and independent simulations (using MCNPX).
 Gamma radiation characteristics have also been predicted and preliminary evaluations indicate that they are consistent with a limited set of measurement data.

### 2015-04-20 Paper2015.tex
Checked and corrected proton current (215nA) and corresponding integral fluence rate values.

@@
 The collimator ensures that the beam is circular.
-Within the beam umbra the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{215}{\nA} is \SI{7.6e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt2013} and \SI{1.0e6}{\neutron\per\cm\squared\per\second} from measurements~\cite{Prokofiev2009}.
-The present calculations therefore underestimate measurements at the SUP by 24\%.
-\todo{Check SUP fluence rates.}
-\todo{Give SUP fluence rates to 3 s.f.}
+Within the beam umbra the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{215}{\nA} is \SI{7.05e5}{\neutron\per\cm\squared\per\second}, compared to \SI{6.38e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt2013} and \SI{1.0e6}{\neutron\per\cm\squared\per\second} from measurements~\cite{Prokofiev2009}.
+The present calculations therefore underestimate measurements at the SUP by 30\%.
 
@@
     \label{fig:CUPProfile}
+    \todo{Fig.~\ref{fig:CUPProfile}: add axis labels.}
 \end{figure}
@@
 As CUP is upstream of the collimator the distribution is not circularly symmetric.
-In the central region the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{215}{\nA} is \SI{8.44e6}{\neutron\per\cm\squared\per\second}, compared to \SI{1.17e7}{\neutron\per\cm\squared\per\second} from measurements~\cite{Prokofiev2014}.
-The present results underestimate measurements at the CUP by 28\%.
-\todo{Check CUP fluence rates.}
+In the central region the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{215}{\nA} is \SI{7.85e6}{\neutron\per\cm\squared\per\second}, compared to \SI{1.17e7}{\neutron\per\cm\squared\per\second} from measurements~\cite{Prokofiev2014}.
+The present results underestimate measurements at the CUP by 33\%.
 
@@
     \label{fig:TOFSpectra}
+    \todo{Fig.~\ref{fig:TOFSpectra}: correct axis labels.}
 \end{figure}

### 2015-04-20 Paper2015.tex
Removed paragraph - not needed for summary - to make it all fit on 4 pages.
This is the paragraph about the multicomponent model.

@@
 
-Prokofiev et al.~\cite{Prokofiev2014} note that the TOF spectrum at the CUP consists of three parts, a component directly from the target, one scattered forward from target surroundings, and one scattered backwards from the front face of the collimator block.
-The present simulations confirm the Prokofiev et al. semi-empirical multi-component model. Details of this confirmation will be presented in the full paper but are omitted here for brevity.
-
 \begin{figure}[t]

### 2015-04-20 Paper2015.tex
Photon counting clarified.

@@
 Note that these are not coincidence peaks, as the simulation counts individual photons.
-\todo{Discuss photon counting with Qian.}
 The calculated dose rate at \SI{200}{\nA} primary proton current is \SI{21}{\milli\seivert\per\hour} at SUP and \SI{370}{\milli\seivert\per\hour} at CUP.

### 2015-04-20 Paper2015.tex
Summary complete. This version is ready to go to the conference.

@@
 \usepackage{todo}
-%\renewcommand\todo[1]{\relax}
-%\renewcommand\todos{\relax}
+\renewcommand\todo[1]{\relax}
+\renewcommand\todos{\relax}
 
@@
     \label{fig:CUPProfile}
-    \todo{Fig.~\ref{fig:CUPProfile}: add axis labels.}
 \end{figure}
@@
     \label{fig:TOFSpectra}
-    \todo{Fig.~\ref{fig:TOFSpectra}: correct axis labels.}
 \end{figure}
@@
 
-Fig.~\ref{fig:Lethargyplots} compares calculated spectra at SUP and CUP with analytical fits based on MCNPX simulations~\cite{Prokofiev2009,Prokofiev2014}.
+Fig.~\ref{fig:Lethargyplots} compares calculated spectra at SUP and CUP with analytical fits based on MCNPX simulations and TOF measurements~\cite{Prokofiev2009,Prokofiev2014}.
 The SUP data are also compared with results from Geant4 simulations of the bare target~\cite{Platt2013}.
@@
 When compared to the fits the calculated spectra from the current work lead to slightly lower neutron yield and slightly higher peak energies in the higher energy peak near \SI{100}{\MeV}.
-This is consistent with results for TOF spectra (see Fig.~\ref{fig:TOFSpectra} and associated discussion.)
+This is consistent with results for the simulated TOF spectra (see Fig.~\ref{fig:TOFSpectra} and associated discussion.)
 It is not surprising that this is unaffected by the improved model geometry as this peak arises from nucleon cascades in the target.
@@
 Fig.~\ref{fig:DifferentialSpectra} summarises neutron spectra results by comparing differential flux as calculated in this work with the analytical fits.
-The SUP calculations and fit agree very closely below \SI{20}{\MeV}; the fit exceeds the calculations somewhat above that energy.
-At CUP the fit exceeds the Geant4 calculations by about 50\%, slightly more than that above \SI{20}{\MeV}.
-\todo{Check differential flux comparison one the curves have been renormalised to the same current.}
+The SUP calculations and fit agree very closely in the range from \SIrange{1}{20}{\MeV}; the fit exceeds the calculations somewhat above that energy.
+At CUP the fit exceeds the Geant4 calculations somewhat at all energies, slightly more so above \SI{20}{\MeV}.
 
@@
     \label{fig:GammaDoseEnergy}
-    \todo{Fig.~\ref{fig:GammaDoseEnergy}: correct y axis units.}
 \end{figure}

### 2015-04-22 Paper2015.tex
Corrected "University of Uppsala" to "Uppsala University"

@@
         \IEEEauthorrefmark{2}
-        Division of Applied Nuclear Physics, University of
-        Uppsala, Sweden
+        Division of Applied Nuclear Physics, Uppsala University, Sweden
     }
@@
         \IEEEauthorrefmark{3}
-        The Svedberg Laboratory, University of Uppsala, Sweden
+        The Svedberg Laboratory, Uppsala University, Sweden
     }

### 2015-04-22 Paper2015.tex
Corrected typo: "emphasis/emphasise".

@@
 The SUP data are also compared with results from Geant4 simulations of the bare target~\cite{Platt2013}.
-These curves are normalised to neutron fluence above \SI{10}{\MeV} and presented as lethargy plots to emphasis the shape of the spectra rather than their integral fluence rate.
+These curves are normalised to neutron fluence above \SI{10}{\MeV} and presented as lethargy plots to emphasise the shape of the spectra rather than their integral fluence rate.
 %The increased integral fluence rate at SUP from the present calculations, compared to the preliminary results of \cite{Platt2013}, is therefore not visible in Fig.~\ref{fig:LethargyplotSUP}.

### 2015-04-22 Paper2015.tex
Clarified some discussion in response to comments from AVP.

@@
 %The increased integral fluence rate at SUP from the present calculations, compared to the preliminary results of \cite{Platt2013}, is therefore not visible in Fig.~\ref{fig:LethargyplotSUP}.
-The present results show an increased contribution below about \SI{1}{\MeV}, consistent with interactions in materials other than the target, absent from the preliminary simulations.
-Fig.~\ref{fig:LethargyplotCUP} shows extremely close agreement between the present results and the analytical fit from~\cite{Prokofiev2014} (which cannot reproduce the structure in the evaporation peak around \SI{1}{\MeV}).
+At SUP, the present results show an increased contribution below about \SI{1}{\MeV}, consistent with interactions in materials other than the target, absent from the preliminary simulations.
+Fig.~\ref{fig:LethargyplotCUP} shows good agreement between the present results and the analytical fit from~\cite{Prokofiev2014}, especially in the evaporation peak around \SI{1}{\MeV} (the fit cannot reproduce the structure in this energy region).
 
